### 2014-04-15 paper/paper.tex
LaTeXファイル追加

%
%
%
\long\def\comment#1{}
\newif\ifcover

% \documentstyle[times,chi2003ea]{article}
% \documentclass[nocopyrightspace,times]{chiproceedings-nospace}
% \documentclass[nocopyrightspace]{chiproceedings-nospace}

% パタンはtt
% 出力文字列はsf

\documentclass{article}
\usepackage{times}
\usepackage{uist04}

\usepackage{here} % [H]とするとその場所に配置されるらしい

\long\def\ttt#1{\texttt{\small #1}}
\long\def\tsf#1{\textsf{\small{#1}}}
\long\def\tit#1{\textit{\small{#1}}}

\usepackage{graphicx}
% mediabb.sty というのを使うとPDFをそのままincludegraphicsできるらしい。
% http://www.ns.musashi-tech.ac.jp/~inoue/Pages/TeX/mediabb.sty.html
%
% \usepackage{mediabb}
% \usepackage{ascmac}

\begin{document}
\title{ExpandHelp: A Flexible Help Architecture \\For the Rest of Us}
\author{
\begin{tabular}{l}
\parbox{5.5cm}{
\begin{center}
%Toshiyuki Masui\\
%Keio University\\
%masui@pitecan.com
~ \\
~ \\
~
\end{center}
}
\end{tabular}
}
\maketitle
\abstract

\keywords Help systems, Approximate pattern matching, Generate-and-filter

\tolerance=400 
  % makes some lines with lots of white space, but 	
  % tends to prevent words from sticking out in the margin

\section*{INTRODUCTION}

\subsubsection*{Vocabulary mismatch}

\subsubsection*{Model mismatch}

%\begin{figure}[H]
%\includegraphics[width=70mm]{figures/43d82e015388a040ce9b854ab064e60f.png}
%\caption{Clicking the ExHelp icon to show a query window of ExpandHelp.}
%\label{exhelp-init}
%\end{figure}

\section*{CONCLUSIONS}

\bibliographystyle{plain}
\bibliography{paper}

\end{document}

### 2014-04-15 paper/paper.tex
added figures and bibfile

@@
 \begin{document}
-\title{ExpandHelp: A Flexible Help Architecture \\For the Rest of Us}
+\title{Strotor: A Minimalistic Approach to Exploring Large Hierarchical Data}
 \author{
@@
 \begin{center}
-%Toshiyuki Masui\\
-%Keio University\\
-%masui@pitecan.com
+Toshiyuki Masui\\
+Keio University\\
+masui@pitecan.com
 ~ \\
@@
 \abstract
+We introduce a new simple information navigation technique
+that enables users to explore large hierarchical data structure
+using only two keys or one rotating device that can generate
+two different signals based on the rotation direction.
+
+Using the disk-based system called "Strotor",
+users can find an entry in a huge hierarchical database easily
+only by rotating a disk or a cylinder in two directions.
+
+Strotor can be easily installed in sofas, kitchens, cars, etc.
+where standard keyboards and remote controllers do not fit.
 
@@
 
-\subsubsection*{Vocabulary mismatch}
+Huge data are often represented as a hierarchical data structure, and
+various navigation methods are provided for exploring the data.
+For example, files on Unix are structured hierarchically, and
+various commands (\tsf{cd}, \tsf{ls}, etc.) and APIs are provided for exploring the file system.
+Large dictionary database can also be treated as a large
+hierarchical data, since the name of the entry can be treated hierarchically:
+e.g. an entry for ``dictionary'' can be stored under ``d'' and ``d/i''.
 
-\subsubsection*{Model mismatch}
+Many information visualization and navigation techniques for huge hierarchical data
+have been proposed[Treemap,etc].
+On personal computers,
+multiple GUI methods are usually provided for
+exploring the hierarchical file structure, because
+there is no best interaction technique for any situation.
+% there is no single interaction technique that is always good for any situation.
 
-%\begin{figure}[H]
-%\includegraphics[width=70mm]{figures/43d82e015388a040ce9b854ab064e60f.png}
-%\caption{Clicking the ExHelp icon to show a query window of ExpandHelp.}
-%\label{exhelp-init}
-%\end{figure}
+When a user cannot use a pointing device or a standard keyboard,
+selection-based interaction techniques are used for
+finding information in hierarchical data.
+For example, a user can hierarchically find a music file by
+selecting an artist from the list of artist names,
+selecting an album title from the title list,
+and selecting a music file from the song list.
+
+Users can do the selection jobs either by using a mouse or by using arrow keys.
+For exaple,
+users can use two keys for choosing an entry from the list
+(e.g. selecting an artist from the artist list),
+and another key is used for selecting an entry and show the next level
+(e.g. selecting an artist and show album titles).
+It is also necessary to provide a way to go back to the previous state, and
+another key can be used for that task
+(e.g. showing the artist list for artist selection).
+%
+This 4-way navigation is popular on small devices (e.g. small MP3 players) and remote controllers like AppleRemote\footnote{http://en.wikipedia.org/wiki/Apple\_Remote}
+for selecting a song from the hierarchical data.
+4-way navigation is also available on desktop software like Finder.app on Mac.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 547 179]{figures/4buttons.png}}
+\caption{4-button controllers}
+\label{u10}
+\end{figure}
+
+% http://www.reigncom.com/eng/media/press/en_pr_read.asp?no_noti=1630&cd_noti_host=9
+% D-Click Control System
+
+% Small devices like Rio MP3 player and remote controllers like AppleRemote have
+% 4 buttons for selecting a song from the hierarchical data.
+
+Using 4 keys might be okay in many cases, but it would be much better
+if we could do the navigation task using only 2 keys.
+In that case, we can use a rotating device like a disk or a cylinder for the navigation,
+since the device can generate two key signals based on the direction of the rotation.
+%
+We have developed a new navigation technique where only two keys are required
+for exploring large hierarchical data, and implemented the system on
+a rotating device ``Strotor''.
+
+% (語源)
+% Navigating large structured data through rotation.
+
+\section*{Navigation Method and Examples}
+
+Stroter is based on the following simple principles:
+
+\begin{enumerate}
+\item Display the selected element, its siblings, its ancestors and their siblings,
+and highlight the selected element.
+\item If the selected element has children, wait for a little moment,
+select the first child, and perform 1.
+As a result, all the siblings of the newly selected element appear in the list.
+\item When a user types U or D, select the element that is displayed next to the currently
+selected element and perform 1.
+If the depth of the newly selected element is different from the currently
+selected element, siblings of the currently selected element will disappear.
+\end{enumerate}
+
+We will show how these works, using a hierarchical data structure of
+shops in a shopping mall shown in Figure 1.
+Rectangles with thick border represent categories, and
+other rectangles represent individual shops.
+We use two keys, "U" (up key) and "D" (down key), for the navigation.
+
+\begin{figure}[H]
+% \includegraphics[width=70mm]{figures/fig1.pdf}
+\centerline{\includegraphics[width=70mm,bb=0 0 490 490]{figures/fig1.pdf}}
+\caption{Shops in a shopping mall.}
+\label{fig1}
+\end{figure}
+
+When the system starts, only the shops and categories
+at the top level are displayed (Figure 2).
+When the user types D,
+the second element (Stationery store) is selected (Figure 3).
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig2.pdf}}
+\caption{Initial display.}
+\label{fig2}
+\end{figure}
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig3.pdf}}
+\caption{Initial display.}
+\label{fig3}
+\end{figure}
+
+If the user types D two more times, 
+\tsf{Food/drink} category is selected (Figure 4).
+If the user stops typing keys and waits for a moment, the shops under the \tsf{Food/drink}
+category are displayed, and the first entry (\tsf{Liquor shop}) is automatically selected (Figure 5).
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig4.pdf}}
+\caption{Initial display.}
+\label{fig4}
+\end{figure}
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=24mm,bb=0 0 139 238]{figures/fig5.pdf}}
+\caption{Initial display.}
+\label{fig5}
+\end{figure}
+
+When the user types D twice and stops typing,
+\tsf{Fresh grocery} category is selected (Figure 6), and
+the shops under the category is automatically selected (Figure 7).
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=24mm,bb=0 0 139 238]{figures/fig6.pdf}}
+\caption{Initial display.}
+\label{fig6}
+\end{figure}
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=24mm,bb=0 0 139 292]{figures/fig7.pdf}}
+\caption{Initial display.}
+\label{fig7}
+\end{figure}
+
+When the user types U here, \tsf{Fresh grocery} is selected,
+the shops under \tsf{Fresh grocery} disappears (Figure 6).
+If the user types U two more times, the display changes to Figure 5,
+and one more typing U will generate? Figure 4.
+
+If the user types D in Figure 4, the next visible entry
+(\tsf{Clothing}) is selected (Figure 8), and then change to Figure 9.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig8.pdf}}
+\caption{Initial display.}
+\label{fig8}
+\end{figure}
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=24mm,bb=0 0 139 211]{figures/fig9.pdf}}
+\caption{Initial display.}
+\label{fig9}
+\end{figure}
+
+When the user types D twice in Figure 7,
+\tsf{Clothing} is selected, and Figure 8 appears.
+
+In this way, users can navigate through the hierarchical structure
+only by typing U/D keys at the right timing.
+
+\section*{Implementation}
+
+A prototype system was built in JavaScript and the system runs on modern browsers.
+Huge list of of news articles, movies, anime films, musics, and e-books are listed in one browser window
+and the content is displayed in another window.
+Users can hit two arrow keys or use the PowerMate device for the navigation.
+
+\section*{DISCUSSIONS}
+
+\subsection{Comparison with existing methods}
+
+4-way navigation are quite common for exploring hierarchical data structure,
+and modern computer users have no problem using it.
+Many mobile phones and PDAs are equipped with a jog dial with a push button,
+where the dial is used for selecting an item from a list and 
+the push button is used for moving to the next level.
+PowerMate is equipped with a push button which can used for such purposes.
+As far as we know,
+Strotor is the only interaction method for exploring hierarchical data structure
+with only two keys or one rotating device.
+
+Using a conventional hierarchical menu, children elements are displayed automatically
+when the parent element is selected by a mouse.
+The ``automatic expansion'' feature is Strotorと同じ。
+
+\subsection{Comparison with InfoVis techniques}
+
+Various information techniques like
+Treemap\cite{Johnson:1991:TSA:949607.949654},
+Hyperbolic Tree\cite{Lamping:1995:FTB:223904.223956},
+and Sunburst\cite{Stasko:2000:FDN:857190.857683}
+have been proposed for visualizing large hierarchical data.
+Zooming interface (ZUI) systems like Pad[], Pad++[]
+have also been used for handling ...
+All of these systems are useful for understanding the structure of
+large hierarchical data, but users of these systems have to use a pointing device
+for exploring the whole data.
+
+LensBar\cite{Masui:1998:LVB:647341.721215}
+is also a ZUI system for handling large hierarchical data,
+but the same data structure used in LensBar can be used for Strotor.
+Users can use a pointing devices when it is appropriate,
+and use two keys or a disk device when pointing devices is not available.
+
+時間を使っているのは問題
+可逆的でないから
+
+\subsection{Subjective Evaluations}
+
+No formal evaluation have been done yet, but Strotor has been used in the authors'
+living room for several months, and the author's family members are using it
+everyday for watching anime films and listening to music.
+
+Since the only thing a user can do with Strotor is rotating the device,
+a user can use the device and see what happens without thinking about
+other interactions.
+Using a disk device for data navigation might be a new experience for
+most of the users, but the hard restriction of the usage seems to be a
+good thing.
+
+Selecting a content only by rotating a dial is very 気持ち良い。
+
+% 音楽ソース、ニュースソース、動画、Wikipediaなどあらゆるものをダイヤルやペダルだけで検索できる
 

### 2014-04-15 paper/paper.tex
...

@@
 \begin{document}
-\title{Strotor: A Minimalistic Approach to Exploring Large Hierarchical Data}
+\title{Strotor: A Minimalistic Approach to \\
+Exploring Large Hierarchical Data}
 \author{
@@
 two different signals based on the rotation direction.
-
+%
 Using the disk-based system called "Strotor",
@@
 only by rotating a disk or a cylinder in two directions.
-
+%
 Strotor can be easily installed in sofas, kitchens, cars, etc.
@@
 
-Many information visualization and navigation techniques for huge hierarchical data
-have been proposed[Treemap,etc].
+Many information visualization techniques and navigation techniques for huge hierarchical data
+have been proposed.
 On personal computers,
-multiple GUI methods are usually provided for
+multiple GUI methods are provided for
 exploring the hierarchical file structure, because
-there is no best interaction technique for any situation.
+there is no best interaction technique for all the users and situations.
 % there is no single interaction technique that is always good for any situation.
@@
 and selecting a music file from the song list.
-
-Users can do the selection jobs either by using a mouse or by using arrow keys.
-For exaple,
-users can use two keys for choosing an entry from the list
+% Users can do the selection jobs either by using a mouse or by using arrow keys.
+% For exaple,
+Users can use two keys for choosing an entry from the list
 (e.g. selecting an artist from the artist list),
@@
 %
-This 4-way navigation is popular on small devices (e.g. small MP3 players) and remote controllers like AppleRemote\footnote{http://en.wikipedia.org/wiki/Apple\_Remote}
+This 4-way navigation is popular on small mp3 players\footnote{
+  e.g. http://www.iriver.com/product/view.asp?pCode=003\&pNo=37
+} and remote controllers like AppleRemote\footnote{http://en.wikipedia.org/wiki/Apple\_Remote}
 for selecting a song from the hierarchical data.
@@
 \centerline{\includegraphics[width=80mm,bb=0 0 547 179]{figures/4buttons.png}}
-\caption{4-button controllers}
+\caption{4-button controllers on a small mp3 player and AppleRemote.}
 \label{u10}
@@
 
-Using 4 keys might be okay in many cases, but it would be much better
+Using 4 keys might be okay on these devices, but it would be much better
 if we could do the navigation task using only 2 keys.
@@
 
-Stroter is based on the following simple principles:
+Stroter's behavior is based on the following simple principles:
 

### 2014-04-15 paper/paper.tex
...

@@
 Using 4 keys might be okay on these devices, but it would be much better
-if we could do the navigation task using only 2 keys.
+if we could perform the navigation task using only 2 keys.
 In that case, we can use a rotating device like a disk or a cylinder for the navigation,
@@
 %
-We have developed a new navigation technique where only two keys are required
-for exploring large hierarchical data, and implemented the system on
-a rotating device ``Strotor''.
+% We have developed a new navigation technique where only two keys are required
+% for exploring large hierarchical data, and implemented the system on
+% a rotating device ``Strotor''.
+%
+We have developed a new navigation technique and device called ``Strotor'',
+where users can explore large hierarchical database by simple rotating operation.
 
@@
 
+\begin{figure}[H]
+\centerline{\includegraphics[width=70mm,bb=0 0 306 110]{figures/rotation.pdf}}
+\caption{Using a rotation device for generating key events.}
+\label{rotation}
+\end{figure}
+
 \section*{Navigation Method and Examples}
 
-Stroter's behavior is based on the following simple principles:
+Stroter's behavior is based on the following simple principles.
+Two types of input, ``U'' (up) and ``D'' (down), are used for the navigation.
+They can be generated either by rotating the Strotor device or typing a keyboard.
 
 \begin{enumerate}
-\item Display the selected element, its siblings, its ancestors and their siblings,
-and highlight the selected element.
-\item If the selected element has children, wait for a little moment,
-select the first child, and perform 1.
-As a result, all the siblings of the newly selected element appear in the list.
-\item When a user types U or D, select the element that is displayed next to the currently
-selected element and perform 1.
+\item A portion of a hierarchical data is shown to the user.
+
+\item Always one element in the hierarchical data is selected and highlighted.
+
+% \item Display the selected element, its siblings, its ancestors and their siblings.
+
+\item When an elemented is selected, its siblings, its ancestors and their siblings are displayed
+around the selected elememt.
+
+\item Users can generate U to select the new element above the currently selected element,
+and generate D to select the new element below the selected element.
+Whenever the selection is changed, 3. is performed.
 If the depth of the newly selected element is different from the currently
 selected element, siblings of the currently selected element will disappear.
+
+\item When a newly selected element has children and the user does no further operations,
+the first child of the selected elemented is selected, and 3. is performed.
+As a result, all the siblings of the newly selected element
+(the first child of the currently selected elmeent) appear in the list.
+
 \end{enumerate}
 
-We will show how these works, using a hierarchical data structure of
-shops in a shopping mall shown in Figure 1.
+We show how Strotor works, using a hierarchical data structure of
+shops list in a shopping mall shown in Figure \ref{fig1}.
 Rectangles with thick border represent categories, and
 other rectangles represent individual shops.
-We use two keys, "U" (up key) and "D" (down key), for the navigation.
 
@@
 % \includegraphics[width=70mm]{figures/fig1.pdf}
-\centerline{\includegraphics[width=70mm,bb=0 0 490 490]{figures/fig1.pdf}}
-\caption{Shops in a shopping mall.}
+\centerline{\includegraphics[width=80mm,bb=0 0 490 490]{figures/fig1.pdf}}
+\caption{Sample data: shops in a shopping mall.}
 \label{fig1}
@@
 
-When the system starts, only the shops and categories
-at the top level are displayed (Figure 2).
-When the user types D,
-the second element (Stationery store) is selected (Figure 3).
+When the user starts the exploration, only the shops and categories
+at the top level are displayed (Figure \ref{fig2}).
+When the user generates D,
+the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3}).
 
@@
 
-If the user types D two more times, 
-\tsf{Food/drink} category is selected (Figure 4).
-If the user stops typing keys and waits for a moment, the shops under the \tsf{Food/drink}
-category are displayed, and the first entry (\tsf{Liquor shop}) is automatically selected (Figure 5).
+If the user generates D two more times, 
+\tsf{Food/drink} category is selected (Figure \ref{fig4}).
+If the user stops the operation and waits for a moment, the shops under the \tsf{Food/drink}
+category are displayed, and the first entry (\tsf{Liquor shop}) is automatically selected (Figure \ref{fig5}).
 
@@
 
-When the user types D twice and stops typing,
-\tsf{Fresh grocery} category is selected (Figure 6), and
-the shops under the category is automatically selected (Figure 7).
+When the user generates D twice and stops the operation,
+\tsf{Fresh grocery} category is selected (Figure \ref{fig6}), and
+after a short moment,
+the shops under the category is automatically selected (Figure \ref{fig7}).
 
@@
 
-When the user types U here, \tsf{Fresh grocery} is selected,
-the shops under \tsf{Fresh grocery} disappears (Figure 6).
-If the user types U two more times, the display changes to Figure 5,
-and one more typing U will generate? Figure 4.
+When the user generates U here, \tsf{Fresh grocery} is selected,
+the shops under \tsf{Fresh grocery} disappears (Figure \ref{fig6}).
+If the user generates U two more times, the display changes to the state
+shown in Figure \ref{fig5},
+and one more U will yield Figure \ref{fig4}.
 
-If the user types D in Figure 4, the next visible entry
-(\tsf{Clothing}) is selected (Figure 8), and then change to Figure 9.
+If the user generates D in Figure \ref{fig4}, the next visible entry
+(\tsf{Clothing}) is selected (Figure \ref{fig8}), and then the state changes to Figure \ref{fig9}.
 
@@
 
-When the user types D twice in Figure 7,
-\tsf{Clothing} is selected, and Figure 8 appears.
+When the user generates D twice in Figure \ref{fig7},
+\tsf{Clothing} is selected, and the display changes to Figure \ref{fig8}.
 
-In this way, users can navigate through the hierarchical structure
-only by typing U/D keys at the right timing.
+In this way, users can explore the hierarchical structure
+only by generating U/D keys at the right timing.
 
@@
 Users can hit two arrow keys or use the PowerMate device for the navigation.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=50mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
+\caption{PowerMate device used for the Strotor prototype.}
+\label{powermate}
+\end{figure}
 
@@
 PowerMate is equipped with a push button which can used for such purposes.
-As far as we know,
+% As far as we know,
+To the best of the authors' knowledge,
 Strotor is the only interaction method for exploring hierarchical data structure
-with only two keys or one rotating device.
+with one rotating device.
 
@@
 
+\small{
 \bibliographystyle{plain}
 \bibliography{paper}
+}
 

### 2014-04-15 paper/paper.tex
...

@@
 
+\long\def\ST{\textsf{\small{Strotor}}}
+
 \usepackage{graphicx}
@@
 \title{Strotor: A Minimalistic Approach to \\
-Exploring Large Hierarchical Data}
+Exploring Hierarchical Data}
 \author{
@@
 %
-Using the disk-based system called "Strotor",
+Using the rotation-based input device called ``\ST'',
 users can find an entry in a huge hierarchical database easily
@@
 %
-Strotor can be easily installed in sofas, kitchens, cars, etc.
+{\ST} can be easily installed in sofas, kitchens, cars, etc.
 where standard keyboards and remote controllers do not fit.
@@
 %
-We have developed a new navigation technique and device called ``Strotor'',
+We have developed a new navigation technique and device called ``{\ST}'',
 where users can explore large hierarchical database by simple rotating operation.
@@
 
-Stroter's behavior is based on the following simple principles.
+{\ST}'s behavior is based on the following simple principles.
 Two types of input, ``U'' (up) and ``D'' (down), are used for the navigation.
-They can be generated either by rotating the Strotor device or typing a keyboard.
+They can be generated either by rotating the {\ST} device or typing a keyboard.
 
 \begin{enumerate}
-\item A portion of a hierarchical data is shown to the user.
+\item A portion of the data is shown to the user as a list.
 
-\item Always one element in the hierarchical data is selected and highlighted.
+\item Always one element in the list is selected and highlighted.
 
@@
 
-\item Users can generate U to select the new element above the currently selected element,
-and generate D to select the new element below the selected element.
+\item Users can generate U to select the element above the currently selected element,
+or generate D to select the element below the selected element.
 Whenever the selection is changed, 3. is performed.
@@
 
-\item When a newly selected element has children and the user does no further operations,
-the first child of the selected elemented is selected, and 3. is performed.
+\item When a newly selected element has children and the user performs no further action,
+the first child of the selected elemented is newly selected and 3. is performed.
 As a result, all the siblings of the newly selected element
@@
 
-We show how Strotor works, using a hierarchical data structure of
+We show how {\ST} works, using a hierarchical data structure of
 shops list in a shopping mall shown in Figure \ref{fig1}.
@@
 
-When the user generates D twice and stops the operation,
-\tsf{Fresh grocery} category is selected (Figure \ref{fig6}), and
-after a short moment,
-the shops under the category is automatically selected (Figure \ref{fig7}).
+When the user generates D twice,
+\tsf{Fresh grocery} category is selected (Figure \ref{fig6}).
 
@@
 \end{figure}
+
+If the user keeps generating D, 
+the list will change to Figure \ref{fig8},
+without expanding the children of \tsf{Fresh grocery}.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig8.pdf}}
+\caption{Initial display.}
+\label{fig8}
+\end{figure}
+
+If the use stops generating D at Figure \ref{fig6},
+the shops under category \tsf{Fresh grocery} is automatically selected (Figure \ref{fig7}).
 
@@
 When the user generates U here, \tsf{Fresh grocery} is selected,
-the shops under \tsf{Fresh grocery} disappears (Figure \ref{fig6}).
+and the shops under \tsf{Fresh grocery} disappears (Figure \ref{fig6}).
 If the user generates U two more times, the display changes to the state
 shown in Figure \ref{fig5},
-and one more U will yield Figure \ref{fig4}.
+and one more U will set the system to Figure \ref{fig4}.
 
@@
 (\tsf{Clothing}) is selected (Figure \ref{fig8}), and then the state changes to Figure \ref{fig9}.
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig8.pdf}}
-\caption{Initial display.}
-\label{fig8}
-\end{figure}
 
@@
 When the user generates D twice in Figure \ref{fig7},
-\tsf{Clothing} is selected, and the display changes to Figure \ref{fig8}.
+\tsf{Clothing} is selected, and the category will be expanded (Figure \ref{fig8}).
 
@@
 
-A prototype system was built in JavaScript and the system runs on modern browsers.
+A prototype system was built in JavaScript and runs on modern browsers.
 Huge list of of news articles, movies, anime films, musics, and e-books are listed in one browser window
@@
 
+ここにスクリーンショット
+
 \begin{figure}[H]
-\centerline{\includegraphics[width=50mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
-\caption{PowerMate device used for the Strotor prototype.}
+\centerline{\includegraphics[width=30mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
+\caption{A PowerMate used for the prototype.}
 \label{powermate}
@@
 To the best of the authors' knowledge,
-Strotor is the only interaction method for exploring hierarchical data structure
+{\ST} is the only interaction method for exploring hierarchical data structure
 with one rotating device.
@@
 when the parent element is selected by a mouse.
-The ``automatic expansion'' feature is Strotorと同じ。
+The ``automatic expansion'' feature is {\ST}と同じ。
 
@@
 is also a ZUI system for handling large hierarchical data,
-but the same data structure used in LensBar can be used for Strotor.
+but the same data structure used in LensBar can be used for {\ST}.
 Users can use a pointing devices when it is appropriate,
@@
 
-No formal evaluation have been done yet, but Strotor has been used in the authors'
+No formal evaluation have been done yet, but {\ST} has been used in the authors'
 living room for several months, and the author's family members are using it
@@
 
-Since the only thing a user can do with Strotor is rotating the device,
+Since the only thing a user can do with {\ST} is rotating the device,
 a user can use the device and see what happens without thinking about

### 2014-04-15 paper/paper.tex
...

@@
 \long\def\ST{\textsf{\small{Strotor}}}
+\long\def\U{\textsf{\small{U}}}
+\long\def\D{\textsf{\small{D}}}
 
@@
 
-Huge data are often represented as a hierarchical data structure, and
+Large data are often represented as a hierarchical data structure, and
 various navigation methods are provided for exploring the data.
@@
 
-Many information visualization techniques and navigation techniques for huge hierarchical data
-have been proposed.
+Many information visualization techniques and navigation techniques
+have been proposed for handling large hierarchical data.
 On personal computers,
@@
 
-When a user cannot use a pointing device or a standard keyboard,
+When a user cannot use a pointing device,
 selection-based interaction techniques are used for
@@
 (e.g. selecting an artist from the artist list),
-and another key is used for selecting an entry and show the next level
+and often another key is used for selecting an entry and showing the next level
 (e.g. selecting an artist and show album titles).
 It is also necessary to provide a way to go back to the previous state, and
-another key can be used for that task
+yet another key can be used for that task
 (e.g. showing the artist list for artist selection).
@@
 This 4-way navigation is popular on small mp3 players\footnote{
-  e.g. http://www.iriver.com/product/view.asp?pCode=003\&pNo=37
-} and remote controllers like AppleRemote\footnote{http://en.wikipedia.org/wiki/Apple\_Remote}
+  e.g. \textsf{http://www.iriver.com/product/view.asp?pCode=003\&pNo=37}
+} and remote controllers like AppleRemote\footnote{\textsf{http://en.wikipedia.org/wiki/Apple\_Remote}}
 for selecting a song from the hierarchical data.
@@
 In that case, we can use a rotating device like a disk or a cylinder for the navigation,
-since the device can generate two key signals based on the direction of the rotation.
+since the device can generate 2 signals based on the direction of the rotation (Figure \ref{rotation}).
 %
@@
 We have developed a new navigation technique and device called ``{\ST}'',
-where users can explore large hierarchical database by simple rotating operation.
+where users can explore large hierarchical database by simple rotating operations.
 
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=70mm,bb=0 0 306 110]{figures/rotation.pdf}}
+\centerline{\includegraphics[width=60mm,bb=0 0 294 110]{figures/rotation.pdf}}
 \caption{Using a rotation device for generating key events.}
@@
 
-\section*{Navigation Method and Examples}
+\section*{NAVIGATION METHOD AND EXAMPLES}
 
 {\ST}'s behavior is based on the following simple principles.
-Two types of input, ``U'' (up) and ``D'' (down), are used for the navigation.
+Two types of input, ``{\U}'' (up) and ``{\D}'' (down), are used for the navigation.
 They can be generated either by rotating the {\ST} device or typing a keyboard.
@@
 
-\item Users can generate U to select the element above the currently selected element,
-or generate D to select the element below the selected element.
+\item Users can generate {\U} to select the element above the currently selected element,
+or generate {\D} to select the element below the selected element.
 Whenever the selection is changed, 3. is performed.
@@
 at the top level are displayed (Figure \ref{fig2}).
-When the user generates D,
+When the user generates {\D},
 the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3}).
@@
 \centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig3.pdf}}
-\caption{Initial display.}
+\caption{Typing {\D}.}
 \label{fig3}
@@
 
-If the user generates D two more times, 
+If the user generates {\D} two more times, 
 \tsf{Food/drink} category is selected (Figure \ref{fig4}).
 If the user stops the operation and waits for a moment, the shops under the \tsf{Food/drink}
-category are displayed, and the first entry (\tsf{Liquor shop}) is automatically selected (Figure \ref{fig5}).
+category are automatically displayed,
+and the first entry (\tsf{Liquor shop}) is selected (Figure \ref{fig5}).
 
@@
 \centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig4.pdf}}
-\caption{Initial display.}
+\caption{Selecting Food/drink.}
 \label{fig4}
@@
 \centerline{\includegraphics[width=24mm,bb=0 0 139 238]{figures/fig5.pdf}}
-\caption{Initial display.}
+\caption{Selecting Liquor shop.}
 \label{fig5}
@@
 
-When the user generates D twice,
+When the user generates {\D} twice,
 \tsf{Fresh grocery} category is selected (Figure \ref{fig6}).
@@
 \centerline{\includegraphics[width=24mm,bb=0 0 139 238]{figures/fig6.pdf}}
-\caption{Initial display.}
+\caption{Selecting Fresh grocery.}
 \label{fig6}
@@
 
-If the user keeps generating D, 
+If the user keeps generating {\D}, 
 the list will change to Figure \ref{fig8},
@@
 \centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig8.pdf}}
-\caption{Initial display.}
+\caption{Selecting Clothing.}
 \label{fig8}
@@
 
-If the use stops generating D at Figure \ref{fig6},
+If the use stops generating {\D} at Figure \ref{fig6},
 the shops under category \tsf{Fresh grocery} is automatically selected (Figure \ref{fig7}).
@@
 \centerline{\includegraphics[width=24mm,bb=0 0 139 292]{figures/fig7.pdf}}
-\caption{Initial display.}
+\caption{Selecting Fish store.}
 \label{fig7}
@@
 
-When the user generates U here, \tsf{Fresh grocery} is selected,
-and the shops under \tsf{Fresh grocery} disappears (Figure \ref{fig6}).
-If the user generates U two more times, the display changes to the state
+When the user generates {\U} here, \tsf{Fresh grocery} is selected,
+and the shops under \tsf{Fresh grocery} disappears, 
+resulting in the same state as Figure \ref{fig6}.
+If the user generates {\U} two more times, the display changes to the state
 shown in Figure \ref{fig5},
-and one more U will set the system to Figure \ref{fig4}.
+and one more {\U} will set the system to the state of Figure \ref{fig4}.
 
-If the user generates D in Figure \ref{fig4}, the next visible entry
+If the user generates {\D} in Figure \ref{fig4}, the next visible entry
 (\tsf{Clothing}) is selected (Figure \ref{fig8}), and then the state changes to Figure \ref{fig9}.
@@
 
-When the user generates D twice in Figure \ref{fig7},
+When the user generates {\D} twice in Figure \ref{fig7},
 \tsf{Clothing} is selected, and the category will be expanded (Figure \ref{fig8}).
@@
 In this way, users can explore the hierarchical structure
-only by generating U/D keys at the right timing.
+only by generating {\U}/{\D} keys at the right timing.
 
@@
 
-A prototype system was built in JavaScript and runs on modern browsers.
+A prototype system was built in JavaScript and the system runs on modern browsers.
 Huge list of of news articles, movies, anime films, musics, and e-books are listed in one browser window

### 2014-04-16 paper/paper.tex
...

@@
 {\ST}'s behavior is based on the following simple principles.
-Two types of input, ``{\U}'' (up) and ``{\D}'' (down), are used for the navigation.
+Two types of operations, ``{\U}'' (up) and ``{\D}'' (down), are used for the navigation.
 They can be generated either by rotating the {\ST} device or typing a keyboard.
@@
 \begin{enumerate}
-\item A portion of the data is shown to the user as a list.
+\item A portion of the data is listed to the user.
 
-\item Always one element in the list is selected and highlighted.
+\item One element in the list is selected and highlighted.
 
@@
 If the depth of the newly selected element is different from the currently
-selected element, siblings of the currently selected element will disappear.
+selected element, siblings of the currently selected element disappear.
 
 \item When a newly selected element has children and the user performs no further action,
-the first child of the selected elemented is newly selected and 3. is performed.
+the first child of the selected elemented is newly selected, and 3. is performed.
 As a result, all the siblings of the newly selected element
@@
 We show how {\ST} works, using a hierarchical data structure of
-shops list in a shopping mall shown in Figure \ref{fig1}.
+shops list in a shopping mall shown in Figure \ref{fig1} as example data.
 Rectangles with thick border represent categories, and
@@
 \centerline{\includegraphics[width=24mm,bb=0 0 139 211]{figures/fig9.pdf}}
-\caption{Initial display.}
+\caption{Selecting Shoed store.}
 \label{fig9}
@@
 
-A prototype system was built in JavaScript and the system runs on modern browsers.
-Huge list of of news articles, movies, anime films, musics, and e-books are listed in one browser window
-and the content is displayed in another window.
-Users can hit two arrow keys or use the PowerMate device for the navigation.
+A prototype system was built using JavaScript and it runs on modern browsers.
+A large list of news articles, movies, anime films, musics, and e-book titles are listed in one browser window
+and the content is displayed in another window (Figure \ref{screenshot}).
 
-ここにスクリーンショット
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 671 464]{figures/95cf2fec71c52ead6fdbcb7f79aca654.png}}
+\caption{Selecting an Internet radio station.}
+\label{screenshot}
+\end{figure}
+
+We used
+PowerMate\footnote{
+  \textsf{http://griffintechnology.com/support/powermate}
+} from Griffin Technology for the rotating device.
+PowerMate generates standard keyboard events when rotated,
+and no special programming techniques are required.
+%
+Users can explore all the contents just by
+rotating the device clockwise and counterclockwise.
 
@@
 4-way navigation are quite common for exploring hierarchical data structure,
-and modern computer users have no problem using it.
-Many mobile phones and PDAs are equipped with a jog dial with a push button,
-where the dial is used for selecting an item from a list and 
-the push button is used for moving to the next level.
-PowerMate is equipped with a push button which can used for such purposes.
+and it is familiar to computer users.
+Some mobile phones and PDAs are equipped with a jog dial with a push button,
+where the dial is used for choosing an item from a list and 
+the push button is used for fixing the selection.
+% PowerMate is equipped with a push button which can used for such purposes.
 % As far as we know,
-To the best of the authors' knowledge,
+All the existing methods require more than 2 keys/buttons, and
+to the best of the authors' knowledge,
 {\ST} is the only interaction method for exploring hierarchical data structure
@@
 
-Using a conventional hierarchical menu, children elements are displayed automatically
-when the parent element is selected by a mouse.
-The ``automatic expansion'' feature is {\ST}と同じ。
+Using a conventional hierarchical menu,
+child elements are displayed automatically when their parent element is selected by a mouse.
+The behavior is common to computer users,
+and {\ST}'s automatic transition (e.g. from Figure \ref{fig4} to Figure \ref{fig5})
+looks familiar to users.
 
@@
 
-Various information techniques like
+Various information visualization techniques like
 Treemap\cite{Johnson:1991:TSA:949607.949654},
@@
 have been proposed for visualizing large hierarchical data.
-Zooming interface (ZUI) systems like Pad[], Pad++[]
-have also been used for handling ...
-All of these systems are useful for understanding the structure of
+Zooming user interface (ZUI) systems like
+Pad\cite{Perlin:1993:PAA:166117.166125} and
+Pad++\cite{Bederson:1994:PZG:192426.192435}
+can also been used for handling large hierarchical data laid out on a 2D space.
+%
+These visualization techniques and descendent technologies have become popular these days and
+all of these systems are useful for understanding the structure of
 large hierarchical data, but users of these systems have to use a pointing device
-for exploring the whole data.
+to take full advantage of their advantages.
 
-LensBar\cite{Masui:1998:LVB:647341.721215}
-is also a ZUI system for handling large hierarchical data,
-but the same data structure used in LensBar can be used for {\ST}.
-Users can use a pointing devices when it is appropriate,
-and use two keys or a disk device when pointing devices is not available.
+% More conventional visualization techniques like TreeView\footnote{
+%   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
+% } by replacing 4-way navigation to our approach.
 
-時間を使っているのは問題
-可逆的でないから
+% {\ST} can be adopted to more conventional visualization techniques like
+% TreeView\footnote{
+%   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
+% } by replacing 4-way navigation to our approach.
 
-\subsection{Subjective Evaluations}
+It seems to be a good idea to use {\ST} on more conventional visualization techniques like
+TreeView\footnote{
+  \textsf{http://en.wikipedia.org/wiki/Tree\_view}
+}, by replacing 4-way navigation to {\ST}.
 
-No formal evaluation have been done yet, but {\ST} has been used in the authors'
-living room for several months, and the author's family members are using it
+% LensBar\cite{Masui:1998:LVB:647341.721215}
+% is also a ZUI system for handling large hierarchical data,
+% but the same data structure used in LensBar can be used for {\ST}.
+% Users can use a pointing devices when it is appropriate,
+% and use two keys or a disk device when pointing devices is not available.
+
+\subsection{Timing control}
+
+The biggest disadvantage of {\ST} is that
+the behavior of {\ST} depends on the speed of the user's operations.
+In Figure \ref{fig4},
+if a user wanted to select \tsf{Clothing} but couldn't generate {\D}
+quickly enough, he will see Figure \ref{fig5} instead of Figure \ref{fig7}.
+This is a tradeoff between usability and simplicty, and
+the best parameter should be set based on the user and the {\ST} device.
+
+\section*{EVALUATION}
+
+No formal evaluation have been done yet, but {\ST} has been used in the author's
+living room for six months, and the author's family members are using it
 everyday for watching anime films and listening to music.
+Besides PowerMate, a wireless mouse is preferred,
+since we can carry the mouse anywhere and select
+a film or a music just by rotating the mouse wheel.
 
+We displayed {\ST} at an exhibition
+held in November 2013, and asked more than 100 people to try it.
+%
 Since the only thing a user can do with {\ST} is rotating the device,
-a user can use the device and see what happens without thinking about
-other interactions.
-Using a disk device for data navigation might be a new experience for
-most of the users, but the hard restriction of the usage seems to be a
-good thing.
+users seemed to be able to understand the behavior of {\ST} with trials and errors.
+% 
+% a user can use the device and see what happens without thinking about
+% other interactions.
+% 
+Using only one rotating device for data navigation is a new experience for
+all the users, but the hard restriction of the device seems to have worked in this case.
 
-Selecting a content only by rotating a dial is very 気持ち良い。
-
+% Selecting a content only by rotating a dial is very 気持ち良い。
 % 音楽ソース、ニュースソース、動画、Wikipediaなどあらゆるものをダイヤルやペダルだけで検索できる

### 2014-04-16 dial.js

@@ -43,17 +43,17 @@ var loadData = function(){
 };
 
 var initData = function(nodes,parent,level){
-    for(var i=0;i<nodes.length;i++){
-	var node = nodes[i];
-	node.number = i;
-	node.level = level;
-	node.elder = (i > 0 ? nodes[i-1] : null);
-	node.younger = (i < nodes.length-1 ? nodes[i+1] : null);
-	node.parent = parent;
-	if(node.children){
-	    initData(node.children,node,level+1);
-	}
+  for(var i=0;i<nodes.length;i++){
+    var node = nodes[i];
+    node.number = i;
+    node.level = level;
+    node.elder = (i > 0 ? nodes[i-1] : null);
+    node.younger = (i < nodes.length-1 ? nodes[i+1] : null);
+    node.parent = parent;
+    if(node.children){
+      initData(node.children,node,level+1);
     }
+  }
 };
 
 var browserHeight = function(){ // jQuery式の標準関数がありそうだが?

### 2014-04-16 paper/paper.tex
...

@@
 When the user generates {\D},
-the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3}).
+the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3})\footnote{
+  Readers can try this at \textsf{http://jsbin.com/lecuroku}.
+}.
 
@@
 %
-Since the only thing a user can do with {\ST} is rotating the device,
+Since the only thing a user can do with {\ST} is to rotate the device,
 users seemed to be able to understand the behavior of {\ST} with trials and errors.
@@
 
+\begin{figure}[H]
+\centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
+\caption{Asking people to use Strotor at an exhibition. The subject is using PowerMate for browsing photos.}
+\label{powermate}
+\end{figure}
+
 % Selecting a content only by rotating a dial is very 気持ち良い。
@@
 \section*{CONCLUSIONS}
+
+We have developed a new very simple interaction method for exploring
+large hierarchical data structure.
+Using only one rotating device,
 

### 2014-04-16 paper/paper.tex
...

@@
 Besides PowerMate, a wireless mouse is preferred,
-since we can carry the mouse anywhere and select
+since we can carry a wireless mouse anywhere and select
 a film or a music just by rotating the mouse wheel.
@@
 We displayed {\ST} at an exhibition
-held in November 2013, and asked more than 100 people to try it.
+held in November 2013, and asked more than 100 people to try it
+(Figure \ref{exhibition}).
 %
@@
 Using only one rotating device for data navigation is a new experience for
-all the users, but the hard restriction of the device seems to have worked in this case.
+all the subjects, but the hard restriction of the device seems to have worked in this case.
 
@@
 \centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
-\caption{Asking people to use Strotor at an exhibition. The subject is using PowerMate for browsing photos.}
-\label{powermate}
+\caption{People trying Strotor at an exhibition.}
+\label{exhibition}
 \end{figure}
@@
 
-We have developed a new very simple interaction method for exploring
+We have developed a new simple interaction method ``{\ST}'' for exploring
 large hierarchical data structure.
-Using only one rotating device,
+{\ST} user can easily find an entry in a huge hierarchical database
+only by using a rotating input device which can be installed at
+wide range of locations where conventional keybords and switches do not fit.
+We are hoping to try various implementations of {\ST} and try them at
+various places like kitchens, restrooms, etc.
 

### 2014-04-16 paper/demo/strotor.js
added demo/

@@ -1,0 +1,314 @@
+//
+// strotor.js
+//
+
+var useAnimation = true;   // アニメーションを使うかどうか
+var showContents = false;   // コンテンツを別ウィンドウで表示 (デバッグ時false)
+
+var nodeList = {};         // 表示可能ノードのリスト. nodeList[0]を中心に表示する
+var oldNodeList;           // アニメーション前のnodeList
+var spans = {};            // 表示されるspan要素のリスト
+var oldSpans;              // アニメーション前のspans
+
+var shrinking = false;     // 回転方向
+
+var timeout;
+var StepTime = 1000;       // 段階的展開のタイムアウト時間
+var ExpandTime = 1500;     // 無操作時展開のタイムアウト時間
+var AnimationTime = 300;   // ズーミングのアニメーション時間
+
+var undoStack = [];        // undoのためにヒストリを覚えておく
+var undoTimeout;           // 
+var UndoTime = 1000;       // この時間以内ならundoを許す
+
+var win;
+if(showContents){
+  win = window.open();  // YouTube, クックパッド等がiframeで表示できないので別ウィンドウを開く
+}
+
+$(function() { // 最初に呼ばれるjQueryのready関数
+  loadData();
+});
+
+var loadData = function(){
+  $.getJSON("paperdata.json",function(data){
+    initData(data,null,0);
+    calc(data[0]);
+    timeout = setTimeout(expand,ExpandTime);
+    calc(data[0]);
+  });
+  // setTimeout(loadData,6*60*60*1000); // 6時間ごとにリロード
+};
+
+var initData = function(nodes,parent,level){
+  for(var i=0;i<nodes.length;i++){
+    var node = nodes[i];
+    node.number = i;
+    node.level = level;
+    node.elder = (i > 0 ? nodes[i-1] : null);
+    node.younger = (i < nodes.length-1 ? nodes[i+1] : null);
+    node.parent = parent;
+    if(node.children){
+      initData(node.children,node,level+1);
+    }
+  }
+};
+
+var browserHeight = function(){ // jQuery式の標準関数がありそうだが?
+  if(window.innerHeight){ return window.innerHeight; }  
+  else if(document.body){ return document.body.clientHeight; }  
+  return 0;  
+};
+
+var expand = function(){ // 注目してるエントリの子供を段階的に展開する
+  timeout = null;
+  shrinking = false;
+  if(nodeList[0] && nodeList[0].children){
[…]

### 2014-04-16 paper/paper.tex
spell check, etc.

@@
 \begin{center}
-Toshiyuki Masui\\
-Keio University\\
-masui@pitecan.com
+% Toshiyuki Masui\\
+% Keio University\\
+% masui@pitecan.com
 ~ \\
@@
 
-\keywords Help systems, Approximate pattern matching, Generate-and-filter
+\keywords Input device, Information navigation, Hierarchical data
 
@@
 exploring the hierarchical file structure, because
-there is no best interaction technique for all the users and situations.
+there is no best interaction technique that fits to all the users and situations.
 % there is no single interaction technique that is always good for any situation.
@@
 finding information in hierarchical data.
-For example, a user can hierarchically find a music file by
+For example, a user can hierarchically find a music data by
 selecting an artist from the list of artist names,
 selecting an album title from the title list,
-and selecting a music file from the song list.
+and selecting a music data from the song list.
 % Users can do the selection jobs either by using a mouse or by using arrow keys.
@@
 (e.g. selecting an artist from the artist list),
-and often another key is used for selecting an entry and showing the next level
+and often another key is used for selecting an entry and moving to the next level
 (e.g. selecting an artist and show album titles).
@@
 In that case, we can use a rotating device like a disk or a cylinder for the navigation,
-since the device can generate 2 signals based on the direction of the rotation (Figure \ref{rotation}).
+since the device can generate 2 signals based on the rotation direction (Figure \ref{rotation}).
 %
@@
 \begin{enumerate}
-\item A portion of the data is listed to the user.
+\item A portion of the hierarchical data is listed to the user.
 
@@
 
-\item When an elemented is selected, its siblings, its ancestors and their siblings are displayed
-around the selected elememt.
+\item When an elemente is selected, its siblings, its ancestors and their siblings are displayed
+around the selected element.
 
-\item Users can generate {\U} to select the element above the currently selected element,
-or generate {\D} to select the element below the selected element.
-Whenever the selection is changed, 3. is performed.
+\item Users can issue {\U} to select the element above the currently selected element,
+or issue {\D} to select the element below the selected element.
+Whenever the selection is changed, 3 is performed.
 If the depth of the newly selected element is different from the currently
@@
 \item When a newly selected element has children and the user performs no further action,
-the first child of the selected elemented is newly selected, and 3. is performed.
+the first child of the selected elemente is newly selected, and 3 is performed.
 As a result, all the siblings of the newly selected element
-(the first child of the currently selected elmeent) appear in the list.
+(the first child of the currently selected element) appear in the list.
 
@@
 We show how {\ST} works, using a hierarchical data structure of
-shops list in a shopping mall shown in Figure \ref{fig1} as example data.
+the shops list in a shopping mall shown in Figure \ref{fig1} as example data.
 Rectangles with thick border represent categories, and
@@
 
-When the user starts the exploration, only the shops and categories
+When a user starts the exploration, only the shops and categories
 at the top level are displayed (Figure \ref{fig2}).
-When the user generates {\D},
+When the user issues {\D},
 the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3})\footnote{
@@
 
-If the user generates {\D} two more times, 
+If the user issues {\D} two more times, 
 \tsf{Food/drink} category is selected (Figure \ref{fig4}).
@@
 
-When the user generates {\D} twice,
+When the user issues {\D} twice here,
 \tsf{Fresh grocery} category is selected (Figure \ref{fig6}).
@@
 
-If the user keeps generating {\D}, 
+If the user keeps issuing {\D}, 
 the list will change to Figure \ref{fig8},
@@
 
-If the use stops generating {\D} at Figure \ref{fig6},
+If the use stops issuing {\D} at Figure \ref{fig6},
 the shops under category \tsf{Fresh grocery} is automatically selected (Figure \ref{fig7}).
@@
 
-When the user generates {\U} here, \tsf{Fresh grocery} is selected,
+When the user issues {\U} here, \tsf{Fresh grocery} is selected,
 and the shops under \tsf{Fresh grocery} disappears, 
 resulting in the same state as Figure \ref{fig6}.
-If the user generates {\U} two more times, the display changes to the state
+If the user issues {\U} two more times, the display changes to the state
 shown in Figure \ref{fig5},
@@
 
-If the user generates {\D} in Figure \ref{fig4}, the next visible entry
+If the user issues {\D} in Figure \ref{fig4}, the next visible entry
 (\tsf{Clothing}) is selected (Figure \ref{fig8}), and then the state changes to Figure \ref{fig9}.
@@
 \centerline{\includegraphics[width=24mm,bb=0 0 139 211]{figures/fig9.pdf}}
-\caption{Selecting Shoed store.}
+\caption{Selecting Shoes store.}
 \label{fig9}
@@
 
-When the user generates {\D} twice in Figure \ref{fig7},
-\tsf{Clothing} is selected, and the category will be expanded (Figure \ref{fig8}).
+When the user issues {\D} twice in Figure \ref{fig7},
+\tsf{Clothing} is selected, and the category under \tsf{Food/drink} will shrinke (Figure \ref{fig8}).
 
 In this way, users can explore the hierarchical structure
-only by generating {\U}/{\D} keys at the right timing.
+only by issuing {\U} and {\D} at the right timing.
 
-\section*{Implementation}
+\section*{IMPLEMENTATION}
 
-A prototype system was built using JavaScript and it runs on modern browsers.
+A prototype of {\ST} was built using JavaScript on modern browsers.
 A large list of news articles, movies, anime films, musics, and e-book titles are listed in one browser window
@@
 
-\subsection{Comparison with existing methods}
+\subsection{Comparison with existing navigation methods}
 
-4-way navigation are quite common for exploring hierarchical data structure,
+4-way navigation is commonly used for exploring hierarchical data structure,
 and it is familiar to computer users.
 Some mobile phones and PDAs are equipped with a jog dial with a push button,
-where the dial is used for choosing an item from a list and 
+where the dial is used for choosing an item from the list and 
 the push button is used for fixing the selection.
@@
 child elements are displayed automatically when their parent element is selected by a mouse.
-The behavior is common to computer users,
+The behavior is well understood by computer users,
 and {\ST}'s automatic transition (e.g. from Figure \ref{fig4} to Figure \ref{fig5})
@@
 Pad++\cite{Bederson:1994:PZG:192426.192435}
-can also been used for handling large hierarchical data laid out on a 2D space.
+can also be used for handling large hierarchical data laid out in a 2D space.
 %
@@
 In Figure \ref{fig4},
-if a user wanted to select \tsf{Clothing} but couldn't generate {\D}
+if a user wanted to select \tsf{Clothing} but couldn't issue {\D}
 quickly enough, he will see Figure \ref{fig5} instead of Figure \ref{fig7}.
-This is a tradeoff between usability and simplicty, and
+This is a tradeoff between usability and simplicity, and
 the best parameter should be set based on the user and the {\ST} device.
@@
 everyday for watching anime films and listening to music.
-Besides PowerMate, a wireless mouse is preferred,
-since we can carry a wireless mouse anywhere and select
+Besides PowerMate, a wireless mouse is also used,
+since we can carry it anywhere and select
 a film or a music just by rotating the mouse wheel.
 
-We displayed {\ST} at an exhibition
+We demonstrated {\ST} at an exhibition
 held in November 2013, and asked more than 100 people to try it
@@
 Using only one rotating device for data navigation is a new experience for
-all the subjects, but the hard restriction of the device seems to have worked in this case.
+all the subjects, but the hard restriction of the device seemed to have worked in this case.
 
@@
 large hierarchical data structure.
-{\ST} user can easily find an entry in a huge hierarchical database
+A {\ST} user can easily find an entry in a huge hierarchical database
 only by using a rotating input device which can be installed at
-wide range of locations where conventional keybords and switches do not fit.
-We are hoping to try various implementations of {\ST} and try them at
+wide range of locations where conventional keyboards and switches do not fit.
+We are hoping to install various implementations of {\ST} and try them at
 various places like kitchens, restrooms, etc.

### 2014-08-24 paper/UIST2014/paper.tex
moved paper => paper/UIST2014

--- 2014-04-16 paper/paper.tex
@@
 \centerline{\includegraphics[width=80mm,bb=0 0 547 179]{figures/4buttons.png}}
-\caption{4-button controllers on a small mp3 player and AppleRemote.}
+\caption{4-button controllers on a small mp3 player (left) and AppleRemote (right).}
 \label{u10}
@@
 We have developed a new navigation technique and device called ``{\ST}'',
-where users can explore large hierarchical database by simple rotating operations.
+where users can explore a large hierarchical database by simple rotating operations.
 
@@
 
-{\ST}'s behavior is based on the following simple principles.
+Interaction with {\ST} is based on the following simple principles.
 Two types of operations, ``{\U}'' (up) and ``{\D}'' (down), are used for the navigation.
@@
 \begin{enumerate}
-\item A portion of the hierarchical data is listed to the user.
+\item A portion of the hierarchical data is shown to the user.
 
@@
 \centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
-\caption{People trying Strotor at an exhibition.}
+\caption{People at the right trying Strotor at an exhibition.}
 \label{exhibition}

### 2014-08-28 dial.js
added WISS2014

@@ -78,6 +78,7 @@ $.allfocus = function(){
 };
 
 var say = function(node){
+  return;
   text = node.title;
   if(text){
     //if(! node.children){

### 2014-09-17 gear.js
"Dial" を "Gear" に名前変更

@@ -1,5 +1,5 @@
 //
-// dial.js - 回転ダイヤルで階層的コンテンツを閲覧する
+// gear.js - 回転ダイヤルやスイッチで階層的コンテンツを閲覧する
 // (C) 増井俊之 2013/12/1
 // 
 //   http://GitHub.com/masui/Dial
@@ -481,92 +481,3 @@ $(window).keydown(function(e){
   }
   return false;
 });
-
-if(false){
-  //
-  // Linda接続
-  //
-  //var socket = io.connect('http://node-linda-base.herokuapp.com:80');
-  var socket = io.connect(location.protocol + "//" + location.host);
-  var linda = new Linda().connect(socket);
-  var ts = linda.tuplespace('paddle');
-  
-  var direction = 'None';
-  var value = 0;
-  //var step1 = null;
-  
-  var starttime = null;
-  var movetimer = null;  // move()をsetTimeout()で呼ぶ
-  var nexttime = null;   // 次のmove()予定時刻
-  
-  // waitだけ待ってfuncを起動し、その後はintervalごとにfuncを起動
-  function fire(wait,interval,func){
-    ////console.log("filre");
-    //console.log(wait);
-    ////console.log(interval);
-    curtime = new Date();
-    if(wait == 0){
-      func();
-      nexttime = Number(curtime) + interval;
-      movetimer = setTimeout(repeatedfunc(interval,func),interval);
-    }
-    else {
-      nexttime = Number(curtime) + wait;
-      movetimer = setTimeout(repeatedfunc(interval,func),wait);
-    }
-  }
-  
-  var repeatedfunc = function(interval,func){
-    return function(){
-      fire(0,interval,func);
-    };
-  };
-  
-  var movefunc = function(delta){
-    return function(){
-      $.move(delta);
-    };
-  };
-  
-  linda.io.on('connect', function(){
-    ts.watch({type:"paddle"}, function(err, tuple){
-      if(err) return;
-      //window.focus();
-      win.focus();
-      direction = tuple.data['direction'];
-      value = tuple.data['value'];
-      curtime = new Date();
-      clearTimeout(movetimer);
-      if(value < 10){
-        direction = 'None';
-        if(curtime - starttime < 300 && $.step1){ // 1ステップだけ動かす
-          $.refresh();
-          $.calc($.step1);
-        }
-        starttime = null;
-        nexttime = null;
-        $.step1 = null;
-        repcount = 0;
-      }
-      else {
-        // このあたりのパラメタは結構重要
-        var interval = 
[…]

### 2014-09-17 paddle.js

@@ -1,5 +1,5 @@
 //
-// Lindaで受け取った圧力センサ値をもとにしてdial.jsを制御する
+// Lindaで受け取った圧力センサ値をもとにしてgear.jsを制御する
 //
 height = screen.availHeight;
 width = screen.availWidth / 5;

### 2015-06-21 javascripts/gear.js
gear.jsを無理矢理追加

@@ -1,0 +1,620 @@
+// Generated by CoffeeScript 1.7.1
+var AnimationTime, ExpandTime, HideAnimationTime, HideTime, StepTime, autoexpand, browserHeight, calc, dispLine, display, dontShowSingleNode, downfunc, expand, expandTimeout, fire, hashIndex, hideLines, hideTimeout, initData, intValue, json, keydownfunc, linda, loadData, move, movefunc, nasty, nextNode, nodeList, node_app, oldNodeList, oldSpans, pauseAtLevelChange, prevNode, refresh, repeatedfunc, resizefunc, say, sayCGI, setup_paddle, showContents, singleWindow, spans, ts, typeCount, typeCountTimeout, upfunc, useAnimation, useAudio, use_linda;
+
+if (typeof useAnimation === "undefined" || useAnimation === null) {
+  useAnimation = true;
+}
+
+if (typeof showContents === "undefined" || showContents === null) {
+  showContents = true;
+}
+
+if (typeof autoexpand === "undefined" || autoexpand === null) {
+  autoexpand = true;
+}
+
+if (typeof pauseAtLevelChange === "undefined" || pauseAtLevelChange === null) {
+  pauseAtLevelChange = true;
+}
+
+if (typeof dontShowSingleNode === "undefined" || dontShowSingleNode === null) {
+  dontShowSingleNode = true;
+}
+
+if (typeof singleWindow === "undefined" || singleWindow === null) {
+  singleWindow = false;
+}
+
+if (typeof json === "undefined" || json === null) {
+  json = 'data.json';
+}
+
+if (typeof useAudio === "undefined" || useAudio === null) {
+  useAudio = false;
+}
+
+if (typeof sayCGI === "undefined" || sayCGI === null) {
+  sayCGI = "http://localhost/~masui/say.cgi";
+}
+
+node_app = typeof require !== 'undefined';
+
+use_linda = typeof io !== 'undefined';
+
+ts = null;
+
+linda = null;
+
+if (node_app) {
+  singleWindow = true;
+}
+
+nodeList = {};
+
+oldNodeList = {};
+
+spans = {};
+
+oldSpans = {};
+
+StepTime = 1000;
+
+ExpandTime = 1500;
+
+expandTimeout = null;
+
+AnimationTime = 300;
+
+HideTime = 1600;
+
+HideAnimationTime = 700;
+
+hideTimeout = null;
+
+typeCount = 0;
+
+typeCountTimeout = null;
+
[…]

### 2020-02-25 paper/HCC2020/paper.tex
HCC2020追加

--- 2014-08-24 paper/UIST2014/paper.tex
@@
 \newif\ifcover
-
-% \documentstyle[times,chi2003ea]{article}
-% \documentclass[nocopyrightspace,times]{chiproceedings-nospace}
-% \documentclass[nocopyrightspace]{chiproceedings-nospace}
 
@@
 
-\long\def\ST{\textsf{\small{Strotor}}}
+% \long\def\ST{\textsf{\small{Strotor}}}
 \long\def\U{\textsf{\small{U}}}
@@
 \begin{document}
-\title{Strotor: A Minimalistic Approach to \\
-Exploring Hierarchical Data}
+\title{Non-click browsing}
 \author{
@@
 \abstract
-We introduce a new simple information navigation technique
-that enables users to explore large hierarchical data structure
-using only two keys or one rotating device that can generate
-two different signals based on the rotation direction.
+
+We introduce a new simple interaction technique for finding and browsing
+data in a huge hierarchical database using only two keys or
+one rotating device.
+% that can generate two different signals based on the rotation direction.
+
+We can enjoy various kinds of movies, musics, books,
+etc. distribued from many service providers like Amazon and Netflix.
+However, 
+finding a data from the huge database is not a trivial task. Users can
+either find an entry using keywords, or using a menu based
+on a hierarchical structure of the data.
+After successfully finding a candidate data,
+the user should confirm that he wants to watch it by pressing a ``select'' button.
+If the user finds that the data is not the one he wanted,
+he should go back to the previous state and perform the search again.
+
+In the past, when only a small number of ``channels'' were availale
+from broadcast TV stations, the only thing users could do was
+using the ``television dial'' to select a ``channel'' and watch the
+broadcasted data.
+Although the variety of the sources were limited,
+the user interface for selecting a station was simple.
 %
-Using the rotation-based input device called ``\ST'',
-users can find an entry in a huge hierarchical database easily
-only by rotating a disk or a cylinder in two directions.
-%
-{\ST} can be easily installed in sofas, kitchens, cars, etc.
-where standard keyboards and remote controllers do not fit.
+We introduce a simple interaction technique called ``Gear'',
+with which users can select an entry from a very large hiearchial database and
+browse it instantly, just like we could select a channel and enjoyed a TV program
+using old television dials.
 
-\keywords Input device, Information navigation, Hierarchical data
+\keywords Input device, Information navigation, Hierarchical data, Gear, Serencast
 
@@
 
-Large data are often represented as a hierarchical data structure, and
+Large data are often represented as a hierarchical structure, and
 various navigation methods are provided for exploring the data.
@@
 hierarchical data, since the name of the entry can be treated hierarchically:
-e.g. an entry for ``dictionary'' can be stored under ``d'' and ``d/i''.
+e.g. an entry for ``\tsf{dictionary}'' can be stored under ``\tsf{d}'' and ``\tsf{d/i}''.
 
@@
 have been proposed for handling large hierarchical data.
-On personal computers,
+On modern personal computers,
 multiple GUI methods are provided for
@@
 there is no best interaction technique that fits to all the users and situations.
+On MacOS, four GUI methods are provided for browsing the file system.
+
 % there is no single interaction technique that is always good for any situation.
+% ZUIの話, ハイパーリンクでたどる方法もある
 
-When a user cannot use a pointing device,
+When a user cannot use GUI,
 selection-based interaction techniques are used for
@@
 (e.g. selecting an artist from the artist list),
-and often another key is used for selecting an entry and moving to the next level
+and use another key for selecting an entry and moving to the next level
 (e.g. selecting an artist and show album titles).
@@
 (e.g. showing the artist list for artist selection).
-%
 This 4-way navigation is popular on small mp3 players\footnote{
@@
 4-way navigation is also available on desktop software like Finder.app on Mac.
+
+Amazon FireTV
 
@@
 Using 4 keys might be okay on these devices, but it would be much better
-if we could perform the navigation task using only 2 keys.
-In that case, we can use a rotating device like a disk or a cylinder for the navigation,
-since the device can generate 2 signals based on the rotation direction (Figure \ref{rotation}).
+if we could perform the navigation task using simpler dvices that have only 2 keys.
+In that case, we can also use a rotating device like a disk or a wheel for the navigation,
+since such devices can generate 2 signals based on the rotation direction (Figure \ref{rotation}).
 %
@@
 %
-We have developed a new navigation technique and device called ``{\ST}'',
+We have developed a new navigation technique called ``{Gear}'',
 where users can explore a large hierarchical database by simple rotating operations.
-
-% (語源)
-% Navigating large structured data through rotation.
 
@@
 
-Interaction with {\ST} is based on the following simple principles.
+Interaction with Gear is based on the following simple principles.
 Two types of operations, ``{\U}'' (up) and ``{\D}'' (down), are used for the navigation.
-They can be generated either by rotating the {\ST} device or typing a keyboard.
+They can be generated either by rotating the Gear device or typing a keyboard.
 
@@
 or issue {\D} to select the element below the selected element.
-Whenever the selection is changed, 3 is performed.
+Whenever the selection is changed, 3. is performed.
 If the depth of the newly selected element is different from the currently
@@
 \item When a newly selected element has children and the user performs no further action,
-the first child of the selected elemente is newly selected, and 3 is performed.
+the first child of the selected elemente is newly selected, and 3. is performed.
 As a result, all the siblings of the newly selected element
@@
 
-We show how {\ST} works, using a hierarchical data structure of
-the shops list in a shopping mall shown in Figure \ref{fig1} as example data.
-Rectangles with thick border represent categories, and
+We show how Gear works, using a hierarchical data structure of
+a shops list in a shopping mall shown in Figure \ref{fig1} as example data.
+A rectangles with a thick border represent categories, and
 other rectangles represent individual shops.
@@
 
+\section{SERENCAST: A GEAR-BASED BROWSING SERVICE}
+
+% SerencastというサービスでGearを使う
+% SerencastはScrapboxを利用したものである
+
+To prove that Gear can be used for selecting entries from a very
+large hierarchical database,
+we have started the ``\sf{Serencast.com}'' service where
+users can enjoy various contents on the Web using the Gear interface.
+
+誰もがCastできるところがポイント
+RSSもできる
+
+Serencast uses the ``\sf{Scrapbox.io}'' system\footnote{
+  Scrapbox.io
+}for listing data sources.
+Scrapbox is an interactive wiki\footnote{
+ Wikipedia
+}system where users can share and edit texts on the Web among people.
+A user can create a Scrapbox page that consists of texts and links,
+and other people can share the page and edit it freely.
+
+(Figure: Using Scrapbox)
+
+When we list the URLs of existing web pages including
+videos and musics on a Scrapbox page, we can get the list and play the
+data using the Gear interface.  We created the Serencast.com service
+with which we can use the Gear interface to select a program from the
+list on Serencast pages, and automatically play it on the browser.
+
+Figure 1 shows a list of movies on a Scrapbox page.
+[https://gyazo.com/65b01a87b67c9a8e838a047b945f6a77]
+
+When we access the page using Serencast, we get a screen like this.(スクリーン)
+When the user pushes the down key, ...
+In this example, we can select only one of the 10 movies using the Gear interface.
+We can hierarchically construct a list of movies and other programs by using another Scrapbox like this.
+
+By using this technique, we can build a very large hierarchical database for watching movies, videos, etc.
+(figure)
+In this page, over 100,000 Web pages are listed, and we can select one of the programs only by typing up/down keys.
+
+\subsection{Input devices for using Serencast}
+
+ Since only two switches are required for using Gear for Serencast, various kinds of input devices can be used for...
+ We have tried various input devices, and collected experiences.
+
+\paragraph{Rollers}
+  We tried various rotating devices for Gear.
+  Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
+  For example, "jog dials" have been widely used for controlling VCRs, and we tried the device for Gear.
+  We have also tried "rollers" for Gear.
+  After trying these devices, we found that controlling rotating devices are not as easy as we expect, because 肱や腕で細かい操作するのは難しいから.
+  We also tried mouse wheels, and found that mouse wheels are very suitable for using Gear, because 指のコントロールは簡単だから.
+
+\paragraph{Keyboards and buttons}
+  The simplest input device for Gear may be keyboards or buttons.
+  We tried using arrow keys on a PC, and it works fairly fine.
+  We also tried special devices with pressure sensors, with which users can press the button strongly to simulate multiple keyboard presses.
+  Two keys or pressure sensors can be placed anywhere: we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
+
+\paragraph{2-way lever}
+
+We tried a lever with two pressure sensors.
+  モールス用「エレキー」
+  [https://gyazo.com/d64d2a8e1dddc57f693267f811510f23]
+
+ After trying various devices, it became clear that simple buttons or wheels can be put at anywhere like on the table or under a chair, and we felt that the integration of furniture and input devices will be important in the IoT age.
+ If we can put input devices that fits to furnituers, we can use the device near the furniture, without making the input devices look awkward.
+  入力装置つきのカッコ良い家具が作れる
+ If we can put the devices neatlly on furnitures and beds, people with disabilities can easilyt use them, 
+ 体が不自由でも使えることは間違いない
+
+\section{Discussions}
+\subsection{Is the Gear interface a new idea?}
+  Since the idea of Gear interface is so simple, we have been wondering if the same idea had been around in the past.
+  But as far as we know, Gear is the first attempt to explore
+
+ こういうデバイスは超簡単なので、存在した可能性はある
+ 特許や論文を調べた限りはみつけられなかった
+
+\section{Evaluations}
+
+\begin{verbatim}
+実際に家で使っていた
+ 階層構成の問題点はあるが、いろんな階層を用意しておけばいい
+  時間的階層、アーティスト的階層、名前的階層、...
+  それはなんとか対応できることをいう
+   もちろん同時に指定できればいいのだが...
+ 音量とか場所とかは?
+ 名前があるものは必ず階層的に検索できる
+  e.g. 辞書
+\end{verbatim}
+
 \section*{IMPLEMENTATION}
 
-A prototype of {\ST} was built using JavaScript on modern browsers.
+A prototype of Gear was built using JavaScript on modern browsers.
 A large list of news articles, movies, anime films, musics, and e-book titles are listed in one browser window
@@
 to the best of the authors' knowledge,
-{\ST} is the only interaction method for exploring hierarchical data structure
+Gear is the only interaction method for exploring hierarchical data structure
 with one rotating device.
@@
 The behavior is well understood by computer users,
-and {\ST}'s automatic transition (e.g. from Figure \ref{fig4} to Figure \ref{fig5})
+and Gear's automatic transition (e.g. from Figure \ref{fig4} to Figure \ref{fig5})
 looks familiar to users.
@@
 
-It seems to be a good idea to use {\ST} on more conventional visualization techniques like
+It seems to be a good idea to use Gear on more conventional visualization techniques like
 TreeView\footnote{
   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
-}, by replacing 4-way navigation to {\ST}.
+}, by replacing 4-way navigation to Gear.
 
@@
 % is also a ZUI system for handling large hierarchical data,
-% but the same data structure used in LensBar can be used for {\ST}.
+% but the same data structure used in LensBar can be used for Gear.
 % Users can use a pointing devices when it is appropriate,
@@
 
-The biggest disadvantage of {\ST} is that
-the behavior of {\ST} depends on the speed of the user's operations.
+The biggest disadvantage of Gear is that
+the behavior of Gear depends on the speed of the user's operations.
 In Figure \ref{fig4},
@@
 This is a tradeoff between usability and simplicity, and
-the best parameter should be set based on the user and the {\ST} device.
+the best parameter should be set based on the user and the Gear device.
 
@@
 
-No formal evaluation have been done yet, but {\ST} has been used in the author's
+No formal evaluation have been done yet, but Gear has been used in the author's
 living room for six months, and the author's family members are using it
@@
 
-We demonstrated {\ST} at an exhibition
+We demonstrated Gear at an exhibition
 held in November 2013, and asked more than 100 people to try it
@@
 %
-Since the only thing a user can do with {\ST} is to rotate the device,
-users seemed to be able to understand the behavior of {\ST} with trials and errors.
+Since the only thing a user can do with Gear is to rotate the device,
+users seemed to be able to understand the behavior of Gear with trials and errors.
 % 
@@
 
-We have developed a new simple interaction method ``{\ST}'' for exploring
+We have developed a new simple interaction method ``Gear'' for exploring
 large hierarchical data structure.
-A {\ST} user can easily find an entry in a huge hierarchical database
+A Gear user can easily find an entry in a huge hierarchical database
 only by using a rotating input device which can be installed at
 wide range of locations where conventional keyboards and switches do not fit.
-We are hoping to install various implementations of {\ST} and try them at
+We are hoping to install various implementations of Gear and try them at
 various places like kitchens, restrooms, etc.

### 2020-02-27 paper/HCC2020/paper.tex
...

@@
 \usepackage{here} % [H]とするとその場所に配置されるらしい
+
+% \def\up{ \includegraphics[width=3mm,bb=0 0 36 36]{figures/uptriangle.pdf} }
+% \def\down{ \includegraphics[width=3mm,bb=0 0 36 36]{figures/downtriangle.pdf} }
+% \def\right{ \includegraphics[width=3mm,bb=0 0 36 36]{figures/righttriangle.pdf} }
+% \def\left{ \includegraphics[width=3mm,bb=0 0 36 36]{figures/lefttriangle.pdf} }
+\def\up{▲}
+\def\down{▼}
+\def\right{▶}
+\def\left{◀}
 
@@
 Interaction with Gear is based on the following simple principles.
-Two types of operations, ``{\U}'' (up) and ``{\D}'' (down), are used for the navigation.
+Two types of operations, ``{\up}'' (up) and ``{\down}'' (down), are used for the navigation.
 They can be generated either by rotating the Gear device or typing a keyboard.
@@
 
-\item Users can issue {\U} to select the element above the currently selected element,
-or issue {\D} to select the element below the selected element.
+\item Users can issue {\up} to select the element above the currently selected element,
+or issue {\down} to select the element below the selected element.
 Whenever the selection is changed, 3. is performed.
@@
 at the top level are displayed (Figure \ref{fig2}).
-When the user issues {\D},
+When the user issues {\down},
 the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3})\footnote{
@@
 \centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig3.pdf}}
-\caption{Typing {\D}.}
+\caption{Typing {\down}.}
 \label{fig3}
@@
 
-If the user issues {\D} two more times, 
+If the user issues {\down} two more times, 
 \tsf{Food/drink} category is selected (Figure \ref{fig4}).
@@
 
-When the user issues {\D} twice here,
+When the user issues {\down} twice here,
 \tsf{Fresh grocery} category is selected (Figure \ref{fig6}).
@@
 
-If the user keeps issuing {\D}, 
+If the user keeps issuing {\down}, 
 the list will change to Figure \ref{fig8},
@@
 
-If the use stops issuing {\D} at Figure \ref{fig6},
+If the use stops issuing {\down} at Figure \ref{fig6},
 the shops under category \tsf{Fresh grocery} is automatically selected (Figure \ref{fig7}).
@@
 
-When the user issues {\U} here, \tsf{Fresh grocery} is selected,
+When the user issues {\up} here, \tsf{Fresh grocery} is selected,
 and the shops under \tsf{Fresh grocery} disappears, 
 resulting in the same state as Figure \ref{fig6}.
-If the user issues {\U} two more times, the display changes to the state
+If the user issues {\up} two more times, the display changes to the state
 shown in Figure \ref{fig5},
-and one more {\U} will set the system to the state of Figure \ref{fig4}.
+and one more {\up} will set the system to the state of Figure \ref{fig4}.
 
-If the user issues {\D} in Figure \ref{fig4}, the next visible entry
+If the user issues {\down} in Figure \ref{fig4}, the next visible entry
 (\tsf{Clothing}) is selected (Figure \ref{fig8}), and then the state changes to Figure \ref{fig9}.
@@
 
-When the user issues {\D} twice in Figure \ref{fig7},
+When the user issues {\down} twice in Figure \ref{fig7},
 \tsf{Clothing} is selected, and the category under \tsf{Food/drink} will shrinke (Figure \ref{fig8}).
@@
 In this way, users can explore the hierarchical structure
-only by issuing {\U} and {\D} at the right timing.
+only by issuing {\up} and {\down} at the right timing.
 
@@
 large hierarchical database,
-we have started the ``\sf{Serencast.com}'' service where
-users can enjoy various contents on the Web using the Gear interface.
+we have started the ``\tsf{Serencast.com}'' service, where
+users can enjoy videos, musics, and other Web pages
+on the browser with the Gear interface.
 
-誰もがCastできるところがポイント
-RSSもできる
+Serencast uses the ``\tsf{Scrapbox.io}'' wiki service\footnote{
+  \tsf{https://Scrapbox.io/}
+} for listing the contents of the hierarchical database.
+Scrapbox is an interactive wiki\footnote{
+  \tsf{https://en.wikipedia.org/wiki/Wiki}
+} system where users can share and edit texts on the Web.
+A user can create a Scrapbox ``project'', and create pages
+that consists of texts and links,
+and people can share the page and edit it freely on their browsers.
 
-Serencast uses the ``\sf{Scrapbox.io}'' system\footnote{
-  Scrapbox.io
-}for listing data sources.
-Scrapbox is an interactive wiki\footnote{
- Wikipedia
-}system where users can share and edit texts on the Web among people.
-A user can create a Scrapbox page that consists of texts and links,
-and other people can share the page and edit it freely.
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 1553 1174]{figures/28818d749896f87f3eb8bd6b6f9e9a36.png}}
+\caption{An example of a Scrapbox project.}
+\label{exampleproject}
+\end{figure}
 
-(Figure: Using Scrapbox)
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 1606 1200]{figures/9e867c325bafc415bd0870c1717fbaf7.png}}
+\caption{An example Scrapbox page.}
+\label{examplepage}
+\end{figure}
 
-When we list the URLs of existing web pages including
-videos and musics on a Scrapbox page, we can get the list and play the
-data using the Gear interface.  We created the Serencast.com service
-with which we can use the Gear interface to select a program from the
+The page is based on plain text, and users can use special markup tags
+like ``\texttt{[}'' and ``\texttt{]}'' to display bold texts, icons, URL links,
+and links to other pages.
+In this example, a URL link to \textsf{http://gyazo.com} is used
+just like \textsf{A} tags in HTML.
+
+{\scriptsize
+\begin{verbatim}
+Features
+(The [Check.icon] means we believe this feature is unique \
+ toScrapbox among competing services.)
+
+[[Easy to use Gyazo images]]
+ By using together with [Gyazo https://gyazo.com] you can \
+ surprisingly paste any image onto the page, and it \
+ displays instantly.
+
+[Check.icon] [[Use of an [image] to represent pages]]
+ By attaching images to each page, it is easier to discover \
+and remember them. Our method allows visual organization to \
+happen spontanteously.
+\end{verbatim}
+}
+
+When we list the URLs of Web pages of
+videos and musics on a Scrapbox page,
+we can create a hierarchical structure from the list and
+use the Gear interface to find data and browse it.
+We can use Serencast.com service
+for using the Gear interface to select a program from the
 list on Serencast pages, and automatically play it on the browser.
 
-Figure 1 shows a list of movies on a Scrapbox page.
-[https://gyazo.com/65b01a87b67c9a8e838a047b945f6a77]
+Figure \ref{movielist} shows a Scrapbox page listing movies.
 
-When we access the page using Serencast, we get a screen like this.(スクリーン)
-When the user pushes the down key, ...
-In this example, we can select only one of the 10 movies using the Gear interface.
-We can hierarchically construct a list of movies and other programs by using another Scrapbox like this.
+\begin{figure}[H]
+% \centerline{\includegraphics[width=40mm,bb=0 0 417 619]{figures/2690db244045aa809a3e2fc2b40ba0a3.png}}
+\centerline{\includegraphics[width=40mm,bb=0 0 387 568]{figures/2b97930bf5730fcaf4d9c0adeb9c5f6e.png}}
+\caption{Movie list.}
+\label{movielist}
+\end{figure}
 
-By using this technique, we can build a very large hierarchical database for watching movies, videos, etc.
-(figure)
-In this page, over 100,000 Web pages are listed, and we can select one of the programs only by typing up/down keys.
+The raw text of this page looks like this.
 
-\subsection{Input devices for using Serencast}
+{\scriptsize
+\begin{verbatim}
+Movies
+ [https://www.netflix.com/watch/70105600 Gran Torino]
+ [https://www.netflix.com/watch/80047616 My Intern]
+ [https://www.netflix.com/watch/330201 Breakfast at Tiffany's]
+ [https://www.netflix.com/watch/70080178 Heroes]
+ [https://www.netflix.com/watch/70174781 Sherlock]
+ [https://www.happyon.jp/watch/100048550 Mad Max]
+ [https://www.netflix.com/watch/60010351 Flashcance]
+ [https://www.netflix.com/watch/80095365 La La Land]
+ [https://www.netflix.com/watch/81191988 Don't stop the camera]
+ [https://youtube.com/embed/AtZr9g2vwrI?autoplay=1 Fireplace]
+\end{verbatim}}
 
- Since only two switches are required for using Gear for Serencast, various kinds of input devices can be used for...
+\begin{figure}[H]
+% \centerline{\includegraphics[width=80mm,bb=0 0 524 598]{figures/65b01a87b67c9a8e838a047b945f6a77.png}}
+\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
+\caption{Showing a movie.}
+\label{tiffany}
+\end{figure}
+
+When we access the Scrapbox page from Serencast,
+``Gran Trino'' from Netflix automatically starts in the right side of the screen,
+just like a TV program starts when we rotate tha channel dial of an old TV.
+When the user pushes the {\down} key twice,
+``Breakfast at Tiffarny's'' is selected and
+the movie starts at the right side of the screen. (Figure \ref{tiffany})
+
+In the above example, we can select only one of the 10 movies using the Gear interface.
+We can add more data by hierarchically proiding the contents of Scrapbox pages.
+
+In one page, we can specify a hierarchical structure by using indentations.
+Figure \ref{musiclist} shows a portion of a list of CDs and
+musics titles by Weather Report and Wes Montgomery are shown.
+For example, 
+``Black Market'' is the first music title in the album ``8:30'' of Weather Report, and
+the tune ``Scarlet Woman'' follows ``Black Market''.
+``Wes Montgomery'' is listed in the same layer as ``Weather Report'', and
+the album ``Tequilla'' is listed below the level.
+
+\begin{figure}[H]
+% \centerline{\includegraphics[width=40mm,bb=0 0 596 808]{figures/6657544cf60cbf0aea91ba7da0455b90.png}}
+\centerline{\includegraphics[width=40mm,bb=0 0 652 926]{figures/d8fe8ff8f3e1bbcb34cf51e268592f8c.png}}
+\caption{Music list.}
+\label{musiclist}
+\end{figure}
+
+The title of this Scrapbox page is ``Music'', and 
+we can collect Movie page, Music page, and other pages by
+listing them in another page (``Top'' page, in this case).
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=40mm,bb=0 0 396 523]{figures/8a8e4d63b75183f1b4d0ed4db733f500.png}}
+\caption{Top page.}
+\label{top}
+\end{figure}
+
+Many pages (Music, Movies, etc.) are listed below the Top page, and
+the pages are treated as children pages of the Top page.
+By constructing data hierarchically like this,
+We can build a very large hierarchical database for watching movies, videos, etc.
+As many as 100,000 pages can be put on a hierarchical Scrapbox pages, and
+we can select one of the entries only by using only {\up} and {\down} keys.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackmarket.png}}
+\caption{Playing a music.}
+\label{blackmarket}
+\end{figure}
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackjack.png}}
+\caption{Reading a comicbook.}
+\label{blackjack}
+\end{figure}
+
+Since anybody can edit the Scrapbox page and construct the hierarchical data,
+people can enjoy creating his own data by editing his Scrapbox pages.
+Also, people who want to distribute their works,
+they can create their Scrapbox page
+and give it to others so that other people can include the page and
+enjoy it by using Gear.
+
+\section{DISCUSSIONS}
+
+\subsection{Input devices for Gear}
+
+Since only two switches are required,
+various kinds of input devices can be used for Gear.
 We have tried various input devices, and collected experiences.
 
-\paragraph{Rollers}
+\paragraph{Keys and buttons}
+
+We can use two arrow keys on a computer for using Serencast.
+
+キーリピートも良い
+
+\paragraph{Rotating devices}
+
 We tried various rotating devices for Gear.
 Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
-  For example, "jog dials" have been widely used for controlling VCRs, and we tried the device for Gear.
+For example, ``jog dials''ave been widely used for controlling VCRs, and we tried the device for Gear.
+
 We have also tried "rollers" for Gear.
-  After trying these devices, we found that controlling rotating devices are not as easy as we expect, because 肱や腕で細かい操作するのは難しいから.
-  We also tried mouse wheels, and found that mouse wheels are very suitable for using Gear, because 指のコントロールは簡単だから.
+After trying these devices, we found that controlling rotating devices are not as easy as we expect,
+because presice control of a hand is fairly difficult.
+People are good at controling fingers, but people are usually not very good at controlling hands.
+
+We also tried mouse wheels, and found that mouse wheels are very suitable for using Gear, because
+we are good at presice control of our fingers.
+
+We can use a rotary encoder as a
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
+\caption{回転板デバイス}
+\label{disk}
+\end{figure}
+
+We used
+PowerMate\footnote{
+  \textsf{http://griffintechnology.com/support/powermate}
+} from Griffin Technology for the rotating device.
+PowerMate generates standard keyboard events when rotated,
+and no special programming techniques are required.
+%
+Users can explore all the contents just by
+rotating the device clockwise and counterclockwise.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=30mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
+\caption{A PowerMate used for the prototype.}
+\label{powermate}
+\end{figure}
 
@@
 モールス用「エレキー」
-  [https://gyazo.com/d64d2a8e1dddc57f693267f811510f23]
+Puddle
 
- After trying various devices, it became clear that simple buttons or wheels can be put at anywhere like on the table or under a chair, and we felt that the integration of furniture and input devices will be important in the IoT age.
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 1200 799]{figures/d64d2a8e1dddc57f693267f811510f23.jpg}}
+\caption{Elekey.}
+\label{elekey}
+\end{figure}
+
+図\ref{paddle}は，
+パドルに貼った2個の圧力センサの値を{\up}{\down}に割り当てている．
+
+\begin{figure}[H]
+  \centerline{\includegraphics[width=54mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
+\caption{左右にはじく「パドル」デバイス}
+\label{paddle}
+\end{figure}
+
+After trying various devices, it became clear that simple buttons or
+wheels can be put at anywhere like on the table or under a chair, and
+we felt that the integration of furniture and input devices will be
+important in the IoT age.
+
 If we can put input devices that fits to furnituers, we can use the device near the furniture, without making the input devices look awkward.
@@
 A prototype of Gear was built using JavaScript on modern browsers.
+
 A large list of news articles, movies, anime films, musics, and e-book titles are listed in one browser window
@@
 \label{screenshot}
-\end{figure}
-
-We used
-PowerMate\footnote{
-  \textsf{http://griffintechnology.com/support/powermate}
-} from Griffin Technology for the rotating device.
-PowerMate generates standard keyboard events when rotated,
-and no special programming techniques are required.
-%
-Users can explore all the contents just by
-rotating the device clockwise and counterclockwise.
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=30mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
-\caption{A PowerMate used for the prototype.}
-\label{powermate}
 \end{figure}
@@
 In Figure \ref{fig4},
-if a user wanted to select \tsf{Clothing} but couldn't issue {\D}
+if a user wanted to select \tsf{Clothing} but couldn't issue {\down}
 quickly enough, he will see Figure \ref{fig5} instead of Figure \ref{fig7}.

### 2020-02-27 paper/HCC2020/paper.tex
...

@@
 
+\def\SC{\textsf{\small Serencast}}
+\def\SB{\textsf{\small Scrapbox}}
+
 \usepackage{graphicx}
@@
 
-We introduce a new simple interaction technique for finding and browsing
+We introduce a novel simple interaction technique for finding and browsing
 data in a huge hierarchical database using only two keys or
@@
 either find an entry using keywords, or using a menu based
-on a hierarchical structure of the data.
+on a hierarchical structure of the database.
 After successfully finding a candidate data,
@@
 broadcasted data.
-Although the variety of the sources were limited,
+Although the number of the sources were limited,
 the user interface for selecting a station was simple.
@@
 with which users can select an entry from a very large hiearchial database and
-browse it instantly, just like we could select a channel and enjoyed a TV program
+browse it instantly, just like we could select a channel and enjoy a TV program
 using old television dials.
@@
 For example, files on Unix are structured hierarchically, and
-various commands (\tsf{cd}, \tsf{ls}, etc.) and APIs are provided for exploring the file system.
+many commands (\tsf{cd}, \tsf{ls}, etc.) and APIs are provided for exploring the file system.
 Large dictionary database can also be treated as a large
 hierarchical data, since the name of the entry can be treated hierarchically:
-e.g. an entry for ``\tsf{dictionary}'' can be stored under ``\tsf{d}'' and ``\tsf{d/i}''.
+e.g. an entry for ``\tsf{dictionary}'' can be stored under ``\tsf{d}'', ``\tsf{d/i}'', and so on.
 
@@
 On modern personal computers,
-multiple GUI methods are provided for
+multiple GUI techniques are provided for
 exploring the hierarchical file structure, because
@@
 
-Amazon FireTV
+% Amazon FireTV
 
@@
 \section*{NAVIGATION METHOD AND EXAMPLES}
+\label{navigation}
 
@@
 Two types of operations, ``{\up}'' (up) and ``{\down}'' (down), are used for the navigation.
-They can be generated either by rotating the Gear device or typing a keyboard.
+They can be performed either by rotating the Gear device or pressing keys.
 
 \begin{enumerate}
-\item A portion of the hierarchical data is shown to the user.
+\item A portion of the hierarchical data is shown to the user as a list.
 
@@
 a shops list in a shopping mall shown in Figure \ref{fig1} as example data.
-A rectangles with a thick border represent categories, and
+A rectangles with a thick border represent shop categories, and
 other rectangles represent individual shops.
@@
 When the user issues {\down},
-the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3})\footnote{
-  Readers can try this at \textsf{http://jsbin.com/lecuroku}.
-}.
+the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3}).
+
+\def\menuwidth{22mm}
 
 \begin{figure}[H]
-\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig2.pdf}}
+\centerline{\includegraphics[width=\menuwidth, bb=0 0 139 157]{figures/fig2.pdf}}
 \caption{Initial display.}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig3.pdf}}
+\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 157]{figures/fig3.pdf}}
 \caption{Typing {\down}.}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig4.pdf}}
+\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 157]{figures/fig4.pdf}}
 \caption{Selecting Food/drink.}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=24mm,bb=0 0 139 238]{figures/fig5.pdf}}
+\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 238]{figures/fig5.pdf}}
 \caption{Selecting Liquor shop.}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=24mm,bb=0 0 139 238]{figures/fig6.pdf}}
+\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 238]{figures/fig6.pdf}}
 \caption{Selecting Fresh grocery.}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=24mm,bb=0 0 139 157]{figures/fig8.pdf}}
+\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 157]{figures/fig8.pdf}}
 \caption{Selecting Clothing.}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=24mm,bb=0 0 139 292]{figures/fig7.pdf}}
+\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 292]{figures/fig7.pdf}}
 \caption{Selecting Fish store.}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=24mm,bb=0 0 139 211]{figures/fig9.pdf}}
+\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 211]{figures/fig9.pdf}}
 \caption{Selecting Shoes store.}
@@
 
-\section{SERENCAST: A GEAR-BASED BROWSING SERVICE}
+\section{SERENCAST: A NON-CLICK BROWSING SERVICE}
 
@@
 
-To prove that Gear can be used for selecting entries from a very
+To prove that Gear is useful for selecting an entry from a very
 large hierarchical database,
-we have started the ``\tsf{Serencast.com}'' service, where
-users can enjoy videos, musics, and other Web pages
+we have developed the ``\tsf{Serencast.com}'' service, where
+users can enjoy movies, musics, and other Web services
 on the browser with the Gear interface.
 
-Serencast uses the ``\tsf{Scrapbox.io}'' wiki service\footnote{
+{\SC} uses the ``\tsf{Scrapbox.io}'' wiki service\footnote{
   \tsf{https://Scrapbox.io/}
 } for listing the contents of the hierarchical database.
-Scrapbox is an interactive wiki\footnote{
+{\SB} is an interactive wiki\footnote{
   \tsf{https://en.wikipedia.org/wiki/Wiki}
-} system where users can share and edit texts on the Web.
-A user can create a Scrapbox ``project'', and create pages
+} system where users can share and edit texts on the Web browser.
+A user can create a {\SB} ``project'', and create pages
 that consists of texts and links,
@@
 \centerline{\includegraphics[width=80mm,bb=0 0 1553 1174]{figures/28818d749896f87f3eb8bd6b6f9e9a36.png}}
-\caption{An example of a Scrapbox project.}
+\caption{An example of a {\SB} project.}
 \label{exampleproject}
@@
 
+Figure \ref{exampleproject} shows an example of a {\SB} project.
+The title of the project is ``Scrapbox help'', and
+many pages like ``Features'' exist inthe project.
+
 \begin{figure}[H]
 \centerline{\includegraphics[width=80mm,bb=0 0 1606 1200]{figures/9e867c325bafc415bd0870c1717fbaf7.png}}
-\caption{An example Scrapbox page.}
+\caption{An example {\SB} page.}
 \label{examplepage}
@@
 
-The page is based on plain text, and users can use special markup tags
-like ``\texttt{[}'' and ``\texttt{]}'' to display bold texts, icons, URL links,
+Figure \ref{examplepage} is an example of a {\SB} page.
+%
+The page is based on plain text just like an WikiPedia page is based on plain text.
+Users can use special markup tags
+like ``\texttt{[}'' and ``\texttt{]}'' to show bold texts, icons, URL links,
 and links to other pages.
-In this example, a URL link to \textsf{http://gyazo.com} is used
-just like \textsf{A} tags in HTML.
+In this example, a URL link to {\tsf{http://gyazo.com}} is used
+just like \tsf{A} tags used in HTML.
+
+The raw text of the {\SB} page looks like this:
 
@@
 (The [Check.icon] means we believe this feature is unique \
- toScrapbox among competing services.)
+ to {\SB} among competing services.)
 
@@
 When we list the URLs of Web pages of
-videos and musics on a Scrapbox page,
+movies and musics on a {\SB} page,
 we can create a hierarchical structure from the list and
 use the Gear interface to find data and browse it.
-We can use Serencast.com service
+We can use \tsf{Serencast.com} service
 for using the Gear interface to select a program from the
-list on Serencast pages, and automatically play it on the browser.
+list on {\SC} pages, and automatically play it on the browser.
 
-Figure \ref{movielist} shows a Scrapbox page listing movies.
+Figure \ref{movielist} shows the movie list defined in a {\SB} page.
 
@@
 
-The raw text of this page looks like this.
+The raw text of this page is shown below:
 
@@
 
-When we access the Scrapbox page from Serencast,
+When we access the {\SB} page from {\SC},
 ``Gran Trino'' from Netflix automatically starts in the right side of the screen,
-just like a TV program starts when we rotate tha channel dial of an old TV.
+just like a TV program starts when we rotate tha channel dial of an old television.
 When the user pushes the {\down} key twice,
@@
 In the above example, we can select only one of the 10 movies using the Gear interface.
-We can add more data by hierarchically proiding the contents of Scrapbox pages.
+But we can add more data by hierarchically providing more contents in {\SB} pages.
 
@@
 Figure \ref{musiclist} shows a portion of a list of CDs and
-musics titles by Weather Report and Wes Montgomery are shown.
+musics titles by ``Weather Report'' and ``Wes Montgomery'' are shown\footnote{
+  Weather Report is the name of a famous Jazz group, and Wes Montgomery is a famous Jazz guitarist.
+}.
 For example, 
-``Black Market'' is the first music title in the album ``8:30'' of Weather Report, and
-the tune ``Scarlet Woman'' follows ``Black Market''.
+``Black Market'' is the first title in the album ``8:30'' of ``Weather Report'', and
+``Scarlet Woman'' follows ``Black Market''.
 ``Wes Montgomery'' is listed in the same layer as ``Weather Report'', and
-the album ``Tequilla'' is listed below the level.
+the album ``Tequilla'' is listed one level below the level of the name of the artist.
 
@@
 
-The title of this Scrapbox page is ``Music'', and 
+The title of this {\SB} page is ``Music'', and 
 we can collect Movie page, Music page, and other pages by
@@
 
-Many pages (Music, Movies, etc.) are listed below the Top page, and
+Many pages (Music, Movies, etc.) are listed in the Top page, and
 the pages are treated as children pages of the Top page.
 By constructing data hierarchically like this,
-We can build a very large hierarchical database for watching movies, videos, etc.
-As many as 100,000 pages can be put on a hierarchical Scrapbox pages, and
-we can select one of the entries only by using only {\up} and {\down} keys.
+We can build a very large hierarchical database for watching movies, videos, news, etc.
+A hierarchical database with
+As many as 100,000 pages can be easily constructed on a {\SB} pages, and
+we can select one of the entries only by using only {\up} and {\down} keys,
+using the Gear technique described in section \ref{navigation}.
 
@@
 
-Since anybody can edit the Scrapbox page and construct the hierarchical data,
-people can enjoy creating his own data by editing his Scrapbox pages.
-Also, people who want to distribute their works,
-they can create their Scrapbox page
-and give it to others so that other people can include the page and
-enjoy it by using Gear.
+Since anybody can edit the {\SB} page and construct the hierarchical data,
+people can enjoy creating their own data by editing their {\SB} pages.
+Also, when people who want to advertise their works,
+they can create their {\SB} page
+and give it to others so that other people can include the page
+in their list and enjoy it using Gear.
 
@@
 
-Since only two switches are required,
+Since only two switches are required in the Gear interface,
 various kinds of input devices can be used for Gear.
@@
 
-We can use two arrow keys on a computer for using Serencast.
+The simplest input device for Gear may be keyboards or buttons.
+We tried using arrow keys on a PC, and it works fairly fine.
+We also tried special devices with pressure sensors, with which users can press the button strongly to simulate multiple keyboard presses.
+Two keys or pressure sensors can be placed anywhere: we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
 
-キーリピートも良い
+We can use two arrow keys on a computer keyboard for using {\SC}.
+It works fine, but Gear is not more useful than using many keys on a computer.
+%
+Good thing is that many keyboard devices are available for personal computers,
+and we can use such devices for using Gear.
+
+% キーリピート
 
@@
 For example, ``jog dials''ave been widely used for controlling VCRs, and we tried the device for Gear.
+
+(figure)
 
@@
 
-\paragraph{Keyboards and buttons}
-  The simplest input device for Gear may be keyboards or buttons.
-  We tried using arrow keys on a PC, and it works fairly fine.
-  We also tried special devices with pressure sensors, with which users can press the button strongly to simulate multiple keyboard presses.
-  Two keys or pressure sensors can be placed anywhere: we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
-
 \paragraph{2-way lever}
 
+We have also tried to use a paddle-like device for generating {\U} and {\D}.
+Users can push the puddle to the right to generate {\U} and
+left to generate {\D}.
+Pressure sensors are installed on the puddle, and
+many {\U}s are generated when the user pushs the puddle strongly.
+
+\begin{figure}[H]
+  \centerline{\includegraphics[width=54mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
+\caption{Paddle device for Gear.}
+\label{paddle}
+\end{figure}
+
+Controling the speed of the scrolling of Gear by pressure is convenient,
+since sometimes users want to jump to a far entry from current position.
+That behavior is close to the key-repeat feature or computer keyboards.
+
+\comment{
 We tried a lever with two pressure sensors.
@@
 
-図\ref{paddle}は，
-パドルに貼った2個の圧力センサの値を{\up}{\down}に割り当てている．
-
-\begin{figure}[H]
-  \centerline{\includegraphics[width=54mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
-\caption{左右にはじく「パドル」デバイス}
-\label{paddle}
-\end{figure}
+}
 
@@
 \section{Discussions}
+
 \subsection{Is the Gear interface a new idea?}
@@
 
-A prototype of Gear was built using JavaScript on modern browsers.
+{\SC} is built using JavaScript on modern browsers.
 
@@
 \end{document}
+
+Non-click browsingの威力
+  ストレスが全然違う
+音声を使う
+満員電車で使える
+速度
+  log(n)
+時計のセットとか

### 2020-02-28 paper/HCC2020/paper.tex
...
time-enoshima.html追加

@@
 on the browser with the Gear interface.
+{\SC} is implemented in JavaScript, and runs on modern browsers
 
@@
 and we can use such devices for using Gear.
-
-% キーリピート
+``Key-repeat'' feature is useful for fast scrolling of the menu.
 
@@
 \centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
-\caption{回転板デバイス}
+\caption{A disk-based device for Gear.}
 \label{disk}
@@
 
-\section{Discussions}
-
-\subsection{Is the Gear interface a new idea?}
-  Since the idea of Gear interface is so simple, we have been wondering if the same idea had been around in the past.
-  But as far as we know, Gear is the first attempt to explore
-
- こういうデバイスは超簡単なので、存在した可能性はある
- 特許や論文を調べた限りはみつけられなかった
-
-\section{Evaluations}
-
-\begin{verbatim}
-実際に家で使っていた
- 階層構成の問題点はあるが、いろんな階層を用意しておけばいい
-  時間的階層、アーティスト的階層、名前的階層、...
-  それはなんとか対応できることをいう
-   もちろん同時に指定できればいいのだが...
- 音量とか場所とかは?
- 名前があるものは必ず階層的に検索できる
-  e.g. 辞書
-\end{verbatim}
-
+\comment{
 \section*{IMPLEMENTATION}
-
-{\SC} is built using JavaScript on modern browsers.
 
@@
 \end{figure}
+}
 
@@
 
+\section{Discussions}
+
+\subsection{Is the Gear interface a new idea?}
+  Since the idea of Gear interface is so simple, we have been wondering if the same idea had been around in the past.
+  But as far as we know, Gear is the first attempt to explore
+
+ こういうデバイスは超簡単なので、存在した可能性はある
+ 特許や論文を調べた限りはみつけられなかった
+
 \section*{EVALUATION}
+
+\begin{verbatim}
+実際に家で使っていた
+ 階層構成の問題点はあるが、いろんな階層を用意しておけばいい
+  時間的階層、アーティスト的階層、名前的階層、...
+  それはなんとか対応できることをいう
+   もちろん同時に指定できればいいのだが...
+ 音量とか場所とかは?
+ 名前があるものは必ず階層的に検索できる
+  e.g. 辞書
+\end{verbatim}
 
@@
 \centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
-\caption{People at the right trying Strotor at an exhibition.}
+\caption{People at the right using {\SC} at an exhibition.}
 \label{exhibition}
@@
   log(n)
-時計のセットとか
+時刻のセットとか
+
+ザッピングの研究はあるか

### 2020-02-28 serendata/bijin.rb

@@ -1,0 +1,14 @@
+#
+# 美人時計をSerencastで観賞する
+#
+(0..23).each { |h|
+  hh = sprintf("%02d",h)
+  puts " #{hh}:--"
+  (0..5).each { |m1|
+    puts "  #{hh}:#{m1}-"
+    (0..9).each { |m2|
+      puts "   [#{hh}:#{m1}#{m2} http://www.bijint.com/assets/pict/jp/pc/#{hh}#{m1}#{m2}.jpg]"
+    }
+  }
+}
+

### 2020-02-29 serendata/enoden.rb
serendata追加

@@ -1,0 +1,17 @@
+#
+# 美人時計をSerencastで観賞する
+#
+i = 1
+(0..23).each { |m|
+  mm = sprintf("%02d",m)
+  puts " #{mm}:--"
+  (0..5).each { |s1|
+    puts "  #{mm}:#{s1}-"
+    (0..9).each { |s2|
+      id = sprintf("%04d",i)
+      puts "   [#{mm}:#{s1}#{s2} http://pitecan.com/enoden/enoden#{id}.jpg]"
+      i += 1
+    }
+  }
+}
+

### 2020-02-29 serendata/monorail.rb
...

@@ -1,0 +1,17 @@
+#
+# モノレールをSerencastで観賞する
+#
+i = 1
+(0..14).each { |m|
+  mm = sprintf("%02d",m)
+  puts " #{mm}:--"
+  (0..5).each { |s1|
+    puts "  #{mm}:#{s1}-"
+    (0..9).each { |s2|
+      id = sprintf("%04d",i)
+      puts "   [#{mm}:#{s1}#{s2} http://pitecan.com/monorail/monorail#{id}.jpg]"
+      i += 1
+    }
+  }
+}
+

### 2020-02-29 serendata/monorail.rb
...

@@ -1,16 +1,16 @@
 #
 # モノレールをSerencastで観賞する
 #
-i = 1
 (0..14).each { |m|
   mm = sprintf("%02d",m)
-  puts " #{mm}:--"
+  id = sprintf("%04d",m*60+1)
+  puts " [#{mm}:-- http://pitecan.com/monorail/monorail#{id}.jpg]"
   (0..5).each { |s1|
-    puts "  #{mm}:#{s1}-"
+    id = sprintf("%04d",m*60+s1*10+1)
+    puts "  [#{mm}:#{s1}-- http://pitecan.com/monorail/monorail#{id}.jpg]"
     (0..9).each { |s2|
-      id = sprintf("%04d",i)
+      id = sprintf("%04d",m*60+s1*10+s2+1)
       puts "   [#{mm}:#{s1}#{s2} http://pitecan.com/monorail/monorail#{id}.jpg]"
-      i += 1
     }
   }
 }

### 2020-03-02 paper/HCC2020/timeset-mac.rb
...

@@ -1,0 +1,23 @@
+require 'io/console'
+
+def randTime()
+  t = rand(867)
+  min = t / 60
+  sec = ("0" + (t % 60).to_s)[-2,2]
+  "#{min}:#{sec}"
+end
+
+start = Time.now.to_f
+
+i = 0
+puts randTime
+while (key = STDIN.getch)
+  i +=1
+  if i < 5
+    puts randTime
+  elsif i == 5
+    time = Time.now.to_f - start
+    puts time / 5
+    exit
+  end
+end

### 2020-03-02 serendata/monorail.rb

@@ -4,10 +4,10 @@
 (0..14).each { |m|
   mm = sprintf("%02d",m)
   id = sprintf("%04d",m*60+1)
-  puts " [#{mm}:-- http://pitecan.com/monorail/monorail#{id}.jpg]"
+  puts " [#{mm}:00 http://pitecan.com/monorail/monorail#{id}.jpg]"
   (0..5).each { |s1|
     id = sprintf("%04d",m*60+s1*10+1)
-    puts "  [#{mm}:#{s1}-- http://pitecan.com/monorail/monorail#{id}.jpg]"
+    puts "  [#{mm}:#{s1}0 http://pitecan.com/monorail/monorail#{id}.jpg]"
     (0..9).each { |s2|
       id = sprintf("%04d",m*60+s1*10+s2+1)
       puts "   [#{mm}:#{s1}#{s2} http://pitecan.com/monorail/monorail#{id}.jpg]"

### 2020-03-04 paper/HCC2020/paper.tex
...

@@
 
-Large data are often represented as a hierarchical structure, and
+\begin{verbatim}
+Macのファインダでは最下層ではザッピングができる
+/ no-clickブラウジングができてて便利
+カバーフローでザッピングできるし、ファイルを選択すると
+中身が右に見える。。。これはno-clickブラウジングである
+しかし階層を上下することはできないし、
+沢山ファイルがあるとザッピングできない
+\end{verbatim}
+
+% 大量のコンテンツから見たいものを捜して再生するのは大変である
+% 
+% 1. 階層から捜すのが大変
+% 2. みつけたものをConfirmする手間がいる
+
+Huge amount of movies, musics, and documents are available on the web, but
+viewing a content usually takes time because
+(1) finding a content is difficult, and
+(2) a ``confirm'' operation is required for viewing.
+
+% 昔のテレビやラジオではこの手間がなかった
+% チャンネルやチューニングつまみを回すだけでよかった
+% 選択操作はなかった
+% つまりいわゆる「ザッピング」が可能であった
+
+The confirm operations were not required on old TVs and radios,
+because we could enjoy the TV and radio program
+as soon as we rotated a ``TV channel'' or a tuning dial of the radio.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 279 272]{figures/9bd96506bdaac48b26c5cd192851c11d.png}}
+\caption{A TV channel}
+\label{TV channel}
+\end{figure}
+
+% 一般に、選択するとすぐに見えるのはどこでも便利なものである
+% Finderのカバーフローや、最下層では選択内容がすぐに見えたりする
+% このときはConfirmの手間なく内容を見られるのは便利なもので、
+% これをno-click browsingと呼ぶことにする
+% TVもラジオもno-click browsingが可能であった
+
+It is always convenient to see the contents of the selected item
+as soon as we select the item.
+We'd like to call this viewing style as ``no-click browsing''.
+We could enjoy no-click browsing on old TVs and radios, but we can
+also use the style on modern personal computers.
+On the ``\tsf{Finder.app}'' program on MacOS, we can use the ``CoverFlow'' mode to browse
+the contents with simple swyping gestures.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
+\caption{Cover Flow}
+\label{coverflow}
+\end{figure}
+
+We can also enjoy no-click browsing on finder windows see the contents of files when ....
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
+\caption{No-click browsing on conventinal Finder mode}
+\label{coverflow}
+\end{figure}
+
+% テレビやカバーフローのザッピングはもちろんソースが少なかったからできるわけだが、
+% 大量データの場合はこれが難しい。
+
+We could enjoy no-click browsing on TVs and radios because the number of
+sources are limited.
+Likely, we can enjoy no-click browsing on the Finder.app when the number of files
+in one directory is not too big.
+
+何千個もソースがある場合は
+階層をたどる処理が必要になり、その移動操作が必要だからである
+
+階層でもそうでなくても、移動操作は慣れている
+適切な階層構造を用意して、クリックしながらたどるのがブラウザでは一般的である
+ブラウザの場合、カバーフローのようなインタフェースは一般的でないので、
+みつけたものを選択したり戻ったりを繰り返さなければならない。
+
+ブラウザでは階層のInfoVis[]もいろいろあるが、操作に頭を使うし、no-clickブラウジングできるものは無い。
+
+小型機器で階層情報をたどるときは4-wayでひとつずつたどるのが普通
+
+ブラウザ上でも小型機器でもザッピングのようなインタフェースで気楽に大量データをブラウズしたい
+
+そのためのGearというインタフェースを考えた
+
+Gearでは、ふたつのスイッチやキーだけを使って大量のコンテンツをno-clickでザッピングできる
+
+Large Large data are often represented as a hierarchical structure, and
 various navigation methods are provided for exploring the data.

### 2020-03-04 paper/HCC2020/paper.tex
...

--- 2020-02-28 paper/HCC2020/paper.tex
@@
 \begin{document}
-\title{Non-click browsing}
+\title{No-click browsing of large hierarchical data}
 \author{
@@
 
+% 大量のコンテンツから見たいものを捜して再生するのは大変である
+% 
+% 1. 階層から捜すのが大変
+% 2. みつけたものをConfirmする手間がいる
+
+Huge amount of movies, musics, and other programs are available on the web, but
+finding and viewing a program usually takes time because
+(1) finding a program takes time, and
+(2) a ``confirm'' operation (clicking something or typing a key)
+is required for viewing the content.
+
+% 昔のテレビやラジオではこの手間がなかった
+% チャンネルやチューニングつまみを回すだけでよかった
+% 選択操作はなかった
+% つまりいわゆる「ザッピング」が可能であった
+
+The confirm operations was not required on old TVs and radios,
+because we could enjoy the TV and radio programs
+as soon as we rotated a ``TV channel dial'' or a tuning dial of the radio.
+
+\begin{figure} % [H]
+\centerline{
+   \includegraphics[width=40mm,bb=0 0 279 272]{figures/9bd96506bdaac48b26c5cd192851c11d.png}
+   \includegraphics[width=40mm,bb=0 0 128 72]{figures/fedc4f3c899c48b5a3ddd0982801c79d.png}
+}
+\caption{A n old TV channel and a radio tuning dial}
+\label{TV channel}
+\end{figure}
+
+% 一般に、選択するとすぐに見えるのはどこでも便利なものである
+% Finderのカバーフローや、最下層では選択内容がすぐに見えたりする
+% このときはConfirmの手間なく内容を見られるのは便利なもので、
+% これをno-click browsingと呼ぶことにする
+% TVもラジオもno-click browsingが可能であった
+
+It is always convenient to view the contents of the selected item
+as soon as we find it.
+We call such viewing style as ``\tit{no-click browsing}''.
+
+We can use the style on modern personal computers.
+Using the ``\tsf{Finder.app}'' on MacOS, we can use the ``CoverFlow''\footnote{
+  \tsf{https://en.wikipedia.org/wiki/Cover\_Flow}
+} viewer to browse the contents in a folder
+with simple swyping gestures (Figure \ref{coverflow}).
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=80mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
+\caption{Cover Flow on MacOS}
+\label{coverflow}
+\end{figure}
+
+We can also enjoy no-click browsing on a Finder.app windows
+when we select a file in a folder and
+type arrow keys for selecting other files.
+The contents of the file is shown at the right as soon as
+we select a file in a folder.
+
+\begin{figure}[H]
+% \centerline{\includegraphics[width=70mm,bb=0 0 1678 846]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
+\centerline{\includegraphics[width=70mm,bb=0 0 839 423]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
+\caption{No-click browsing on conventinal Finder mode}
+\label{noclickfinder}
+\end{figure}
+
+% テレビやカバーフローのザッピングはもちろんソースが少なかったからできるわけだが、
+% 大量データの場合はこれが難しい。
+% 何千個もソースがある場合は
+% 階層をたどる処理が必要になり、その移動操作が必要だからである
+
+We can enjoy no-click browsing on old TVs and radios because the number of
+source channels are limited.
+Likely, we can enjoy no-click browsing on Finder.app when the number of files
+in one folder is not very large.
+
+No-click browsing is not popular on the GUI of personal computers.
+People are used to click-based browsing on web browsers and other
+information visualization systems.
+People can navigate through a huge information space by
+clicking links, zooming by dragging, and other GUI operations.
+These techniques are useful for finding an item in a large information space,
+but many clicks and dragging operations are required.
+The contents of the items are usually not shown while
+
+% 階層でもそうでなくても、移動操作は慣れている
+% 適切な階層構造を用意して、クリックしながらたどるのがブラウザでは一般的である
+% ブラウザの場合、カバーフローのようなインタフェースは一般的でないので、
+% みつけたものを選択したり戻ったりを繰り返さなければならない。
+% 
+% ブラウザでは階層のInfoVis[]もいろいろあるが、操作に頭を使うし、no-clickブラウジングできるものは無い。
+
+% 階層的なら上下操作でなんとかなる
+% 小型機器で階層情報をたどるときは4-wayでひとつずつたどるのが普通
+
+% The simplest way of navigatin a hierarchical data is to use four keys
+
+When a user cannot use GUI, key-based interaction techniques are widely used for
+finding information in hierarchical data.
+%
+For example, a user can find a music data by
+selecting an artist from the list of artist names,
+selecting an album title from the title list,
+and selecting a music data from the song list.
+%
+Users can use two keys for choosing an entry from the list
+% (e.g. selecting an artist from the artist list),
+and use another key for selecting an entry and moving to the next level.
+% (e.g. selecting an artist and show album titles).
+It is also necessary to provide a way to go back to the previous state, and
+yet another key can be used for that task.
+% (e.g. showing the artist list for artist selection).
+This 4-way navigation is popular on small devices
+and remote controllers like AppleRemote\footnote{\textsf{http://en.wikipedia.org/wiki/Apple\_Remote}}
+for selecting a song from the hierarchical data.
+4-way navigation is also available on desktop software like Finder.app.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=50mm,bb=0 0 333 250]{figures/0048a5e91ddcf1d5670bd958e3c55619.jpg}}
+\caption{A small device supporting 4-way navigation}
+\label{rio}
+\end{figure}
+
+Using 4 keys might be okay on these devices, but it would be much better
+if we could perform the navigation task using simpler dvices that have only 2 keys.
+In that case, we can also use a rotating device like a disk or a wheel for the navigation,
+since such devices can generate 2 signals based on the rotation direction (Figure \ref{rotation}).
+%
+% We have developed a new navigation technique where only two keys are required
+% for exploring large hierarchical data, and implemented the system on
+% a rotating device ``Strotor''.
+%
+We have developed a new navigation technique called ``{Gear}'',
+where users can explore a large hierarchical database by simple rotating operations.
+%
+Using Gear, we can enjoy no-click browsing only by typing two keys or
+rotating a dial
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=60mm,bb=0 0 294 110]{figures/rotation.pdf}}
+\caption{Using a rotation device for generating key events.}
+\label{rotation}
+\end{figure}
+
+\comment{
+ブラウザ上でも小型機器でもザッピングのようなインタフェースで気楽に大量データをブラウズしたい
+
+そのためのGearというインタフェースを考えた
+
+Gearでは、ふたつのスイッチやキーだけを使って大量のコンテンツをno-clickでザッピングできる
+}
+
+\comment{
 Large data are often represented as a hierarchical structure, and
@@
 On MacOS, four GUI methods are provided for browsing the file system.
+}
 
-% there is no single interaction technique that is always good for any situation.
-% ZUIの話, ハイパーリンクでたどる方法もある
-
-When a user cannot use GUI,
-selection-based interaction techniques are used for
-finding information in hierarchical data.
-For example, a user can hierarchically find a music data by
-selecting an artist from the list of artist names,
-selecting an album title from the title list,
-and selecting a music data from the song list.
-% Users can do the selection jobs either by using a mouse or by using arrow keys.
-% For exaple,
-Users can use two keys for choosing an entry from the list
-(e.g. selecting an artist from the artist list),
-and use another key for selecting an entry and moving to the next level
-(e.g. selecting an artist and show album titles).
-It is also necessary to provide a way to go back to the previous state, and
-yet another key can be used for that task
-(e.g. showing the artist list for artist selection).
-This 4-way navigation is popular on small mp3 players\footnote{
-  e.g. \textsf{http://www.iriver.com/product/view.asp?pCode=003\&pNo=37}
-} and remote controllers like AppleRemote\footnote{\textsf{http://en.wikipedia.org/wiki/Apple\_Remote}}
-for selecting a song from the hierarchical data.
-4-way navigation is also available on desktop software like Finder.app on Mac.
-
-% Amazon FireTV
-
+\comment{
 \begin{figure}[H]
@@
 % 4 buttons for selecting a song from the hierarchical data.
-
-Using 4 keys might be okay on these devices, but it would be much better
-if we could perform the navigation task using simpler dvices that have only 2 keys.
-In that case, we can also use a rotating device like a disk or a wheel for the navigation,
-since such devices can generate 2 signals based on the rotation direction (Figure \ref{rotation}).
-%
-% We have developed a new navigation technique where only two keys are required
-% for exploring large hierarchical data, and implemented the system on
-% a rotating device ``Strotor''.
-%
-We have developed a new navigation technique called ``{Gear}'',
-where users can explore a large hierarchical database by simple rotating operations.
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=60mm,bb=0 0 294 110]{figures/rotation.pdf}}
-\caption{Using a rotation device for generating key events.}
-\label{rotation}
-\end{figure}
+}
 

### 2020-03-05 paper/HCC2020/paper.tex
...

@@
 
-\def\SC{\textsf{\small Serencast}}
-\def\SB{\textsf{\small Scrapbox}}
+\def\SC{\tsf{Serencast}}
+\def\SB{\tsf{Scrapbox}}
 
@@
 We introduce a novel simple interaction technique for finding and browsing
-data in a huge hierarchical database using only two keys or
-one rotating device.
+data in a huge hierarchical database using only two keys.
+% or one rotating device.
 % that can generate two different signals based on the rotation direction.
@@
 We can enjoy various kinds of movies, musics, books,
-etc. distribued from many service providers like Amazon and Netflix.
+etc. distributed from many service providers like Amazon and Netflix.
 However, 
@@
 If the user finds that the data is not the one he wanted,
-he should go back to the previous state and perform the search again.
+he should go back to the previous state and perform the selection again.
 
@@
 Huge amount of movies, musics, and other programs are available on the web, but
-finding and viewing a program usually takes time because
+finding and viewing a program is not easy because
 (1) finding a program takes time, and
@@
 The confirm operations was not required on old TVs and radios,
-because we could enjoy the TV and radio programs
+because we could enjoy TV/radio programs
 as soon as we rotated a ``TV channel dial'' or a tuning dial of the radio.
@@
 
-We can use the style on modern personal computers.
+We can see the non-click browsing style on personal computers.
 Using the ``\tsf{Finder.app}'' on MacOS, we can use the ``CoverFlow''\footnote{
@@
 \centerline{\includegraphics[width=80mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
+% \centerline{\includegraphics[width=80mm,bb=0 0 803 555]{figures/5d46fb09c3c5b4baccfd68ca026ef25b.png}} % Monorail
 \caption{Cover Flow on MacOS}
@@
 
-We can also enjoy no-click browsing on a Finder.app windows
+We can also enjoy no-click browsing on a Finder.app window
 when we select a file in a folder and
 type arrow keys for selecting other files.
-The contents of the file is shown at the right as soon as
-we select a file in a folder.
+Using the ``column view'' mode, 
+the contents of the file is shown at the right side of the window
+as soon as we select a file in a folder (Figure \ref{noclickfinder}).
 
@@
 \centerline{\includegraphics[width=70mm,bb=0 0 839 423]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
-\caption{No-click browsing on conventinal Finder mode}
+\caption{No-click browsing on the column view of Finder.app.}
 \label{noclickfinder}
@@
 
-We can enjoy no-click browsing on old TVs and radios because the number of
-source channels are limited.
-Likely, we can enjoy no-click browsing on Finder.app when the number of files
-in one folder is not very large.
+We can use no-click browsing on old TVs and radios because the number of
+broadcast channels are limited.
+Likewise, we can use no-click browsing on Finder.app when the number of files
+in a folder is not very large.
 
-No-click browsing is not popular on the GUI of personal computers.
+No-click browsing is not popular on conventional GUI of personal computers.
 People are used to click-based browsing on web browsers and other
@@
 People can navigate through a huge information space by
-clicking links, zooming by dragging, and other GUI operations.
+clicking links, zooming by dragging, and using other GUI techniques.
 These techniques are useful for finding an item in a large information space,
-but many clicks and dragging operations are required.
-The contents of the items are usually not shown while
+but many clicks and drag operations are required.
+The contents of the items are usually not shown during the search.
 
@@
 
-When a user cannot use GUI, key-based interaction techniques are widely used for
+When a user cannot use a pointing device,
+key-based interaction techniques are used for
 finding information in hierarchical data.
@@
 selecting an album title from the title list,
-and selecting a music data from the song list.
+and selecting a music title from the song list.
 %
@@
 % (e.g. selecting an artist and show album titles).
-It is also necessary to provide a way to go back to the previous state, and
-yet another key can be used for that task.
+It is also necessary to use another key for going back to the previous level.
 % (e.g. showing the artist list for artist selection).
@@
 for selecting a song from the hierarchical data.
-4-way navigation is also available on desktop software like Finder.app.
+4-way navigation is also available on the column view of Finder.app.
 
 \begin{figure}[H]
-\centerline{\includegraphics[width=50mm,bb=0 0 333 250]{figures/0048a5e91ddcf1d5670bd958e3c55619.jpg}}
-\caption{A small device supporting 4-way navigation}
+\centerline{
+  \includegraphics[width=30mm,bb=0 0 333 250]{figures/0048a5e91ddcf1d5670bd958e3c55619.jpg}
+  \includegraphics[width=30mm,bb=0 0 551 551]{figures/70c036b24525c6cace9955b24152e97e.jpg}
+  }
+\caption{Small devices supporting 4-way navigation}
 \label{rio}
@@
 Using 4 keys might be okay on these devices, but it would be much better
-if we could perform the navigation task using simpler dvices that have only 2 keys.
-In that case, we can also use a rotating device like a disk or a wheel for the navigation,
-since such devices can generate 2 signals based on the rotation direction (Figure \ref{rotation}).
-%
-% We have developed a new navigation technique where only two keys are required
-% for exploring large hierarchical data, and implemented the system on
-% a rotating device ``Strotor''.
-%
-We have developed a new navigation technique called ``{Gear}'',
-where users can explore a large hierarchical database by simple rotating operations.
-%
-Using Gear, we can enjoy no-click browsing only by typing two keys or
-rotating a dial
+if we could perform the navigation task using simpler dvices that have only two keys.
+In that case, we can use a rotating device like a disk or a wheel for the navigation,
+since such devices can generate 2 signals based on the rotation direction.
 
+We have developed a new navigation technique called ``{Gear}'' for no-click browsing,
+where users can explore a large hierarchical database by using only two keys.
+
+\comment{
 \begin{figure}[H]
@@
 Interaction with Gear is based on the following simple principles.
-Two types of operations, ``{\up}'' (up) and ``{\down}'' (down), are used for the navigation.
-They can be performed either by rotating the Gear device or pressing keys.
+Two types of operations,
+``{\up}'' (up) and ``{\down}'' (down), are used for the navigation.
+They can be performed either by pressing keys or rotating a dial.
 
@@
 large hierarchical database,
-we have developed the ``\tsf{Serencast.com}'' service, where
+we have developed the ``{\SC}'' service, where
 users can enjoy movies, musics, and other Web services
@@
 use the Gear interface to find data and browse it.
-We can use \tsf{Serencast.com} service
+We can use {\SC} service
 for using the Gear interface to select a program from the
@@
 \centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
-\caption{Showing a movie.}
+\caption{Showing ``Breakfast at Tiffany's''.}
 \label{tiffany}
@@
 various kinds of input devices can be used for Gear.
-We have tried various input devices, and collected experiences.
+We have tried some input devices and collected experiences.
 

### 2020-03-06 paper/HCC2020.save/paper.tex
IEEE用に修正

--- 2020-03-05 paper/HCC2020/paper.tex
@@
 The simplest input device for Gear may be keyboards or buttons.
-We tried using arrow keys on a PC, and it works fairly fine.
-We also tried special devices with pressure sensors, with which users can press the button strongly to simulate multiple keyboard presses.
-Two keys or pressure sensors can be placed anywhere: we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
-
-We can use two arrow keys on a computer keyboard for using {\SC}.
-It works fine, but Gear is not more useful than using many keys on a computer.
-%
-Good thing is that many keyboard devices are available for personal computers,
-and we can use such devices for using Gear.
-``Key-repeat'' feature is useful for fast scrolling of the menu.
-
-\paragraph{Rotating devices}
-
-We tried various rotating devices for Gear.
-Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
-For example, ``jog dials''ave been widely used for controlling VCRs, and we tried the device for Gear.
-
-(figure)
-
-We have also tried "rollers" for Gear.
-After trying these devices, we found that controlling rotating devices are not as easy as we expect,
-because presice control of a hand is fairly difficult.
-People are good at controling fingers, but people are usually not very good at controlling hands.
-
-We also tried mouse wheels, and found that mouse wheels are very suitable for using Gear, because
-we are good at presice control of our fingers.
-
-We can use a rotary encoder as a
+We tried using arrow keys on a PC, and it works fine.
+Various HID devices\footnote{
+  https://en.wikipedia.org/wiki/Human\_interface\_device
+} are available on the market, and
+all such devices can be used as an input device for Gear.
+For example, a foot switch for turning music score pages\footnote{
+  airturn pedpro
+} can be used as the input device for Gear.
 
 \begin{figure}[H]
-\centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
-\caption{A disk-based device for Gear.}
-\label{disk}
+\centerline{\includegraphics[width=40mm,bb=0 0 900 900]{figures/8d4f811f5a0c393acaff304102ba963f.jpg}}
+\caption{A foot switch for turning a music score.}
+\label{footswitch}
 \end{figure}
 
-We used
-PowerMate\footnote{
-  \textsf{http://griffintechnology.com/support/powermate}
-} from Griffin Technology for the rotating device.
-PowerMate generates standard keyboard events when rotated,
-and no special programming techniques are required.
 %
-Users can explore all the contents just by
-rotating the device clockwise and counterclockwise.
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=30mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
-\caption{A PowerMate used for the prototype.}
-\label{powermate}
-\end{figure}
+% Good thing is that many keyboard devices are available for personal computers,
+% and we can use such devices for using Gear.
+% ``Key-repeat'' feature is useful for fast scrolling of the menu.
 
@@
 
-We have also tried to use a paddle-like device for generating {\U} and {\D}.
-Users can push the puddle to the right to generate {\U} and
-left to generate {\D}.
+% We also tried speciial devices with pressure sensors, with which
+% users can press the button strongly to simulate multiple keyboard presses.
+
+We have also tried to use a paddle-like device for generating {\up} and {\down}.
+Users can push the puddle to the right to generate {\up} and
+left to generate {\down}.
 Pressure sensors are installed on the puddle, and
-many {\U}s are generated when the user pushs the puddle strongly.
+many {\up}'s are generated when the user pushs the puddle strongly.
 
@@
 since sometimes users want to jump to a far entry from current position.
-That behavior is close to the key-repeat feature or computer keyboards.
+That behavior is similar to the key-repeat feature or computer keyboards.
+
+% Keys and pressure sensors can be placed anywhere:
+% we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
+
+\paragraph{Rotating devices}
+
+We then tried various rotating devices for Gear.
+%
+We tried mouse wheels first, and found that they are very suitable for Gear,
+because we are good at controling fingerf precisely.
+
+Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
+For example, ``jog dials'' have been widely used for controlling VCRs, and we tried the device for Gear.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=54mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
+\caption{Using a jog dial.}
+\label{jog}
+\end{figure}
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
+\caption{A disk-based device for Gear.}
+\label{disk}
+\end{figure}
+
+We have also tried using a cylinder for Gear.
+The cylinder shown in Figure \ref{roller} is touching the mouse wheel, and
+mouse whell events are generated as the user rotates the cylinder using his arm or hand.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=54mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
+\caption{Using a roller.}
+\label{roller}
+\end{figure}
+
+After trying these devices, we found that controlling rotating devices
+like jog dials and cylinders are not as easy as we expected,
+because presice control of an arm or a hand is fairly difficult.
+People are good at controling fingers, but people are usually not very good at controlling hands.
+
+Keys and pressure sensors can be placed anywhere:
+we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
 
@@
 \end{figure}
-
 }
@@
 
-If we can put input devices that fits to furnituers, we can use the device near the furniture, without making the input devices look awkward.
-  入力装置つきのカッコ良い家具が作れる
- If we can put the devices neatlly on furnitures and beds, people with disabilities can easilyt use them, 
- 体が不自由でも使えることは間違いない
-
-\comment{
-\section*{IMPLEMENTATION}
-
-A large list of news articles, movies, anime films, musics, and e-book titles are listed in one browser window
-and the content is displayed in another window (Figure \ref{screenshot}).
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=80mm,bb=0 0 671 464]{figures/95cf2fec71c52ead6fdbcb7f79aca654.png}}
-\caption{Selecting an Internet radio station.}
-\label{screenshot}
-\end{figure}
-}
-
-\section*{DISCUSSIONS}
+If we can install the devices neatlly on furnitures and beds, people with disabilities can easilyt use them,
 
@@
 
+To compare the speed of Gear with conventional navigation method,
+we create two applications that can check how fast a user can select an entry
+from a large hierarchical database.
+%
+Both applicatons behaves the same way:
+a user can set the date to a specific time to see a photo of a monorail from Ofuna station to Enoshima station in Japan.
+%
+Using the first one, a user  can set the time using Gear (Figure \ref{monorailgear}),
+using {\up} and {\down} keys.
+
+\begin{figure}[H]
+\centerline{
+%  \includegraphics[width=38mm,bb=0 0 1624 1193]{figures/d663e8556732d40e70e55592ca1f1258.png}
+  \includegraphics[width=70mm,bb=0 0 1624 1193]{figures/75007628f75ef1038bd5737e10a728b7.png}
+}
+\caption{Monorail.}
+\label{monorailgeary}
+\end{figure}
+
+Using the second one, a user can set the time using the \verb+<input>+ tag of HTML (Figure \ref{monorailinput}).
+Users can first set the value of the ``minute'' side using up/down keys,
+and move to the ``second'' side and use up/down keys to the value of the ``second''.
+
+\begin{figure}[H]
+\centerline{
+  \includegraphics[width=70mm,bb=0 0 1596 1116]{figures/325208a6d94c68e4f08e61a67df419c4.png}
+}
+\caption{Monorail.}
+\label{monorailinput}
+\end{figure}
+
+On both applications, target time is displayed on the screen and the subjects are
+asked to set the time to the displayed value.
+After repeating the task 5 times, the average time is logged.
+
+We asked 5 people to try these tasks 10 times, and the result of the experiment is
+shown in Figure \ref{monorailtime}.
+
+\begin{figure}[H]
+\centerline{
+  \includegraphics[width=38mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
+  \includegraphics[width=38mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
+}
+\caption{Average time.}
+\label{monorailtime}
+\end{figure}
+
+The average time for finding an entry using Gear was 6.84s,
+and the average time using standard \verb+<input>+ was 4.96s.
+It takes about 40\% more time than using conventional method.
+
+This is not 素晴らしい結果
+
+\comment{
 4-way navigation is commonly used for exploring hierarchical data structure,
@@
 with one rotating device.
+}
 
@@
 large hierarchical data, but users of these systems have to use a pointing device
-to take full advantage of their advantages.
+to take full advantage of these methods.
 
@@
 
-\section{Discussions}
+\subsection{Is the Gear interface new?}
 
-\subsection{Is the Gear interface a new idea?}
-  Since the idea of Gear interface is so simple, we have been wondering if the same idea had been around in the past.
-  But as far as we know, Gear is the first attempt to explore
+Since the idea of Gear interface is so simple,
+we have been wondering if the same idea had been around in the past.
+The Gear interface had never been popular before, and
+we could not find a similar method in the patent database.
 
- こういうデバイスは超簡単なので、存在した可能性はある
+こういうデバイスは超簡単なので、存在した可能性はあるが
 特許や論文を調べた限りはみつけられなかった
 
-\section*{EVALUATION}
+\subsection*{Using Gear in the wild}
 

### 2020-03-06 paper/HCC2020/paper.tex
...

@@
 %
+% HCC用にIEEEフォーマットにしたもの
 %
-%
-\long\def\comment#1{}
-\newif\ifcover
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
 
-% パタンはtt
-% 出力文字列はsf
-
-\documentclass{article}
-\usepackage{times}
-\usepackage{uist04}
+\usepackage{cite}
+% \usepackage{amsmath,amssymb,amsfontOBs}
+% \usepackage{algorithmic}
+\usepackage{graphicx}
+% \usepackage{textcomp}
+% \usepackage{xcolor}
 
 \usepackage{here} % [H]とするとその場所に配置されるらしい
+\long\def\comment#1{}
 
-% \def\up{ \includegraphics[width=3mm,bb=0 0 36 36]{figures/uptriangle.pdf} }
-% \def\down{ \includegraphics[width=3mm,bb=0 0 36 36]{figures/downtriangle.pdf} }
-% \def\right{ \includegraphics[width=3mm,bb=0 0 36 36]{figures/righttriangle.pdf} }
-% \def\left{ \includegraphics[width=3mm,bb=0 0 36 36]{figures/lefttriangle.pdf} }
+\long\def\comment#1{}
+
+\long\def\ttt#1{\texttt{\small #1}}
+\long\def\tsf#1{\textsf{\small{#1}}}
+\long\def\tit#1{\textit{\small{#1}}}
+
 \def\up{▲}
@@
 
-\long\def\ttt#1{\texttt{\small #1}}
-\long\def\tsf#1{\textsf{\small{#1}}}
-\long\def\tit#1{\textit{\small{#1}}}
-
-% \long\def\ST{\textsf{\small{Strotor}}}
-\long\def\U{\textsf{\small{U}}}
-\long\def\D{\textsf{\small{D}}}
-
-\def\SC{\tsf{Serencast}}
-\def\SB{\tsf{Scrapbox}}
-
-\usepackage{graphicx}
-% mediabb.sty というのを使うとPDFをそのままincludegraphicsできるらしい。
-% http://www.ns.musashi-tech.ac.jp/~inoue/Pages/TeX/mediabb.sty.html
-%
-% \usepackage{mediabb}
-% \usepackage{ascmac}
+\def\SC{Serencast}
+\def\SB{Scrapbox}
 
 \begin{document}
+
 \title{No-click browsing of large hierarchical data}
-\author{
-\begin{tabular}{l}
-\parbox{5.5cm}{
-\begin{center}
-% Toshiyuki Masui\\
-% Keio University\\
-% masui@pitecan.com
-~ \\
-~ \\
-~
-\end{center}
+%
+% zero-click? no-click? clickless?
+% zero-click searchとかclickless searchとかいうのは、Google検索の結果だけ見てクリックをしないことをそう呼ぶらしい
+% no-click search という言葉も使われている
+%
+
+\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
 }
-\end{tabular}
-}
+
 \maketitle
-\abstract
 
+\begin{abstract}
 We introduce a novel simple interaction technique for finding and browsing
@@
 using old television dials.
+\end{abstract}
 
-\keywords Input device, Information navigation, Hierarchical data, Gear, Serencast
+\begin{IEEEkeywords}
+component, formatting, style, styling, insert
+\end{IEEEkeywords}
 
-\tolerance=400 
-  % makes some lines with lots of white space, but 	
-  % tends to prevent words from sticking out in the margin
-
-\section*{INTRODUCTION}
+\section{Introduction}
 
@@
 
-\begin{figure} % [H]
+\begin{figure}[H]
 \centerline{
-   \includegraphics[width=40mm,bb=0 0 279 272]{figures/9bd96506bdaac48b26c5cd192851c11d.png}
-   \includegraphics[width=40mm,bb=0 0 128 72]{figures/fedc4f3c899c48b5a3ddd0982801c79d.png}
+   \includegraphics[width=35mm,bb=0 0 279 272]{figures/9bd96506bdaac48b26c5cd192851c11d.png}
+   \includegraphics[width=35mm,bb=0 0 128 72]{figures/fedc4f3c899c48b5a3ddd0982801c79d.png}
 }
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=80mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
+\centerline{\includegraphics[width=65mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
 % \centerline{\includegraphics[width=80mm,bb=0 0 803 555]{figures/5d46fb09c3c5b4baccfd68ca026ef25b.png}} % Monorail
@@
 
-\comment{
-\begin{figure}[H]
-\centerline{\includegraphics[width=60mm,bb=0 0 294 110]{figures/rotation.pdf}}
-\caption{Using a rotation device for generating key events.}
-\label{rotation}
-\end{figure}
-}
-
-\comment{
-ブラウザ上でも小型機器でもザッピングのようなインタフェースで気楽に大量データをブラウズしたい
-
-そのためのGearというインタフェースを考えた
-
-Gearでは、ふたつのスイッチやキーだけを使って大量のコンテンツをno-clickでザッピングできる
-}
-
-\comment{
-Large data are often represented as a hierarchical structure, and
-various navigation methods are provided for exploring the data.
-For example, files on Unix are structured hierarchically, and
-many commands (\tsf{cd}, \tsf{ls}, etc.) and APIs are provided for exploring the file system.
-Large dictionary database can also be treated as a large
-hierarchical data, since the name of the entry can be treated hierarchically:
-e.g. an entry for ``\tsf{dictionary}'' can be stored under ``\tsf{d}'', ``\tsf{d/i}'', and so on.
-
-Many information visualization techniques and navigation techniques
-have been proposed for handling large hierarchical data.
-On modern personal computers,
-multiple GUI techniques are provided for
-exploring the hierarchical file structure, because
-there is no best interaction technique that fits to all the users and situations.
-On MacOS, four GUI methods are provided for browsing the file system.
-}
-
-\comment{
-\begin{figure}[H]
-\centerline{\includegraphics[width=80mm,bb=0 0 547 179]{figures/4buttons.png}}
-\caption{4-button controllers on a small mp3 player (left) and AppleRemote (right).}
-\label{u10}
-\end{figure}
-
-% http://www.reigncom.com/eng/media/press/en_pr_read.asp?no_noti=1630&cd_noti_host=9
-% D-Click Control System
-
-% Small devices like Rio MP3 player and remote controllers like AppleRemote have
-% 4 buttons for selecting a song from the hierarchical data.
-}
-
-\section*{NAVIGATION METHOD AND EXAMPLES}
+\section{Navigation method and examples}
 \label{navigation}
@@
 % \includegraphics[width=70mm]{figures/fig1.pdf}
-\centerline{\includegraphics[width=80mm,bb=0 0 490 490]{figures/fig1.pdf}}
-\caption{Sample data: shops in a shopping mall.}
+\centerline{\includegraphics[width=70mm,bb=0 0 490 490]{figures/fig1.pdf}}
+\caption{Sample data: shops data of a shopping mall.}
 \label{fig1}
@@
 
-\section{SERENCAST: A NON-CLICK BROWSING SERVICE}
+\section{Serencast: a non-click browsing service}
 
@@
 
-To prove that Gear is useful for selecting an entry from a very
+To prove that Gear is useful for selecting an entry from a
 large hierarchical database,
-we have developed the ``{\SC}'' service, where
-users can enjoy movies, musics, and other Web services
-on the browser with the Gear interface.
-{\SC} is implemented in JavaScript, and runs on modern browsers
+we have developed the ``\tsf{\SC}'' service, where
+users can enjoy movies, musics, and other web services
+on the browser with the Gear interface without selectiong (clicking) an item.
+{\SC} is implemented in JavaScript, and runs on modern web browsers
 
-{\SC} uses the ``\tsf{Scrapbox.io}'' wiki service\footnote{
+{\SC} uses the ``\tsf{\SB}'' wiki service\footnote{
   \tsf{https://Scrapbox.io/}
@@
   \tsf{https://en.wikipedia.org/wiki/Wiki}
-} system where users can share and edit texts on the Web browser.
+} system where users can share and edit texts on the web browser.
 A user can create a {\SB} ``project'', and create pages
-that consists of texts and links,
-and people can share the page and edit it freely on their browsers.
+that consists of texts and links.
+People can share the page and edit it interactively on their browsers
+just like the Google Docs system\footnote{
+  \tsf{https://www.google.com/docs/about/}
+}.
 
 \begin{figure}[H]
-\centerline{\includegraphics[width=80mm,bb=0 0 1553 1174]{figures/28818d749896f87f3eb8bd6b6f9e9a36.png}}
+\centerline{\includegraphics[width=75mm,bb=0 0 1553 1174]{figures/28818d749896f87f3eb8bd6b6f9e9a36.png}}
 \caption{An example of a {\SB} project.}
@@
 The title of the project is ``Scrapbox help'', and
-many pages like ``Features'' exist inthe project.
+other pages like ``Features'' exist in the project.
 
@@
 In this example, a URL link to {\tsf{http://gyazo.com}} is used
-just like \tsf{A} tags used in HTML.
+just like an \tsf{A} tags in HTML.
 
@@
 movies and musics on a {\SB} page,
-we can create a hierarchical structure from the list and
-use the Gear interface to find data and browse it.
+% we can create a hierarchical structure from the list and
+% use the Gear interface to find data and browse it.
 We can use {\SC} service
@@
 % \centerline{\includegraphics[width=40mm,bb=0 0 417 619]{figures/2690db244045aa809a3e2fc2b40ba0a3.png}}
-\centerline{\includegraphics[width=40mm,bb=0 0 387 568]{figures/2b97930bf5730fcaf4d9c0adeb9c5f6e.png}}
-\caption{Movie list.}
+\centerline{\includegraphics[width=30mm,bb=0 0 387 568]{figures/2b97930bf5730fcaf4d9c0adeb9c5f6e.png}}
+\caption{A movie list page on {\SB}.}
 \label{movielist}
@@
 
-When we access the {\SB} page from {\SC},
+When we access this {\SB} page from {\SC},
 ``Gran Trino'' from Netflix automatically starts in the right side of the screen,
-just like a TV program starts when we rotate tha channel dial of an old television.
+just like a TV program starts when we rotate the channel dial of an old television.
 When the user pushes the {\down} key twice,
@@
 
-In the above example, we can select only one of the 10 movies using the Gear interface.
-But we can add more data by hierarchically providing more contents in {\SB} pages.
+In the above example, we can select only one of the 10 movies from the movie list.
+But we can add more data by hierarchically providing contents in {\SB} pages.
 
 In one page, we can specify a hierarchical structure by using indentations.
-Figure \ref{musiclist} shows a portion of a list of CDs and
-musics titles by ``Weather Report'' and ``Wes Montgomery'' are shown\footnote{
+Figure \ref{musiclist} shows a portion of a list of music CDs and
+titles by ``Weather Report'' and ``Wes Montgomery'' are shown\footnote{
   Weather Report is the name of a famous Jazz group, and Wes Montgomery is a famous Jazz guitarist.
@@
 % \centerline{\includegraphics[width=40mm,bb=0 0 596 808]{figures/6657544cf60cbf0aea91ba7da0455b90.png}}
-\centerline{\includegraphics[width=40mm,bb=0 0 652 926]{figures/d8fe8ff8f3e1bbcb34cf51e268592f8c.png}}
+\centerline{\includegraphics[width=50mm,bb=0 0 652 926]{figures/d8fe8ff8f3e1bbcb34cf51e268592f8c.png}}
 \caption{Music list.}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=40mm,bb=0 0 396 523]{figures/8a8e4d63b75183f1b4d0ed4db733f500.png}}
+% \centerline{\includegraphics[width=40mm,bb=0 0 396 523]{figures/8a8e4d63b75183f1b4d0ed4db733f500.png}}
+\centerline{\includegraphics[width=27mm,bb=0 0 262 515]{figures/5a644f357ba6a6b81b011e200019d736.png}}
 \caption{Top page.}
@@
 \centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackjack.png}}
-\caption{Reading a comicbook.}
+\caption{Reading a comic book.}
 \label{blackjack}
@@
 
-Since anybody can edit the {\SB} page and construct the hierarchical data,
-people can enjoy creating their own data by editing their {\SB} pages.
-Also, when people who want to advertise their works,
-they can create their {\SB} page
-and give it to others so that other people can include the page
-in their list and enjoy it using Gear.
+Since anybody can edit {\SB} pages and construct the hierarchical data,
+people can enjoy creating their own hierarchical database by editing their {\SB} pages.
+When someone wants to advertise their works,
+he can create his {\SB} pages
+and give them to other people so that they can watch the pages.
+People can freely include other people's {\SB} pages in their own list
+and enjoy all the contents just by using Gear.
 
-\section{DISCUSSIONS}
+\section{Discussion}
 
@@
 Since only two switches are required in the Gear interface,
-various kinds of input devices can be used for Gear.
-We have tried some input devices and collected experiences.
+any kind of input devices can be used for Gear.
+We have tried various input devices and collected experiences.
 
-\paragraph{Keys and buttons}
+\subsubsection{Keys and buttons}
 
-The simplest input device for Gear may be keyboards or buttons.
-We tried using arrow keys on a PC, and it works fairly fine.
-We also tried special devices with pressure sensors, with which users can press the button strongly to simulate multiple keyboard presses.
-Two keys or pressure sensors can be placed anywhere: we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
-
-We can use two arrow keys on a computer keyboard for using {\SC}.
-It works fine, but Gear is not more useful than using many keys on a computer.
-%
-Good thing is that many keyboard devices are available for personal computers,
-and we can use such devices for using Gear.
-``Key-repeat'' feature is useful for fast scrolling of the menu.
-
-\paragraph{Rotating devices}
-
-We tried various rotating devices for Gear.
-Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
-For example, ``jog dials''ave been widely used for controlling VCRs, and we tried the device for Gear.
-
-(figure)
-
-We have also tried "rollers" for Gear.
-After trying these devices, we found that controlling rotating devices are not as easy as we expect,
-because presice control of a hand is fairly difficult.
-People are good at controling fingers, but people are usually not very good at controlling hands.
-
-We also tried mouse wheels, and found that mouse wheels are very suitable for using Gear, because
-we are good at presice control of our fingers.
-
-We can use a rotary encoder as a
+The simplest input device for Gear may be keyboards and push buttons.
+We tried using arrow keys on a PC, and it works fine.
+Various HID devices\footnote{
+  https://en.wikipedia.org/wiki/Human\_interface\_device
+} are available on the market, and
+all such devices can be used as an input device for Gear.
+For example, a foot switch for turning music score pages\footnote{
+  airturn pedpro
+} can be used as the input device for Gear.
+Even a special foot pedal can be used for Gear (Figure \ref{footswitch}).
 
 \begin{figure}[H]
-\centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
-\caption{A disk-based device for Gear.}
-\label{disk}
+\centerline{\includegraphics[width=40mm,bb=0 0 900 900]{figures/8d4f811f5a0c393acaff304102ba963f.jpg}}
+\caption{A foot switch for turning a music score.}
+\label{footswitch}
 \end{figure}
 
-We used
-PowerMate\footnote{
-  \textsf{http://griffintechnology.com/support/powermate}
-} from Griffin Technology for the rotating device.
-PowerMate generates standard keyboard events when rotated,
-and no special programming techniques are required.
 %
-Users can explore all the contents just by
-rotating the device clockwise and counterclockwise.
+% Good thing is that many keyboard devices are available for personal computers,
+% and we can use such devices for using Gear.
+% ``Key-repeat'' feature is useful for fast scrolling of the menu.
 
-\begin{figure}[H]
-\centerline{\includegraphics[width=30mm,bb=0 0 389 348]{figures/d3a69499f7e7314ae6dc10f5bf3a2be5.png}}
-\caption{A PowerMate used for the prototype.}
-\label{powermate}
-\end{figure}
+\subsubsection{2-way lever}
 
-\paragraph{2-way lever}
-
-We have also tried to use a paddle-like device for generating {\U} and {\D}.
-Users can push the puddle to the right to generate {\U} and
-left to generate {\D}.
+We have also tried to use a paddle-like device for generating {\up} and {\down}.
+Users can push the puddle to the right to generate {\up} and
+left to generate {\down}.
 Pressure sensors are installed on the puddle, and
-many {\U}s are generated when the user pushs the puddle strongly.
+many {\up}'s are generated when the user pushs the puddle strongly.
 
@@
 Controling the speed of the scrolling of Gear by pressure is convenient,
-since sometimes users want to jump to a far entry from current position.
-That behavior is close to the key-repeat feature or computer keyboards.
+since sometimes users want to jump to anentry far from current position.
+That behavior is similar to the key-repeat feature of computer keyboards.
+
+% Keys and pressure sensors can be placed anywhere:
+% we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
+
+\subsubsection{Rotating devices}
+
+We then tried various rotating devices for Gear.
+%
+We tried mouse wheels first, and found that they are very suitable for Gear,
+because we are good at controling our finger with precision.
+
+Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
+For example, ``jog dials'' have been widely used for controlling VCRs, and we tried the device for Gear.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=54mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
+\caption{Using a jog dial.}
+\label{jog}
+\end{figure}
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
+\caption{A disk-based device for Gear.}
+\label{disk}
+\end{figure}
+
+We have also tried using a cylinder for Gear.
+The rotating cylinder shown in Figure \ref{roller} is touching the mouse wheel, and
+mouse whell events are generated as the user rotates the cylinder using his arm or hand.
+
+\begin{figure}[H]
+\centerline{\includegraphics[width=54mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
+\caption{Using a roller.}
+\label{roller}
+\end{figure}
+
+After trying these devices, we found that controlling rotating devices
+like jog dials and cylinders are not as easy as we expected,
+because presice control of an arm or a hand is fairly difficult.
+People are good at controling fingers, but people are usually not very good at
+controlling arms and hands precisely.
+
+Keys and pressure sensors can be placed anywhere:
+we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
 
@@
 
+To compare the speed of Gear with conventional navigation method,
+we created two applications for checking how fast a user can select an entry
+from a large hierarchical database.
+%
+Both applicatons behaves the same way:
+a user can set the date to a specific time to see a photo in a 15-minite monorail trip.
+%
+Using the first one (App1), a user can set the time using Gear (Figure \ref{monorailgear})
+with up/down arrow keys for {\up} and {\down}.
+
+\begin{figure}[H]
+\centerline{
+%  \includegraphics[width=38mm,bb=0 0 1624 1193]{figures/d663e8556732d40e70e55592ca1f1258.png}
+  \includegraphics[width=70mm,bb=0 0 1624 1193]{figures/75007628f75ef1038bd5737e10a728b7.png}
+}
+\caption{App1: Gear-based application for finding a monorail picture.}
+\label{monorailgear}
+\end{figure}
+
+Using the second one, a user can set the time using the \ttt{{\textless}input type="time"{\textgreater}} tag of HTML (Figure \ref{monorailinput}).
+Users can first set the value of the ``minute'' value at the top-left using up/down cursor keys,
+and move to the right with the right-arrow key and set the ``second'' value with up/down arrow keys.
+
+\begin{figure}[H]
+\centerline{
+  \includegraphics[width=70mm,bb=0 0 1596 1116]{figures/325208a6d94c68e4f08e61a67df419c4.png}
+}
+\caption{App2: using input element.}
+\label{monorailinput}
+\end{figure}
+
+On both applications, a random target time is displayed on the screen and the subjects are
+asked to set the time to the displayed target time.
+After repeating the task 5 times, the average time is shown to the user, and the value
+is reported.
+
+We asked 5 people to try these tasks 10 times, and the result of the experiment is
+shown in Figure \ref{monorailtime}.
+
+\begin{figure}[H]
+\centerline{
+  \includegraphics[width=38mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
+  \includegraphics[width=38mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
+}
+\caption{Average search time of App1 and App2.}
+\label{monorailtime}
+\end{figure}
+
+The average time for finding an entry using Gear was 6.84s,
+and the average time using standard \verb+<input>+ was 4.96s.
+It takes about 40\% more time than using conventional method.
+The standard deviations were 0.71s and 0.93s, respectively.
+%
+This is not a great result for Gear,
+but we are happy to see that
+no-click browsing with Gear is not too slower than
+conventional methods.
+
+We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}, and
+got similar results as App2.
+
+\comment{
 4-way navigation is commonly used for exploring hierarchical data structure,
@@
 all of these systems are useful for understanding the structure of
-large hierarchical data, but users of these systems have to use a pointing device
-to take full advantage of their advantages.
+large hierarchical data.
+However, users of these systems have to use a pointing device
+to take full advantage of these methods, and
+no-click browsing is not supported.
 
@@
 
-\section{Discussions}
+\subsection{Is the Gear interface new?}
 
-\subsection{Is the Gear interface a new idea?}
-  Since the idea of Gear interface is so simple, we have been wondering if the same idea had been around in the past.
-  But as far as we know, Gear is the first attempt to explore
+Since the idea of Gear interface is so simple,
+we have been wondering if the same idea existed in the past.
+We are almost sure that The Gear interface had never been popular before,
+and we could not find a similar method in the patent database.
 
- こういうデバイスは超簡単なので、存在した可能性はある
- 特許や論文を調べた限りはみつけられなかった
+\subsection{Using Gear in the wild}
 
-\section*{EVALUATION}
+One of the authors have been using Gear in his living room for several years
+with a small personal computer connected to a 60-inch TV monitor.
+The database is managed on {\SB}, and
+a mouse wheel of a wireless Bluetooth is used for Gear interface.
+With Gear, the user can enjoy all available contents on the web with the mouse wheel
+without selecting the source of the movies, animes, and musics (e.g. Amazon, Netflix, etc.)
 
-\begin{verbatim}
-実際に家で使っていた
- 階層構成の問題点はあるが、いろんな階層を用意しておけばいい
-  時間的階層、アーティスト的階層、名前的階層、...
-  それはなんとか対応できることをいう
-   もちろん同時に指定できればいいのだが...
- 音量とか場所とかは?
- 名前があるものは必ず階層的に検索できる
-  e.g. 辞書
-\end{verbatim}
+We can enjoy using Gear everywhere using a stick PC and a wireless mouse,
+just like Amazon FireTV can be used for the same purpose.
+Using {\SC} is more fun for the author, since no-click browsing is more convenient than
+selection-based interface on existing systems.
+
+\comment{
+Large dictionary database can also be treated as a large
+hierarchical data, since the name of the entry can be treated hierarchically:
+e.g. an entry for ``\tsf{dictionary}'' can be stored under ``\tsf{d}'', ``\tsf{d/i}'', and so on.
 
@@
 a film or a music just by rotating the mouse wheel.
+}
 
 We demonstrated Gear at an exhibition
-held in November 2013, and asked more than 100 people to try it
+% held in November 2013,
+and asked more than 100 people to try it
 (Figure \ref{exhibition}).
 %
-Since the only thing a user can do with Gear is to rotate the device,
+Since the only thing a user can do with Gear was to rotate a wheel,
 users seemed to be able to understand the behavior of Gear with trials and errors.
@@
 Using only one rotating device for data navigation is a new experience for
-all the subjects, but the hard restriction of the device seemed to have worked in this case.
+all the visitors, but the hard restriction of the device seemed to have worked in this case.
 
@@
 \centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
-\caption{People at the right using {\SC} at an exhibition.}
+\caption{People at the right using a wheel device at an exhibition.}
 \label{exhibition}
@@
 
-\section*{CONCLUSIONS}
+\section{Conclusions}
 
@@
 \small{
-\bibliographystyle{plain}
+\bibliographystyle{IEEEtran}
 \bibliography{paper}
@@
 \end{document}
-
-Non-click browsingの威力
-  ストレスが全然違う
-音声を使う
-満員電車で使える
-速度
-  log(n)
-時刻のセットとか
-
-ザッピングの研究はあるか

### 2020-03-06 paper/HCC2020/paper.tex
軽くスペルチェック

@@
 However, 
-finding a data from the huge database is not a trivial task. Users can
+finding a data from a huge database is not a trivial task. Users can
 either find an entry using keywords, or using a menu based
 on a hierarchical structure of the database.
-After successfully finding a candidate data,
-the user should confirm that he wants to watch it by pressing a ``select'' button.
+After successfully finding an entry,
+the user should confirm that he wants to watch it by clicking a ``select'' button.
 If the user finds that the data is not the one he wanted,
@@
 
-In the past, when only a small number of ``channels'' were availale
+In the past, when only a small number of ``channels'' were available
 from broadcast TV stations, the only thing users could do was
-using the ``television dial'' to select a ``channel'' and watch the
-broadcasted data.
+using a television dial to select a ``channel'' and watch the
+broadcast data.
 Although the number of the sources were limited,
@@
 We introduce a simple interaction technique called ``Gear'',
-with which users can select an entry from a very large hiearchial database and
+with which users can select an entry from a very large hierarchical database and
 browse it instantly, just like we could select a channel and enjoy a TV program
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+  Input device, Information navigation, No-click browsing,
+  Hierarchical data, Gear, Serencast
 \end{IEEEkeywords}
@@
 }
-\caption{A n old TV channel and a radio tuning dial}
+\caption{An old TV channel dial and a radio tuning dial}
 \label{TV channel}
@@
 as soon as we find it.
-We call such viewing style as ``\tit{no-click browsing}''.
+We call such viewing style as ``\textbf{\tit{no-click browsing}}''.
 
-We can see the non-click browsing style on personal computers.
-Using the ``\tsf{Finder.app}'' on MacOS, we can use the ``CoverFlow''\footnote{
+We can use the non-click browsing style on personal computers.
+Using the Finder.app on MacOS, we can use the ``Cover Flow''\footnote{
   \tsf{https://en.wikipedia.org/wiki/Cover\_Flow}
 } viewer to browse the contents in a folder
-with simple swyping gestures (Figure \ref{coverflow}).
+with simple swiping gestures (Figure \ref{coverflow}).
 
@@
 \centerline{\includegraphics[width=70mm,bb=0 0 839 423]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
-\caption{No-click browsing on the column view of Finder.app.}
+\caption{No-click browsing on the ``column view'' of Finder.app.}
 \label{noclickfinder}
@@
 This 4-way navigation is popular on small devices
-and remote controllers like AppleRemote\footnote{\textsf{http://en.wikipedia.org/wiki/Apple\_Remote}}
-for selecting a song from the hierarchical data.
+and remote controllers for selecting a song from the hierarchical data.
 4-way navigation is also available on the column view of Finder.app.
@@
 Using 4 keys might be okay on these devices, but it would be much better
-if we could perform the navigation task using simpler dvices that have only two keys.
+if we could perform the navigation task using simpler devices that have only two keys.
 In that case, we can use a rotating device like a disk or a wheel for the navigation,
@@
 Two types of operations,
-``{\up}'' (up) and ``{\down}'' (down), are used for the navigation.
+{\up} (up) and {\down} (down), are used for the navigation.
 They can be performed either by pressing keys or rotating a dial.
@@
 \begin{enumerate}
-\item A portion of the hierarchical data is shown to the user as a list.
+\item A portion of hierarchical data is shown to the user as a list.
 
@@
 
-\item When an elemente is selected, its siblings, its ancestors and their siblings are displayed
+\item When an element is selected, its siblings, its ancestors and their siblings are displayed
 around the selected element.
@@
 \item When a newly selected element has children and the user performs no further action,
-the first child of the selected elemente is newly selected, and 3. is performed.
+the first child of the selected element is newly selected, and 3. is performed.
 As a result, all the siblings of the newly selected element
@@
 When the user issues {\down} twice in Figure \ref{fig7},
-\tsf{Clothing} is selected, and the category under \tsf{Food/drink} will shrinke (Figure \ref{fig8}).
+\tsf{Clothing} is selected, and the category under \tsf{Food/drink} will shrink (Figure \ref{fig8}).
 
@@
 users can enjoy movies, musics, and other web services
-on the browser with the Gear interface without selectiong (clicking) an item.
+on the browser with the Gear interface without selecting (clicking) an item.
 {\SC} is implemented in JavaScript, and runs on modern web browsers
@@
  [https://www.happyon.jp/watch/100048550 Mad Max]
- [https://www.netflix.com/watch/60010351 Flashcance]
+ [https://www.netflix.com/watch/60010351 Flashdance]
  [https://www.netflix.com/watch/80095365 La La Land]
@@
 Pressure sensors are installed on the puddle, and
-many {\up}'s are generated when the user pushs the puddle strongly.
+many {\up}'s are generated when the user pushes the puddle strongly.
 
@@
 
-Controling the speed of the scrolling of Gear by pressure is convenient,
-since sometimes users want to jump to anentry far from current position.
+Controlling the speed of the scrolling of Gear by pressure is convenient,
+since sometimes users want to jump to an entry far from current position.
 That behavior is similar to the key-repeat feature of computer keyboards.
@@
 We tried mouse wheels first, and found that they are very suitable for Gear,
-because we are good at controling our finger with precision.
+because we are good at controlling our finger with precision.
 
@@
 The rotating cylinder shown in Figure \ref{roller} is touching the mouse wheel, and
-mouse whell events are generated as the user rotates the cylinder using his arm or hand.
+mouse wheel events are generated as the user rotates the cylinder using his arm or hand.
 
@@
 like jog dials and cylinders are not as easy as we expected,
-because presice control of an arm or a hand is fairly difficult.
-People are good at controling fingers, but people are usually not very good at
+because precise control of an arm or a hand is fairly difficult.
+People are good at controlling fingers, but people are usually not very good at
 controlling arms and hands precisely.
@@
 
-If we can install the devices neatlly on furnitures and beds, people with disabilities can easilyt use them,
+If we can install the devices neatly on furniture and beds, people with disabilities can easily use them,
 
@@
 %
-Both applicatons behaves the same way:
-a user can set the date to a specific time to see a photo in a 15-minite monorail trip.
+Both applications behaves the same way:
+a user can set the date to a specific time to see a photo in a 15-minute monorail trip.
 %
@@
 With Gear, the user can enjoy all available contents on the web with the mouse wheel
-without selecting the source of the movies, animes, and musics (e.g. Amazon, Netflix, etc.)
+without selecting the source of the movies, animes, and musics (e.g. Amazon, Netflix, etc.).
 
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
+\centerline{\includegraphics[width=80mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
 \caption{People at the right using a wheel device at an exhibition.}
@@
 
-\section{Conclusions}
+\section{Conclusion}
 

### 2020-03-07 paper/HCC2020/paper.tex
...

@@
 % HCC用にIEEEフォーマットにしたもの
+%
+% 参考文献に適当なものを入れたい
+%  Dynamic Queryとか no-click browsingが気持ちよい理由
+%
+%  https://dl.acm.org/doi/abs/10.1145/964696.964706 五十嵐氏の カスケーディングメニューのトラバース
+%
+% tree traverseという言葉を使いたい
+%
+% Dasher, LensBar
 %
@@
 \end{IEEEkeywords}
+
+% Input device, Information navigation, No-click browsing, Hierarchical data, Gear, Serencast
 
@@
 The simplest input device for Gear may be keyboards and push buttons.
-We tried using arrow keys on a PC, and it works fine.
+Gear works pretty comfortably with arrow keys on a PC.
 Various HID devices\footnote{
@@
 
+\begin{figure}[H]
+\centerline{
+  \includegraphics[width=38mm,bb=0 0 188 188]{figures/treeview.png}
+}
+\caption{A TreeView example.}
+\label{treeview}
+\end{figure}
+
 % LensBar\cite{Masui:1998:LVB:647341.721215}
@@
 we have been wondering if the same idea existed in the past.
+%
+We could not find a research paper on 
+navigation techniques based on two keys.
+Many key-based navigation techniques are found on patent database,
+but we could not find a navigation method based on two keys.
 We are almost sure that The Gear interface had never been popular before,
-and we could not find a similar method in the patent database.
 

### 2020-03-07 paper/HCC2020/paper.tex
...

@@
 % Dasher, LensBar
+%
+% Abstractが210語あるので減らす
 %
@@
 
-\def\up{▲}
-\def\down{▼}
-\def\right{▶}
-\def\left{◀}
+\def\up{\tsf{▲}}
+\def\down{\tsf{▼}}
+\def\right{\tsf{▶}}
+\def\left{\tsf{◀}}
 
@@
 data in a huge hierarchical database using only two keys.
-% or one rotating device.
-% that can generate two different signals based on the rotation direction.
 
-We can enjoy various kinds of movies, musics, books,
-etc. distributed from many service providers like Amazon and Netflix.
-However, 
-finding a data from a huge database is not a trivial task. Users can
-either find an entry using keywords, or using a menu based
-on a hierarchical structure of the database.
-After successfully finding an entry,
-the user should confirm that he wants to watch it by clicking a ``select'' button.
-If the user finds that the data is not the one he wanted,
-he should go back to the previous state and perform the selection again.
+Finding a data from a huge hierarchical database takes time
+because users should traverse the tree using a mouse or a keyboard,
+and click a ``select'' button to check the content.
+If the data was not appropriate,
+he should go to the next entry and perform the selection task again.
 
 In the past, when only a small number of ``channels'' were available
-from broadcast TV stations, the only thing users could do was
-using a television dial to select a ``channel'' and watch the
-broadcast data.
-Although the number of the sources were limited,
-the user interface for selecting a station was simple.
-%
+from broadcast TV stations, users could simply rotate
+a television dial to select a channel and watch the program.
 We introduce a simple interaction technique called ``Gear'',
-with which users can select an entry from a very large hierarchical database and
-browse it instantly, just like we could select a channel and enjoy a TV program
+with which users can select an entry from a large hierarchical database and
+browse it instantly, just like we could select a channel and enjoy a program
 using old television dials.
@@
 because we could enjoy TV/radio programs
-as soon as we rotated a ``TV channel dial'' or a tuning dial of the radio.
+as soon as we rotated a TV channel dial or a tuning dial of the radio.
 
@@
 
-We can use the non-click browsing style on personal computers.
+We can use the no-click browsing style on personal computers.
 Using the Finder.app on MacOS, we can use the ``Cover Flow''\footnote{
@@
 
-We can also enjoy no-click browsing on a Finder.app window
-when we select a file in a folder and
-type arrow keys for selecting other files.
-Using the ``column view'' mode, 
+We can also enjoy no-click browsing on the ``column view'' mode of Finder.app.
+In the column view mode, 
 the contents of the file is shown at the right side of the window
 as soon as we select a file in a folder (Figure \ref{noclickfinder}).
+When we type an arrow key and select another file,
+the contents is shown instantly without a confirm operation.
 
@@
 
-Using 4 keys might be okay on these devices, but it would be much better
+Using 4 keys might be okay on these devices, but it would be better
 if we could perform the navigation task using simpler devices that have only two keys.
 In that case, we can use a rotating device like a disk or a wheel for the navigation,
-since such devices can generate 2 signals based on the rotation direction.
+since such devices can generate two signals based on the rotation direction.
 
@@
 
-\section{Navigation method and examples}
+\section{Navigation method of Gear}
 \label{navigation}
@@
 
-\section{Serencast: a non-click browsing service}
+\section{Serencast: a no-click browsing service}
 
@@
 } for listing the contents of the hierarchical database.
-{\SB} is an interactive wiki\footnote{
-  \tsf{https://en.wikipedia.org/wiki/Wiki}
-} system where users can share and edit texts on the web browser.
+{\SB} is an interactive wiki
+system where users can share and edit texts on the web browser.
 A user can create a {\SB} ``project'', and create pages
@@
 Since only two switches are required in the Gear interface,
-any kind of input devices can be used for Gear.
+almost any kind of input devices can be used for Gear.
 We have tried various input devices and collected experiences.
@@
 Various HID devices\footnote{
-  https://en.wikipedia.org/wiki/Human\_interface\_device
+  \tsf{https://en.wikipedia.org/wiki/Human\_interface\_device}
 } are available on the market, and
@@
 For example, a foot switch for turning music score pages\footnote{
-  airturn pedpro
-} can be used as the input device for Gear.
+  \tsf{https://airturn.com/products/airturn-pedpro}
+} can be used as an input device for Gear.
 Even a special foot pedal can be used for Gear (Figure \ref{footswitch}).
@@
 
-Keys and pressure sensors can be placed anywhere:
-we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
+% Keys and pressure sensors can be placed anywhere:
+% we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
 
@@
 important in the IoT age.
-
+%
 If we can install the devices neatly on furniture and beds, people with disabilities can easily use them,
@@
 The average time for finding an entry using Gear was 6.84s,
-and the average time using standard \verb+<input>+ was 4.96s.
+and the average time using standard \ttt{{\textless}input{\textgreater}} was 4.96s.
 It takes about 40\% more time than using conventional method.
@@
 %
-This is not a great result for Gear,
+This is a little bit disappointing,
 but we are happy to see that
@@
 
-We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}, and
+We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}), and
 got similar results as App2.
@@
   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
-}, by replacing 4-way navigation to Gear.
+}, by replacing 4-way navigation with Gear.
 
@@
 but we could not find a navigation method based on two keys.
-We are almost sure that The Gear interface had never been popular before,
+We are almost sure that The Gear interface had never been popular before.
 
@@
 The database is managed on {\SB}, and
-a mouse wheel of a wireless Bluetooth is used for Gear interface.
+a mouse wheel of a wireless Bluetooth mouse is used for Gear interface.
 With Gear, the user can enjoy all available contents on the web with the mouse wheel
@@
 just like Amazon FireTV can be used for the same purpose.
-Using {\SC} is more fun for the author, since no-click browsing is more convenient than
+Using {\SC} is more fun for the author, since no-click browsing is more comfortable than
 selection-based interface on existing systems.
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=80mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
+\centerline{\includegraphics[width=84mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
 \caption{People at the right using a wheel device at an exhibition.}

### 2020-03-07 paper/HCC2020/paper.tex
...

@@
 broadcast channels are limited.
-Likewise, we can use no-click browsing on Finder.app when the number of files
-in a folder is not very large.
+Likewise, no-click browsing on Finder.app is useful
+when the number of files in a folder is not very large.
 
@@
 These techniques are useful for finding an item in a large information space,
-but many clicks and drag operations are required.
-The contents of the items are usually not shown during the search.
+but many clicks and drag operations are required,
+and the contents of the items are usually not shown during the search.
 
@@
 \centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
-\caption{Showing ``Breakfast at Tiffany's''.}
+\caption{Watching ``Breakfast at Tiffany's''.}
 \label{tiffany}
@@
 With Gear, the user can enjoy all available contents on the web with the mouse wheel
-without selecting the source of the movies, animes, and musics (e.g. Amazon, Netflix, etc.).
+without selecting the source of the movies, animes, and musics from Amazon, Netflix, etc.
 

### 2020-05-26 paper/HCC2020-short/paper.tex
Short論文化したもの

--- 2020-03-07 paper/HCC2020/paper.tex
@@
 
-\long\def\ttt#1{\texttt{\small #1}}
+\long\def\ttt#1{\texttt{\textbf{\small #1}}}
 \long\def\tsf#1{\textsf{\small{#1}}}
@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\author{\IEEEauthorblockN{Toshiyuki Masui}
+  \IEEEauthorblockA{
+    \textit{Keio University} \\
+    \textit{Faculty of Environment and Information Studies}\\
+    5322 Endo, Fujisawa, Kanagawa 252-0882 Japan \\
+    masui@pitecan.com
+  }
 }
@@
 \begin{abstract}
-We introduce a novel simple interaction technique for finding and browsing
-data in a huge hierarchical database using only two keys.
+We introduce a simple interaction technique for finding and browsing
+data in a large hierarchical database using only two keys.
 
@@
 If the data was not appropriate,
-he should go to the next entry and perform the selection task again.
+they should go to the next entry and perform the selection task again.
 
@@
 from broadcast TV stations, users could simply rotate
-a television dial to select a channel and watch the program.
-We introduce a simple interaction technique called ``Gear'',
+a television dial to select a channel and watch a program.
+We introduce a simple interaction technique called ``\textit{Gear}'',
 with which users can select an entry from a large hierarchical database and
@@
 is required for viewing the content.
-
-% 昔のテレビやラジオではこの手間がなかった
-% チャンネルやチューニングつまみを回すだけでよかった
-% 選択操作はなかった
-% つまりいわゆる「ザッピング」が可能であった
-
+%
 The confirm operations was not required on old TVs and radios,
@@
 as soon as we rotated a TV channel dial or a tuning dial of the radio.
-
-\begin{figure}[H]
-\centerline{
-   \includegraphics[width=35mm,bb=0 0 279 272]{figures/9bd96506bdaac48b26c5cd192851c11d.png}
-   \includegraphics[width=35mm,bb=0 0 128 72]{figures/fedc4f3c899c48b5a3ddd0982801c79d.png}
-}
-\caption{An old TV channel dial and a radio tuning dial}
-\label{TV channel}
-\end{figure}
-
-% 一般に、選択するとすぐに見えるのはどこでも便利なものである
-% Finderのカバーフローや、最下層では選択内容がすぐに見えたりする
-% このときはConfirmの手間なく内容を見られるのは便利なもので、
-% これをno-click browsingと呼ぶことにする
-% TVもラジオもno-click browsingが可能であった
-
+%
 It is always convenient to view the contents of the selected item
@@
 
-We can use the no-click browsing style on personal computers.
-Using the Finder.app on MacOS, we can use the ``Cover Flow''\footnote{
-  \tsf{https://en.wikipedia.org/wiki/Cover\_Flow}
-} viewer to browse the contents in a folder
-with simple swiping gestures (Figure \ref{coverflow}).
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=65mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
-% \centerline{\includegraphics[width=80mm,bb=0 0 803 555]{figures/5d46fb09c3c5b4baccfd68ca026ef25b.png}} % Monorail
-\caption{Cover Flow on MacOS}
-\label{coverflow}
-\end{figure}
-
-We can also enjoy no-click browsing on the ``column view'' mode of Finder.app.
+We can use no-click browsing on the ``column view'' mode of Finder.app on MacOS.
 In the column view mode, 
@@
 \begin{figure}[H]
-% \centerline{\includegraphics[width=70mm,bb=0 0 1678 846]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
   \centerline{\includegraphics[width=70mm,bb=0 0 839 423]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
@@
 \end{figure}
-
-% テレビやカバーフローのザッピングはもちろんソースが少なかったからできるわけだが、
-% 大量データの場合はこれが難しい。
-% 何千個もソースがある場合は
-% 階層をたどる処理が必要になり、その移動操作が必要だからである
 
@@
 
-% 階層でもそうでなくても、移動操作は慣れている
-% 適切な階層構造を用意して、クリックしながらたどるのがブラウザでは一般的である
-% ブラウザの場合、カバーフローのようなインタフェースは一般的でないので、
-% みつけたものを選択したり戻ったりを繰り返さなければならない。
+It would be better
+if we could perform the navigation task using devices that have only two keys.
 %
-% ブラウザでは階層のInfoVis[]もいろいろあるが、操作に頭を使うし、no-clickブラウジングできるものは無い。
-
-% 階層的なら上下操作でなんとかなる
-% 小型機器で階層情報をたどるときは4-wayでひとつずつたどるのが普通
-
-% The simplest way of navigatin a hierarchical data is to use four keys
-
-When a user cannot use a pointing device,
-key-based interaction techniques are used for
-finding information in hierarchical data.
-%
-For example, a user can find a music data by
-selecting an artist from the list of artist names,
-selecting an album title from the title list,
-and selecting a music title from the song list.
-%
-Users can use two keys for choosing an entry from the list
-% (e.g. selecting an artist from the artist list),
-and use another key for selecting an entry and moving to the next level.
-% (e.g. selecting an artist and show album titles).
-It is also necessary to use another key for going back to the previous level.
-% (e.g. showing the artist list for artist selection).
-This 4-way navigation is popular on small devices
-and remote controllers for selecting a song from the hierarchical data.
-4-way navigation is also available on the column view of Finder.app.
-
-\begin{figure}[H]
-\centerline{
-  \includegraphics[width=30mm,bb=0 0 333 250]{figures/0048a5e91ddcf1d5670bd958e3c55619.jpg}
-  \includegraphics[width=30mm,bb=0 0 551 551]{figures/70c036b24525c6cace9955b24152e97e.jpg}
-  }
-\caption{Small devices supporting 4-way navigation}
-\label{rio}
-\end{figure}
-
-Using 4 keys might be okay on these devices, but it would be better
-if we could perform the navigation task using simpler devices that have only two keys.
-In that case, we can use a rotating device like a disk or a wheel for the navigation,
-since such devices can generate two signals based on the rotation direction.
-
 We have developed a new navigation technique called ``{Gear}'' for no-click browsing,
@@
 {\up} (up) and {\down} (down), are used for the navigation.
-They can be performed either by pressing keys or rotating a dial.
 
@@
 \begin{figure}[H]
-% \includegraphics[width=70mm]{figures/fig1.pdf}
-\centerline{\includegraphics[width=70mm,bb=0 0 490 490]{figures/fig1.pdf}}
+  \centerline{\includegraphics[width=55mm,bb=0 0 490 490]{figures/fig1.pdf}}
   \caption{Sample data: shops data of a shopping mall.}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=\menuwidth, bb=0 0 139 157]{figures/fig2.pdf}}
+  \begin{minipage}{0.45\hsize}
+    \centerline{\includegraphics[width=17mm, bb=0 0 139 157]{figures/fig2.pdf}}
     \caption{Initial display.}
     \label{fig2}
-\end{figure}
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 157]{figures/fig3.pdf}}
+  \end{minipage}
+  \begin{minipage}{0.45\hsize}
+    \centerline{\includegraphics[width=17mm,bb=0 0 139 157]{figures/fig3.pdf}}
     \caption{Typing {\down}.}
     \label{fig3}
+  \end{minipage}
 \end{figure}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 157]{figures/fig4.pdf}}
+  \begin{minipage}{0.45\hsize}
+    \centerline{\includegraphics[width=17mm,bb=0 0 139 157]{figures/fig4.pdf}}
     \caption{Selecting Food/drink.}
     \label{fig4}
-\end{figure}
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 238]{figures/fig5.pdf}}
+  \end{minipage}
+  \begin{minipage}{0.45\hsize}
+    \centerline{\includegraphics[width=17mm,bb=0 0 139 238]{figures/fig5.pdf}}
     \caption{Selecting Liquor shop.}
     \label{fig5}
+  \end{minipage}
 \end{figure}
@@
 \tsf{Fresh grocery} category is selected (Figure \ref{fig6}).
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 238]{figures/fig6.pdf}}
-\caption{Selecting Fresh grocery.}
-\label{fig6}
-\end{figure}
-
+%
 If the user keeps issuing {\down}, 
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 157]{figures/fig8.pdf}}
+  \begin{minipage}{0.45\hsize}
+    \centerline{\includegraphics[width=17mm,bb=0 0 139 238]{figures/fig6.pdf}}
+    \caption{Selecting Fresh grocery.}
+    \label{fig6}
+  \end{minipage}
+  \begin{minipage}{0.45\hsize}
+    \centerline{\includegraphics[width=17mm,bb=0 0 139 157]{figures/fig8.pdf}}
     \caption{Selecting Clothing.}
     \label{fig8}
+  \end{minipage}
 \end{figure}
@@
 the shops under category \tsf{Fresh grocery} is automatically selected (Figure \ref{fig7}).
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 292]{figures/fig7.pdf}}
-\caption{Selecting Fish store.}
-\label{fig7}
-\end{figure}
-
+%
 When the user issues {\up} here, \tsf{Fresh grocery} is selected,
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 211]{figures/fig9.pdf}}
+  \begin{minipage}{0.45\hsize}
+    \centerline{\includegraphics[width=17mm,bb=0 0 139 292]{figures/fig7.pdf}}
+    \caption{Selecting Fish store.}
+    \label{fig7}
+  \end{minipage}
+  \begin{minipage}{0.45\hsize}
+    \centerline{\includegraphics[width=17mm,bb=0 0 139 211]{figures/fig9.pdf}}
     \caption{Selecting Shoes store.}
     \label{fig9}
+  \end{minipage}
 \end{figure}
@@
 
-% SerencastというサービスでGearを使う
-% SerencastはScrapboxを利用したものである
-
 To prove that Gear is useful for selecting an entry from a
 large hierarchical database,
-we have developed the ``\tsf{\SC}'' service, where
-users can enjoy movies, musics, and other web services
-on the browser with the Gear interface without selecting (clicking) an item.
-{\SC} is implemented in JavaScript, and runs on modern web browsers
-
+we have developed the ``\tsf{\SC}'' service\footnote{
+  \tsf{https://serencast.com/}
+}, where users can enjoy movies, musics, and other web services
+on the browser with the Gear interface without clicking an entry.
+{\SC} is implemented in JavaScript and runs on modern web browsers.
+%
 {\SC} uses the ``\tsf{\SB}'' wiki service\footnote{
@@
 {\SB} is an interactive wiki
-system where users can share and edit texts on the web browser.
-A user can create a {\SB} ``project'', and create pages
-that consists of texts and links.
-People can share the page and edit it interactively on their browsers
-just like the Google Docs system\footnote{
-  \tsf{https://www.google.com/docs/about/}
-}.
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=75mm,bb=0 0 1553 1174]{figures/28818d749896f87f3eb8bd6b6f9e9a36.png}}
-\caption{An example of a {\SB} project.}
-\label{exampleproject}
-\end{figure}
-
-Figure \ref{exampleproject} shows an example of a {\SB} project.
-The title of the project is ``Scrapbox help'', and
-other pages like ``Features'' exist in the project.
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=80mm,bb=0 0 1606 1200]{figures/9e867c325bafc415bd0870c1717fbaf7.png}}
-\caption{An example {\SB} page.}
-\label{examplepage}
-\end{figure}
-
-Figure \ref{examplepage} is an example of a {\SB} page.
-%
-The page is based on plain text just like an WikiPedia page is based on plain text.
-Users can use special markup tags
-like ``\texttt{[}'' and ``\texttt{]}'' to show bold texts, icons, URL links,
-and links to other pages.
-In this example, a URL link to {\tsf{http://gyazo.com}} is used
-just like an \tsf{A} tags in HTML.
-
-The raw text of the {\SB} page looks like this:
-
-{\scriptsize
-\begin{verbatim}
-Features
-(The [Check.icon] means we believe this feature is unique \
- to {\SB} among competing services.)
-
-[[Easy to use Gyazo images]]
- By using together with [Gyazo https://gyazo.com] you can \
- surprisingly paste any image onto the page, and it \
- displays instantly.
-
-[Check.icon] [[Use of an [image] to represent pages]]
- By attaching images to each page, it is easier to discover \
-and remember them. Our method allows visual organization to \
-happen spontanteously.
-\end{verbatim}
-}
+system where users can share and edit texts on the web browser,
+just like the Google Docs system.
 
@@
 movies and musics on a {\SB} page,
-% we can create a hierarchical structure from the list and
-% use the Gear interface to find data and browse it.
-We can use {\SC} service
+we can use {\SC} service
 for using the Gear interface to select a program from the
-list on {\SC} pages, and automatically play it on the browser.
+list on {\SB} pages, and automatically play it on the browser.
 
@@
 
+\comment{
 \begin{figure}[H]
-% \centerline{\includegraphics[width=40mm,bb=0 0 417 619]{figures/2690db244045aa809a3e2fc2b40ba0a3.png}}
   \centerline{\includegraphics[width=30mm,bb=0 0 387 568]{figures/2b97930bf5730fcaf4d9c0adeb9c5f6e.png}}
@@
 \end{figure}
+}
 
-The raw text of this page is shown below:
-
+\begin{figure}[H]
 {\scriptsize
 \begin{verbatim}
-Movies
+Movies and videos
  [https://www.netflix.com/watch/70105600 Gran Torino]
@@
  [https://youtube.com/embed/AtZr9g2vwrI?autoplay=1 Fireplace]
-\end{verbatim}}
-
-\begin{figure}[H]
-% \centerline{\includegraphics[width=80mm,bb=0 0 524 598]{figures/65b01a87b67c9a8e838a047b945f6a77.png}}
-\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
-\caption{Watching ``Breakfast at Tiffany's''.}
-\label{tiffany}
+\end{verbatim}
+}
+\caption{A movie list page on {\SB}.}
+\label{movielist}
 \end{figure}
@@
 ``Breakfast at Tiffarny's'' is selected and
-the movie starts at the right side of the screen. (Figure \ref{tiffany})
+the movie starts automatically at the right side of the screen. (Figure \ref{tiffany})
+
+\begin{figure}[H]
+  \centerline{\includegraphics[width=65mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
+  \caption{Watching ``Breakfast at Tiffany's''.}
+  \label{tiffany}
+\end{figure}
 
@@
 the album ``Tequilla'' is listed one level below the level of the name of the artist.
+%
+The title of {\SB} page shown in Figure \ref{musiclist} is ``Music'', and 
+we can collect Movie page, Music page, and other pages by
+listing them in another page (``Top'' page) shown in Figure \ref{top}.
 
 \begin{figure}[H]
-% \centerline{\includegraphics[width=40mm,bb=0 0 596 808]{figures/6657544cf60cbf0aea91ba7da0455b90.png}}
-\centerline{\includegraphics[width=50mm,bb=0 0 652 926]{figures/d8fe8ff8f3e1bbcb34cf51e268592f8c.png}}
+ \begin{minipage}{0.45\hsize}
+  \centerline{\includegraphics[width=30mm,bb=0 0 652 926]{figures/d8fe8ff8f3e1bbcb34cf51e268592f8c.png}}
   \caption{Music list.}
   \label{musiclist}
+ \end{minipage}
+ \begin{minipage}{0.45\hsize}
+  \centerline{\includegraphics[width=22mm,bb=0 0 262 515]{figures/5a644f357ba6a6b81b011e200019d736.png}}
+  \caption{Top page.}
+  \label{top}
+ \end{minipage}
 \end{figure}
 
-The title of this {\SB} page is ``Music'', and 
-we can collect Movie page, Music page, and other pages by
-listing them in another page (``Top'' page, in this case).
-
-\begin{figure}[H]
-% \centerline{\includegraphics[width=40mm,bb=0 0 396 523]{figures/8a8e4d63b75183f1b4d0ed4db733f500.png}}
-\centerline{\includegraphics[width=27mm,bb=0 0 262 515]{figures/5a644f357ba6a6b81b011e200019d736.png}}
-\caption{Top page.}
-\label{top}
-\end{figure}
-
-Many pages (Music, Movies, etc.) are listed in the Top page, and
+Many {\SB} pages (Music, Movies, etc.) are listed in the Top page, and
 the pages are treated as children pages of the Top page.
@@
 A hierarchical database with
-As many as 100,000 pages can be easily constructed on a {\SB} pages, and
-we can select one of the entries only by using only {\up} and {\down} keys,
-using the Gear technique described in section \ref{navigation}.
+As many as 100,000 pages can be easily constructed on {\SB}, and
+we can select one of the entries only by using {\up} and {\down} keys,
+with the Gear technique described in section \ref{navigation}.
 
+\comment{
 \begin{figure}[H]
@@
 \end{figure}
+}
 
 Since anybody can edit {\SB} pages and construct the hierarchical data,
-people can enjoy creating their own hierarchical database by editing their {\SB} pages.
+people can enjoy creating their own database by editing their {\SB} pages.
 When someone wants to advertise their works,
@@
 all such devices can be used as an input device for Gear.
-For example, a foot switch for turning music score pages\footnote{
-  \tsf{https://airturn.com/products/airturn-pedpro}
-} can be used as an input device for Gear.
-Even a special foot pedal can be used for Gear (Figure \ref{footswitch}).
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=40mm,bb=0 0 900 900]{figures/8d4f811f5a0c393acaff304102ba963f.jpg}}
-\caption{A foot switch for turning a music score.}
-\label{footswitch}
-\end{figure}
-
-%
-% Good thing is that many keyboard devices are available for personal computers,
-% and we can use such devices for using Gear.
-% ``Key-repeat'' feature is useful for fast scrolling of the menu.
 
@@
 \begin{figure}[H]
-  \centerline{\includegraphics[width=54mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
+  \centerline{\includegraphics[width=38mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
   \caption{Paddle device for Gear.}
@@
 That behavior is similar to the key-repeat feature of computer keyboards.
-
-% Keys and pressure sensors can be placed anywhere:
-% we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
 
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=54mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
+  \begin{minipage}{0.49\hsize}
+    \centerline{\includegraphics[width=38mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
     \caption{Using a jog dial.}
     \label{jog}
-\end{figure}
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
+  \end{minipage}
+  \begin{minipage}{0.49\hsize}
+    \centerline{\includegraphics[width=38mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
     \caption{A disk-based device for Gear.}
     \label{disk}
+  \end{minipage}
 \end{figure}
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=54mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
+  \centerline{\includegraphics[width=38mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
   \caption{Using a roller.}
@@
 
-% Keys and pressure sensors can be placed anywhere:
-% we tried putting two pressure sensors at the bottom of a chair, and it worked fine.
-
-\comment{
-We tried a lever with two pressure sensors.
-モールス用「エレキー」
-Puddle
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=80mm,bb=0 0 1200 799]{figures/d64d2a8e1dddc57f693267f811510f23.jpg}}
-\caption{Elekey.}
-\label{elekey}
-\end{figure}
-}
-
 After trying various devices, it became clear that simple buttons or
@@
 we felt that the integration of furniture and input devices will be
-important in the IoT age.
+important in the IoT age\cite{10.1145/2494091.2497326}.
 %
-If we can install the devices neatly on furniture and beds, people with disabilities can easily use them,
+If we can install the devices neatly on furniture and beds,
+people with disabilities can easily use them.
 
@@
 
-\begin{figure}[H]
-\centerline{
-%  \includegraphics[width=38mm,bb=0 0 1624 1193]{figures/d663e8556732d40e70e55592ca1f1258.png}
-  \includegraphics[width=70mm,bb=0 0 1624 1193]{figures/75007628f75ef1038bd5737e10a728b7.png}
-}
-\caption{App1: Gear-based application for finding a monorail picture.}
-\label{monorailgear}
-\end{figure}
-
 Using the second one, a user can set the time using the \ttt{{\textless}input type="time"{\textgreater}} tag of HTML (Figure \ref{monorailinput}).
@@
 \begin{figure}[H]
-\centerline{
-  \includegraphics[width=70mm,bb=0 0 1596 1116]{figures/325208a6d94c68e4f08e61a67df419c4.png}
-}
+  \begin{minipage}{0.49\hsize}
+    \centerline{\includegraphics[width=40mm,bb=0 0 1624 1193]{figures/75007628f75ef1038bd5737e10a728b7.png}}
+    \caption{App1: Gear-based application for finding a monorail picture.}
+    \label{monorailgear}
+  \end{minipage}
+  \begin{minipage}{0.49\hsize}
+    \centerline{\includegraphics[width=40mm,bb=0 0 1596 1116]{figures/325208a6d94c68e4f08e61a67df419c4.png}}
     \caption{App2: using input element.}
     \label{monorailinput}
+  \end{minipage}
 \end{figure}
@@
 \centerline{
-  \includegraphics[width=38mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
-  \includegraphics[width=38mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
+  \includegraphics[width=39mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
+  \includegraphics[width=39mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
 }
@@
 and the average time using standard \ttt{{\textless}input{\textgreater}} was 4.96s.
-It takes about 40\% more time than using conventional method.
+It takes about 40\% longer than using conventional method.
 The standard deviations were 0.71s and 0.93s, respectively.
@@
 conventional methods.
-
+%
 We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}), and
@@
 
-% More conventional visualization techniques like TreeView\footnote{
-%   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
-% } by replacing 4-way navigation to our approach.
-
-% {\ST} can be adopted to more conventional visualization techniques like
-% TreeView\footnote{
-%   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
-% } by replacing 4-way navigation to our approach.
-
 It seems to be a good idea to use Gear on more conventional visualization techniques like
@@
 
+\comment{
   \begin{figure}[H]
@@
   \end{figure}
+}
 
@@
 
+\comment{
 \subsection{Timing control}
@@
 We are almost sure that The Gear interface had never been popular before.
+}
 

### 2020-05-27 paper/HCC2020-short/paper.tex
IEEE Copyright notice追加

@@
   \IEEEauthorblockA{
+    % \textit{Faculty of Environment and Information Studies}\\
     \textit{Keio University} \\
-    \textit{Faculty of Environment and Information Studies}\\
-    5322 Endo, Fujisawa, Kanagawa 252-0882 Japan \\
+    % Fujisawa, Japan \\
+    5322 Endo, Fujisawa, Kanagawa 252-0882, Japan \\
     masui@pitecan.com
@@
 
+\IEEEoverridecommandlockouts
+\IEEEpubid{\makebox[\columnwidth]{978-1-7281-6901-9/20/\$31.00~\copyright2020 IEEE\hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
+
 \maketitle
+
+\IEEEpubidadjcol
 
@@
 
-Finding a data from a huge hierarchical database takes time
+Finding data from a huge hierarchical database takes time
 because users should traverse the tree using a mouse or a keyboard,
@@
 \begin{enumerate}
-\item A portion of hierarchical data is shown to the user as a list.
+\item A portion of hierarchical data is shown to the user.
 
@@
 We show how Gear works, using a hierarchical data structure of
-a shops list in a shopping mall shown in Figure \ref{fig1} as example data.
-A rectangles with a thick border represent shop categories, and
+a shop list in a shopping mall shown in Figure \ref{fig1} as example data.
+A rectangles with a thick border represents a shop category, and
 other rectangles represent individual shops.
@@
 large hierarchical database,
-we have developed the ``\tsf{\SC}'' service\footnote{
-  \tsf{https://serencast.com/}
+we developed the ``\tsf{\SC}'' service\footnote{
+  \tsf{https://Serencast.com/}
 }, where users can enjoy movies, musics, and other web services
@@
   \centerline{\includegraphics[width=65mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
-  \caption{Watching ``Breakfast at Tiffany's''.}
+  \caption{Watching ``Breakfast at Tiffany's'' on Serencast.}
   \label{tiffany}
@@
 
-In one page, we can specify a hierarchical structure by using indentations.
-Figure \ref{musiclist} shows a portion of a list of music CDs and
-titles by ``Weather Report'' and ``Wes Montgomery'' are shown\footnote{
-  Weather Report is the name of a famous Jazz group, and Wes Montgomery is a famous Jazz guitarist.
-}.
-For example, 
-``Black Market'' is the first title in the album ``8:30'' of ``Weather Report'', and
-``Scarlet Woman'' follows ``Black Market''.
-``Wes Montgomery'' is listed in the same layer as ``Weather Report'', and
-the album ``Tequilla'' is listed one level below the level of the name of the artist.
-%
-The title of {\SB} page shown in Figure \ref{musiclist} is ``Music'', and 
-we can collect Movie page, Music page, and other pages by
-listing them in another page (``Top'' page) shown in Figure \ref{top}.
-
-\begin{figure}[H]
- \begin{minipage}{0.45\hsize}
-  \centerline{\includegraphics[width=30mm,bb=0 0 652 926]{figures/d8fe8ff8f3e1bbcb34cf51e268592f8c.png}}
-  \caption{Music list.}
-  \label{musiclist}
- \end{minipage}
- \begin{minipage}{0.45\hsize}
-  \centerline{\includegraphics[width=22mm,bb=0 0 262 515]{figures/5a644f357ba6a6b81b011e200019d736.png}}
-  \caption{Top page.}
-  \label{top}
- \end{minipage}
-\end{figure}
-
-Many {\SB} pages (Music, Movies, etc.) are listed in the Top page, and
-the pages are treated as children pages of the Top page.
-By constructing data hierarchically like this,
-We can build a very large hierarchical database for watching movies, videos, news, etc.
-A hierarchical database with
-As many as 100,000 pages can be easily constructed on {\SB}, and
-we can select one of the entries only by using {\up} and {\down} keys,
-with the Gear technique described in section \ref{navigation}.
-
-\comment{
-\begin{figure}[H]
-\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackmarket.png}}
-\caption{Playing a music.}
-\label{blackmarket}
-\end{figure}
-
-\begin{figure}[H]
-\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackjack.png}}
-\caption{Reading a comic book.}
-\label{blackjack}
-\end{figure}
-}
-
 Since anybody can edit {\SB} pages and construct the hierarchical data,
@@
 and give them to other people so that they can watch the pages.
-People can freely include other people's {\SB} pages in their own list
-and enjoy all the contents just by using Gear.
 
@@
 } are available on the market, and
-all such devices can be used as an input device for Gear.
+all such devices can be used as input devices for Gear.
 
@@
 
-We have also tried to use a paddle-like device for generating {\up} and {\down}.
+We have also tried to use a paddle-like device for generating {\up} and {\down} (Figure \ref{paddle}).
 Users can push the puddle to the right to generate {\up} and
@@
 \begin{figure}[H]
+  \begin{minipage}{0.49\hsize}
     \centerline{\includegraphics[width=38mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
@@
     \label{paddle}
+  \end{minipage}
+  \begin{minipage}{0.49\hsize}
+    \centerline{\includegraphics[width=38mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
+    \caption{Using a jog dial.}
+    \label{jog}
+  \end{minipage}
 \end{figure}
@@
 Many kinds of rotating input devices have been used for controlling TVs and VCRs so far.
-For example, ``jog dials'' have been widely used for controlling VCRs, and we tried the device for Gear.
+For example, ``jog dials'' have been widely used for controlling VCRs,
+and we tried the device for Gear (Figure \ref{jog}).
 
 \begin{figure}[H]
-  \begin{minipage}{0.49\hsize}
-    \centerline{\includegraphics[width=38mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
-    \caption{Using a jog dial.}
-    \label{jog}
-  \end{minipage}
   \begin{minipage}{0.49\hsize}
@@
     \label{disk}
+  \end{minipage}
+  \begin{minipage}{0.49\hsize}
+    \centerline{\includegraphics[width=38mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
+    \caption{Using a roller.}
+    \label{roller}
   \end{minipage}
@@
 mouse wheel events are generated as the user rotates the cylinder using his arm or hand.
-
-\begin{figure}[H]
-  \centerline{\includegraphics[width=38mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
-  \caption{Using a roller.}
-  \label{roller}
-\end{figure}
 
@@
 %
-Using the first one (App1), a user can set the time using Gear (Figure \ref{monorailgear})
-with up/down arrow keys for {\up} and {\down}.
+Using the first one (App1), a user can set the time using Gear
+with up/down arrow keys for {\up} and {\down} (Figure \ref{monorailgear}).
 
@@
 \centerline{
-  \includegraphics[width=39mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
-  \includegraphics[width=39mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
+  \includegraphics[width=43mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
+  \includegraphics[width=43mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
 }
@@
   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
-}, by replacing 4-way navigation with Gear.
+}, where 4 keys are used for navigation.
+%
+We can also use Gear on a 1D zooming system like
+LensBar\cite{Masui:1998:LVB:647341.721215},
+where pointing devices are mainly used for navigation.
 
-\comment{
-  \begin{figure}[H]
-    \centerline{
-      \includegraphics[width=38mm,bb=0 0 188 188]{figures/treeview.png}
-    }
-    \caption{A TreeView example.}
-    \label{treeview}
-  \end{figure}
-}
-
-% LensBar\cite{Masui:1998:LVB:647341.721215}
 % is also a ZUI system for handling large hierarchical data,
@@
 
-\comment{
-\subsection{Timing control}
-
-The biggest disadvantage of Gear is that
-the behavior of Gear depends on the speed of the user's operations.
-In Figure \ref{fig4},
-if a user wanted to select \tsf{Clothing} but couldn't issue {\down}
-quickly enough, he will see Figure \ref{fig5} instead of Figure \ref{fig7}.
-This is a tradeoff between usability and simplicity, and
-the best parameter should be set based on the user and the Gear device.
-
-\subsection{Is the Gear interface new?}
-
-Since the idea of Gear interface is so simple,
-we have been wondering if the same idea existed in the past.
-%
-We could not find a research paper on 
-navigation techniques based on two keys.
-Many key-based navigation techniques are found on patent database,
-but we could not find a navigation method based on two keys.
-We are almost sure that The Gear interface had never been popular before.
-}
-
 \subsection{Using Gear in the wild}
 
-One of the authors have been using Gear in his living room for several years
+The author have been using Gear in his living room for several years
 with a small personal computer connected to a 60-inch TV monitor.
@@
 
-\comment{
-Large dictionary database can also be treated as a large
-hierarchical data, since the name of the entry can be treated hierarchically:
-e.g. an entry for ``\tsf{dictionary}'' can be stored under ``\tsf{d}'', ``\tsf{d/i}'', and so on.
-
-No formal evaluation have been done yet, but Gear has been used in the author's
-living room for six months, and the author's family members are using it
-everyday for watching anime films and listening to music.
-Besides PowerMate, a wireless mouse is also used,
-since we can carry it anywhere and select
-a film or a music just by rotating the mouse wheel.
-}
-
 We demonstrated Gear at an exhibition
-% held in November 2013,
 and asked more than 100 people to try it
@@
 \begin{figure}[H]
-\centerline{\includegraphics[width=84mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
+\centerline{\includegraphics[width=50mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
 \caption{People at the right using a wheel device at an exhibition.}
@@
 We have developed a new simple interaction method ``Gear'' for exploring
-large hierarchical data structure.
+a large hierarchical data structure.
 A Gear user can easily find an entry in a huge hierarchical database
-only by using a rotating input device which can be installed at
+only by using two keys or a rotating device that can be installed at
 wide range of locations where conventional keyboards and switches do not fit.

### 2020-05-28 paper/HCC2020-short/paper.tex
...

@@
 People can navigate through a huge information space by
-clicking links, zooming by dragging, and using other GUI techniques.
+clicking links, zooming and scrolling by dragging, and using other GUI techniques.
 These techniques are useful for finding an item in a large information space,
@@
 or issue {\down} to select the element below the selected element.
-Whenever the selection is changed, 3. is performed.
+Whenever the selection is changed, 3) is performed.
 If the depth of the newly selected element is different from the currently
@@
 \item When a newly selected element has children and the user performs no further action,
-the first child of the selected element is newly selected, and 3. is performed.
+the first child of the selected element is newly selected, and 3) is performed.
 As a result, all the siblings of the newly selected element
@@
 \begin{figure}[H]
-  \centerline{\includegraphics[width=55mm,bb=0 0 490 490]{figures/fig1.pdf}}
-  \caption{Sample data: shops data of a shopping mall.}
+  \centerline{\includegraphics[width=60mm,bb=0 0 490 490]{figures/fig1.pdf}}
+  \caption{Sample data: shop list of a shopping mall.}
   \label{fig1}
@@
 ``Breakfast at Tiffarny's'' is selected and
-the movie starts automatically at the right side of the screen. (Figure \ref{tiffany})
+the movie starts automatically at the right side of the screen (Figure \ref{tiffany}).
 
@@
 After repeating the task 5 times, the average time is shown to the user, and the value
-is reported.
+was reported.
 

### 2020-05-29 paper/HCC2020-short/paper.tex
...

@@
 \begin{abstract}
-We introduce a simple interaction technique for finding and browsing
+We introduce a novel simple interaction technique for finding and browsing
 data in a large hierarchical database using only two keys.
@@
 as soon as we find it.
-We call such viewing style as ``\textbf{\tit{no-click browsing}}''.
+We call such viewing style as ``\tit{no-click browsing}''.
 
-We can use no-click browsing on the ``column view'' mode of Finder.app on MacOS.
+We can perform no-click browsing on the ``column view'' mode of Finder.app on
+MacOS using four keys.
 In the column view mode, 
@@
 
-We can use no-click browsing on old TVs and radios because the number of
-broadcast channels are limited.
+We could use no-click browsing on old TVs and radios because the number of
+broadcast channels were limited.
 Likewise, no-click browsing on Finder.app is useful
@@
 
-No-click browsing is not popular on conventional GUI of personal computers.
+No-click browsing is not popular on modern GUI of personal computers.
 People are used to click-based browsing on web browsers and other
@@
 %
-We have developed a new navigation technique called ``{Gear}'' for no-click browsing,
+We have developed a new navigation technique called ``\tit{Gear}'' for no-click browsing,
 where users can explore a large hierarchical database by using only two keys.
@@
 Interaction with Gear is based on the following simple principles.
-Two types of operations,
+Two operations,
 {\up} (up) and {\down} (down), are used for the navigation.
@@
 \begin{figure}[H]
-  \centerline{\includegraphics[width=60mm,bb=0 0 490 490]{figures/fig1.pdf}}
-  \caption{Sample data: shop list of a shopping mall.}
+  \centerline{\includegraphics[width=70mm,bb=0 0 490 490]{figures/fig1.pdf}}
+  \caption{Sample data: shop list in a shopping mall.}
   \label{fig1}
@@
 If the user issues {\down} in Figure \ref{fig4}, the next visible entry
-(\tsf{Clothing}) is selected (Figure \ref{fig8}), and then the state changes to Figure \ref{fig9}.
+(\tsf{Clothing}) is selected (Figure \ref{fig8}), and the state changes to Figure \ref{fig9}.
 
@@
 for using the Gear interface to select a program from the
-list on {\SB} pages, and automatically play it on the browser.
+list on {\SB} pages and automatically play it on the browser.
 
@@
 no-click browsing with Gear is not too slower than
-conventional methods.
+conventional methods using four keys.
 %
 We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}), and
-got similar results as App2.
-
-\comment{
-4-way navigation is commonly used for exploring hierarchical data structure,
-and it is familiar to computer users.
-Some mobile phones and PDAs are equipped with a jog dial with a push button,
-where the dial is used for choosing an item from the list and 
-the push button is used for fixing the selection.
-% PowerMate is equipped with a push button which can used for such purposes.
-% As far as we know,
-All the existing methods require more than 2 keys/buttons, and
-to the best of the authors' knowledge,
-Gear is the only interaction method for exploring hierarchical data structure
-with one rotating device.
-}
+got similar results.
 
@@
   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
-}, where 4 keys are used for navigation.
+}, where four keys are used for navigation.
 %
@@
 %
-Since the only thing a user can do with Gear was to rotate a wheel,
+Since the only thing a user could do with the Gear device was to rotate a wheel,
 users seemed to be able to understand the behavior of Gear with trials and errors.
@@
 % 
-Using only one rotating device for data navigation is a new experience for
-all the visitors, but the hard restriction of the device seemed to have worked in this case.
+Although using only one rotating device for navigation was a new experience for the visitors,
+they seemed to have felt it natural in a short while.
 
 \begin{figure}[H]
-\centerline{\includegraphics[width=50mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
+\centerline{\includegraphics[width=60mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
 \caption{People at the right using a wheel device at an exhibition.}
@@
 only by using two keys or a rotating device that can be installed at
-wide range of locations where conventional keyboards and switches do not fit.
+wide ranges of locations where conventional devices do not fit.
 We are hoping to install various implementations of Gear and try them at
